### 2021-09-22 01-data-cleaning/00-scrape-amicus-text.Rmd
scrape amicus text

---
title: "Tidy Amicus Data"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip?
library(tidyverse)

# parallel processing
library(R.utils)
library(doParallel)
```

# Purpose

There are ~40 folders in Amicus IV > data > amicus files. For each amicus file (denoted by files with "amicus" or "amici" in the file name), copy the file ID, file name, case name, and file text into a CSV.

# 1. Obtain file names and IDs

Set working directory to amcius files folder

```{r}
box_setwd("146066009084")
```

Get IDs of all the case folders

```{r}
# Get the IDs of all the case folders 
case_folders <- box_ls() %>%
  as.data.frame() %>% 
  filter(type == "folder") %>% 
  rename(case = name)

case_folders %>% head(1)
```

For all of the folders, retrieve every file name and ID.

```{r}
# number of cores available
n_cores <- detectCores() - 1

# given a df of ids for SC folder, extract names and ids of all files in case folder
# then, save only the name and id of the decision file
all_file_names <- function(case_folder_ids) {

  # get info for all files contained in each case folder
  # stored in a list of lists
  cases_ids_list <- mclapply(case_folder_ids$id,
                                box_ls,
                                mc.cores = n_cores)

  # convert to list of df
  cases_ids_list <- map(cases_ids_list, as.data.frame)

  # get name of folder (this is case name)
  # NOTE path col is Amicus IV/data/amicus files/case name - we want the last bit "case name"
  cases_ids_list <- lapply(cases_ids_list, function(x) transform(x, case = sub(".*/", "", path)))

  print("Created list of dfs; each element is a case folder")

  # create iterator that will go through list element by element
  it <- iter(cases_ids_list, by = "row")

  # in each case folder, grab the name and id of the decision file
  file_ids <-
    foreach(i = it,
            .combine = rbind,
            .inorder = F) %dopar% {
              i %>%
                filter(grepl("amicus|amici", name, ignore.case = T)) %>%
                select(case, name, id)
            }
  print("Obtained amicus file ids")

  return(file_ids)
}

# run the function for Abortion and Sex Discrim folders
amicus_file_ids <- all_file_names(case_folders)

doParallel::stopImplicitCluster()
```

Check what we have - count of amicus briefs by case for manual comparision

```{r}
# save this file to data > processed amicus files
amicus_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  group_by(case) %>% 
  summarize(n = sum(grepl("amicus|amici", name, ignore.case = T))) %>% 
  arrange(case) #%>% 
  #box_write(., "amicus brief counts.xlsx", dir_id = "145990409196")
```

# 2. Scrape Text

Obtain the raw text from each amicus brief. Note that we have two file types here: DOCX & PDF.

Add file extension as col

```{r}
amicus_file_ids <- amicus_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
amicus_file_ids %>% group_by(file_type) %>% summarize(n = n())
```

```{r}
# create iterator 
itd <- iter(amicus_file_ids, by = "row")

# set up cluster
n_cores <- detectCores() - 1
registerDoParallel(n_cores)

# get text of cases in parallel
amicus_txt <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {

  # get id and file type of current file
  id <- i %>% pull(id)
  type <- i %>% pull(file_type)

  # grab case and brief names
  case <- i %>% pull(case)
  brief <- i %>% pull(name)

  if (type == "pdf") {
    # is the file a PDF

    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        pdftools::pdf_text(x) %>%
        readr::read_lines()
    )

  } else if (type == "docx") {
    # is the file a DOCX

    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_docx(x)
    )

  }  else {
    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_document(x)
    )

  }

  # grab text and concat to string
  #txt <- box_read(
  #  file_id = id,
  #  read_fun = function(x)
  #    textreadr::read_document(x)
  #)

  # concatenate to string
  txt_full <- paste(txt, sep = ' ', collapse = ' ')

  # add row
  data.frame(case, brief, id, txt_full)
}

doParallel::stopImplicitCluster()
```

# 3. Write file to Box

```{r}
box_write(amicus_txt,
          file_name = "raw-amicus-brief-text.csv",
          dir_id = '145990409196')
```

### 2021-09-26 data-cleaning/amicus-structure.Rmd
amicus structure

---
title: "Amicus Structure"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip?
library(tidyverse)
```

# Purpose

To identify which of the amicus briefs follow the structure below:

Summary of (the) argument

Introductory statement

Statement of (the) case

Interest of (the) amici/amicus/amicus curiae (we’re hoping to exclude this section)

Purpose of the motion

Questions presented

Argument (where this is the only word on the line)

# One Example

After some trial and error, below is how we should process the text and search for the phrases of interest. NOte that Box reads in files line by line, so we are able to search individual lines for each phrase.

```{r}
id <- '861820915273'

txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_pdf(x)
    )

#txt_full <- paste(txt, sep = ' ', collapse = ' ')

#txt <- gsub('[[:punct:]]','', txt)
txt <- gsub('\\*.', '', txt)
txt <- str_replace_all(txt, "[^a-zA-z]", replacement = "")
txt <- tolower(txt)

"introductorystatement" %in% txt
"summaryofargument" %in% txt
"summaryoftheargument" %in% txt
"argument" %in% txt
"statementofcase" %in% txt
"statementofthecase" %in% txt
"statementsofinterestofamicuscuriae" %in% txt
"interestofamici" %in% txt
"interestoftheamici" %in% txt
"interestofamicus" %in% txt
"interestoftheamicus" %in% txt
"interestofamicuscuriae" %in% txt
"interestoftheamicuscuriae" %in% txt
"purposeofthemotion" %in% txt
"questionspresented" %in% txt
```

# Read in all files, process & search for phrases

Read in amicus file ids csv

```{r}
amicus_ids <- box_read("864720529825")
amicus_ids <- amicus_ids %>% filter(!is.na(id))
amicus_ids %>% head(5)
```

Break up into smaller sections

Search for phrases:

```{r}
# create iterator 
itd <- iter(amicus_ids, by = "row")

# set up cluster
n_cores <- detectCores() - 1
registerDoParallel(n_cores)

# get text of cases in parallel
amicus_structure <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {

  # get id and file type of current file
  id <- i %>% pull(id)
  type <- i %>% pull(file_type)

  # grab case and brief names
  case <- i %>% pull(case)
  brief <- i %>% pull(name)

  cat(case)
  cat("\t brief started:", brief)

  if (type == "pdf") {
    # is the file a PDF

    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        pdftools::pdf_text(x) %>%
        readr::read_lines()
    )

  } else if (type == "docx") {
    # is the file a DOCX

    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_docx(x)
    )

  }  else {
    txt <- box_read(
      file_id = id,
      read_fun = function(x)
        textreadr::read_document(x)
    )

  }

  cat("\t \t text read")

  # clean
  txt <- gsub('\\*.', '', txt)
  txt <- str_replace_all(txt, "[^a-zA-z]", replacement = "")
  txt <- tolower(txt)

  # search
  intro <- "introductorystatement" %in% txt
  summary <- ifelse("summaryofargument" %in% txt|"summaryoftheargument" %in% txt, T, F)
  argument <- "argument" %in% txt
  statement <- ifelse("statementofcase" %in% txt|"statementofthecase" %in% txt, T, F)
  interest <- ifelse("statementsofinterestofamicuscuriae" %in% txt |
                       "interestofamicuscuriae" %in% txt |
                       "interestoftheamicuscuriae" %in% txt |
                       "interestofamici" %in% txt |
                       "interestoftheamici" %in% txt |
                       "interestofamicus" %in% txt |
                       "interestoftheamicus" %in% txt, T, F)
  purpose <- "purposeofthemotion" %in% txt
  question <- "questionspresented" %in% txt

  cat("\t \t phrases found")
  cat("\t \t brief finished")

  # add row
  data.frame(case, brief, id, intro, summary, argument, statement, interest, purpose, question)
}

doParallel::stopImplicitCluster()
```

Save to Box

```{r}
box_write(amicus_structure, "amicus structure.xlsx", dir_id = "145990409196")
```

# Check

The main vars we are interested in are "interest" and "summary". Between these two headings is information about the interests of amicus brief authors that we want to remove.

From the first pass, we see that 244 documents have both the interest and summary sections and 103 are missing both.

```{r}
amicus_structure %>% 
  select(case, brief, interest, summary) %>% 
  group_by(interest, summary) %>% 
  summarize(n = n())
```

Individually check some that are missing "interest". Are there some cases where the formatting/langauge is just different? It's bc they are pdfs and pdfs don't read in line-by-line :(

```{r}
amicus_structure %>% filter(!interest) %>% group_by(case) %>% summarize(n = n()) %>% arrange(-n)
```

# Backup - grepl in text to search for phrases

We can search for all phrases except "argument" by itself

```{r}
amicus <- box_read("863216279471")
```

Search for phrases using grepl:

```{r}
amicus <- amicus %>%
  mutate(txt_full = tolower(txt_full),
         txt_full = str_squish(txt_full)) %>% 
  mutate(intro = grepl("introductory statement", txt_full),
         summary = grepl("summary of argument|summary of the argument", txt_full),
         interest = grepl("interest of amicus|interest of the amicus|interest of amici|interest of the amici", txt_full),
         statement = grepl("statement of case|statement of the case", txt_full),
         purpose = grepl("purpose of the motion", txt_full),
         question = grepl("questions presented", txt_full))

amicus_summary <- amicus %>% 
  select(-txt_full)

amicus_summary %>% head(5)
```

Add to Box

```{r}
box_write(amicus_summary, "amicus summary.xlsx", dir_id = "145990409196")
```

check results - most briefs have summary and interest

```{r}
amicus_summary %>% select(intro:question) %>% summarize(across(.fns = ~ sum(., is.na(.), 0)))
```
Check co-occurrence - Most briefs have "summary" and "interest" sections (517).

```{r}
amicus_summary %>% group_by(summary, statement) %>% summarize(n = n())
```

Which briefs don't have "summary" ?

```{r}
amicus_summary %>% filter(!summary) %>% group_by(case) %>% summarize(n = n()) %>% arrange(-n)
```

```{r}
amicus_summary %>% filter(case == "Harris v. McRae", !summary)
```

### 2021-10-29 eda/amicus-word-count.Rmd
word count + shortening

---
title: "Amicus Word Count"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(tidytext)
```

# Purpose

Get word count of amicus briefs -- min, max, med, avg. May need to use long transformers instead of regular since we have some pretty long docs?

consult w/ JSS

```{r}
# raw amicus text
amicus <- box_read("863216279471")

amicus %>% head(5)
```

# Tokenize

Tokenize text as is then get # words per brief

```{r}
# returns case, brief, word for all words in all cases
amicus_tokens <- amicus %>% 
  select(case, brief, text = txt_full) %>%
  group_by(brief) %>% 
  unnest_tokens(word, text)

# word ct per brief
amicus_wrdct <- amicus_tokens %>% group_by(brief) %>% summarize(n=n())
```

# Explore word count

Summary - way higher than BERT.

```{r}
summary(amicus_wrdct$n)
```

LongFormers can use up to 16k tokens... any texts that are longer than this? Yes. We have 45 amicus briefs with 16k+ tokens. Possible we may be able to pare these down but it will have to be manual and we need to make sure we aren't losing information.

```{r}
amicus_wrdct %>% filter(n >= 16000) %>% arrange(-n)
```

### 2021-11-04 data-cleaning/01-shorten-amicus-text.Rmd
reorg

---
title: "Amicus Word Count"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(tidytext)
```

# Purpose

To pare down amicus text by removing unnecessary/irrelevant text.

1) Remove text AFTER "Summary of Argument" keyword.

2) Remove text AFTER "Appendix" keyword

* "footnotes" ??

Use footnotes when present. If not footnotes, use appendix. If neither: check. There are 154 docs with neither

```{r}
amicus <- amicus %>%
  mutate(txt_full = tolower(txt_full),
         txt_full = str_squish(txt_full)) %>% 
  mutate(appendix = str_count(txt_full, "appendix"),
         footnotes = str_count(txt_full, "footnote"))

amicus %>% select(case, brief, appendix, footnotes) %>% 
  group_by(appendix > 0, footnotes >0) %>% 
  summarize(n())
```

```{r}
amicus %>% filter()
```

### 2021-11-04 eda/amicus-structure.Rmd
reorg

--- 2021-09-26 data-cleaning/amicus-structure.Rmd
@@
 ```{r}
-amicus_summary %>% filter(case == "Harris v. McRae", !summary)
+amicus_summary %>% filter(!summary) %>% group_by(intro, statement) %>% summarize(n=n())
 ```
+
+```{r}
+amicus_summary %>% filter(grepl("docx", brief), !summary)
+```
+
+```{r}
+sum_id <- readxl::read_excel(path = "../reference_files/docx_summary_ids.xlsx")
+sum_id %>% head(5)
+```
+
+```{r}
+amicus %>% filter(id == 861820896073) %>% 
+  mutate(t = grepl("protecting a woman’s health. argument", txt_full)) %>% 
+  select(t)
+```

### 2021-11-04 data-cleaning/00-scrape-amicus-text.Rmd
amicus structure
scrape text w/shorten keyword

--- 2021-09-22 01-data-cleaning/00-scrape-amicus-text.Rmd
@@
 n_cores <- detectCores() - 1
+registerDoParallel(n_cores)
 
@@
 
-Check what we have - count of amicus briefs by case for manual comparision
+Check what we have - count of amicus briefs by case for manual comparison
 
@@
   #box_write(., "amicus brief counts.xlsx", dir_id = "145990409196")
+```
+
+Save list of amicus file IDs on Box
+
+```{r}
+amicus_file_ids %>% 
+  right_join(., case_folders, "case") %>% 
+  select(-id.y) %>% 
+  rename(id = id.x) %>% 
+  mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
+  box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
 ```
@@
 box_write(amicus_txt,
-          file_name = "raw-amicus-brief-text.csv",
+          file_name = "shortened-amicus-brief-text.csv",
           dir_id = '145990409196')

### 2021-11-05 data-cleaning/01-shorten-amicus-text.Rmd
rmv intros from amicus text

@@
 library(tidytext)
+
+# data
+# data/processed amicus files/shortened-amicus-brief-text.csv
+amicus <- box_read("880862059511")
+# data/processed amicus files/amicus summary.xlsx
+alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
+  select(case, brief, id, alternative) %>% 
+  filter(!is.na(alternative))
 ```
@@
 
-* "footnotes" ??
+# Remove after "Summary of Argument"
+
+For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document.
+This represents the point at which the brief starts discussing their argument.
+We don't need text prior to this, as it's mainly intro information about the case and/or the authors.
+If "summary of argument" text doesn't exist (only in the case of a few pdfs), use the `alternative_rmv` df to find where to start reading the text.
+
+alternate removal strings
+
+```{r}
+alternate_rmv %>% select(id,alternative)
+```
+Shorten
+
+```{r}
+# remove text after "summary of argument" if it exists
+amicus <- amicus %>% 
+  mutate(txt_full = str_to_lower(txt_full),
+         txt_full = str_squish(txt_full),
+         txt_short = case_when(
+           grepl("summary of argument", txt_full) ~ 
+             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
+           grepl("summary of the argument", txt_full) ~
+             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
+           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", x = txt_full),
+           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
+           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
+           T ~ ""),
+         txt_short = str_squish(txt_short))
+```
+
+Check none are missed
+
+```{r}
+amicus %>% filter(txt_short == "") %>% select(-txt_full)
+```
+
+Check a few by running this line a few times.
+
+```{r}
+#amicus %>% sample_n(1) %>% pull(txt_short)
+```
+
+# Remove text after "Appendix" or "Footnotes"
 
@@
 amicus <- amicus %>%
-  mutate(txt_full = tolower(txt_full),
-         txt_full = str_squish(txt_full)) %>% 
   mutate(appendix = str_count(txt_full, "appendix"),
@@
 
-amicus %>% select(case, brief, appendix, footnotes) %>% 
-  group_by(appendix > 0, footnotes >0) %>% 
-  summarize(n())
+amicus %>% select(case, brief, id, appendix, footnotes) %>% 
+  filter(appendix==0 & footnotes==0)
+```
+
+# Save
+
+Original text saved, just added new txt_short col
+
+```{r}
+amicus %>% colnames
 ```
@@
 ```{r}
-amicus %>% filter()
+box_write(amicus,
+          file_name = "shortened-amicus-brief-text.csv",
+          dir_id = '145990409196')
 ```

### 2021-11-05 eda/amicus-word-count.Rmd
word count on shortened txt

@@
 ```{r}
-# raw amicus text
-amicus <- box_read("863216279471")
+# shortened amicus text
+amicus <- box_read("880862059511")
 
@@
 amicus_tokens <- amicus %>% 
-  select(case, brief, text = txt_full) %>%
+  select(case, brief, text = txt_short) %>%
   group_by(brief) %>% 
@@
 
+Number of docs w/ > 512 tokens (regular transformers), > 4,096 tokens (longformer), > 16k tokens (longformer w/adjustments & computing power)
+
+```{r}
+amicus_wrdct <- amicus_wrdct %>% 
+  mutate(greater_512 = n > 512,
+         num_blocks_512 = ceiling(n/512),
+         greater_4096 = n > 4096,
+         num_blocks_4096 = ceiling(n/4096),
+         greater_16k = n > 16000,
+         num_blocks_16k = ceiling(n/16000))
+
+# num docs at each length
+amicus_wrdct %>% 
+  summarize(greater_512 = sum(greater_512*1),
+            greater_4096 = sum(greater_4096*1),
+            greater_16k = sum(greater_16k*1))
+```
+
+How many processing blocks would we need for each model?
+
+```{r}
+amicus_wrdct %>% 
+  filter(brief != "Ayotte v Planned Parenthood of Northern New England. Amici Brief for Petitioner%2c by Loren Leman et al.docx") %>% 
+  summarize(med_blocks_512 = median(num_blocks_512),
+            med_blocks_4096 = median(num_blocks_4096),
+            med_blocks_16k = median(num_blocks_16k))
+```
+
 LongFormers can use up to 16k tokens...

### 2021-11-10 data-cleaning/01-shorten-amicus-text.Rmd
update file saves, list of app/fn briefs

@@
 ```{r}
-amicus <- amicus %>%
-  mutate(appendix = str_count(txt_full, "appendix"),
-         footnotes = str_count(txt_full, "footnote"))
+amicus_ends <- amicus %>%
+  mutate(appendix = str_count(txt_short, "appendix"),
+         appendices = str_count(txt_short, "appendices"),
+         footnotes = str_count(txt_short, "footnotes"))
 
-amicus %>% select(case, brief, id, appendix, footnotes) %>% 
-  filter(appendix==0 & footnotes==0)
+amicus_ends <- amicus_ends %>% select(case, brief, id, appendix, footnotes)
+
+#box_write(amicus_ends,
+#          file_name = "amicus appendix and footnotes counts.csv",
+#          dir_id = 145990409196)
 ```
@@
 ```{r}
+amicus <- amicus %>% select(-txt_full)
 amicus %>% colnames
@@
           file_name = "shortened-amicus-brief-text.csv",
-          dir_id = '145990409196')
+          dir_id = 145990409196)
 ```

### 2021-11-12 data-cleaning/01-shorten-amicus-text.Rmd
footnotes search #1

@@
 library(tidytext)
+library(conText)
 
@@
 
-# Remove text after "Appendix" or "Footnotes"
+# Check isntances of "Appendix" or "Footnotes"
 
@@
 
+# Remove footnotes instances
+
+Process:
+
+0. Check if "footnotes" is within three words of "omitted" -> in this case, do not remove any text.
+1. Ignore instances of "footnotes" in our exceptions:
+    * 861810659757"
+    * 861821999947 (ignore first instance, second instance is footnotes)
+    * 861823138310
+    * 861811382099
+    * 861820447683
+2. If "footnotes" is referenced one time, remove all text after this reference
+3. If "footnotes" is mentioned more than once, remove text after the first reference
+
+First, get context around "footnotes"
+
+```{r}
+# context function changes brief names to "textN" 
+# create this var here so we can map files back
+brief_names <- amicus %>% 
+  arrange(case,brief) %>% 
+  mutate(docname = paste0("text", 1:n())) %>%
+  select(brief, id, docname)
+
+# remove punctuation
+amicus <- amicus %>% 
+  arrange(case, brief) %>% 
+  mutate(txt_short_clean = gsub("[^[:alpha:][:space:][:digit:]]", " ", txt_short),
+                            txt_short_clean = str_squish(txt_short_clean))
+
+# get context around "footnotes"
+footnotes_context <- get_context(x = amicus$txt_short_clean, target = "footnotes", 
+                                 window = 5, valuetype = "fixed",
+                                 case_insensitive = T, hard_cut = F, verbose = F)
+```
+
+Cases where "footnotes" actually references footnotes section, by intuition and some manual inspection:
+* footnotes 1
+* footnotes counsel of record
+
+```{r}
+footnotes_confirmed <- brief_names %>%
+  left_join(., footnotes_context, by = "docname") %>%
+  select(-target) %>%
+  mutate(footnotes_true = ifelse(grepl(" 1 ", context) |
+                                   grepl("counsel of record", context),
+                                 1, 0)) %>%
+  filter(footnotes_true == 1)
+
+footnotes_confirmed %>% distinct(id) %>% nrow()
+```
+
+No footnotes:
+
+```{r}
+amicus %>% filter(!grepl("footnotes", txt_short)) %>% nrow()
+```
+
+Remaining cases: note that this df can have multiple instances of the same case if more than one instance of "footnotes" found.
+
+```{r}
+footnotes_tbd <- brief_names %>%
+  left_join(., footnotes_context, by = "docname") %>%
+  # remove instances of confirmed footnotes (n = 398)
+  filter(!(id %in% footnotes_confirmed$id)) %>% 
+  # remove instances where "footnotes" not found (n = 270)
+  filter(!is.na(context))
+```
+
+Save this file for checking:
+
+```{r}
+#box_write(footnotes_tbd, file_name = "briefs to check footnotes.xlsx", dir_id = 145990409196)
+```
+
 # Save

### 2022-01-11 data-cleaning/01-shorten-amicus-text.Rmd
notes

@@
 ```
-Shorten
+
+Remove text before summary of argument (already done)
 
@@
 
-# Check isntances of "Appendix" or "Footnotes"
+# Check instances of "Appendix" or "Footnotes"
 
@@
 
+# Remove appendices instances
+
+From undergrad assistant: "I have found that often, the appendix will start with an asterisk (usually *1A Appendix). The Appendix also almost always immediately precedes the footnotes."
+
+We need to:
+
+1. find instances of "*1A Appendix" in the text 
+2. Check that this only occurs 1x in a doc. 
+3a. If 2) is true, then remove text after these instances.
+3b. If 3) is false, further inspect the text (may require manual removal)
+4. If it does not occur at all, check for the marker for footnotes (see next section). 
+5a. If footnote marker exists, remove all text after
+5b. If footnote marker does not exist, then manually inspect text. If there are footnotes/appendix, insert flag into text: "MNOPQRST" (w/o quotes) and remove all text after that flag.
+
+```{r}
+brief_names <- amicus %>% 
+  arrange(case,brief) %>% 
+  mutate(docname = paste0("text", 1:n())) %>%
+  select(brief, id, docname)
+
+# remove punctuation
+amicus <- amicus %>% 
+  arrange(case, brief) %>% 
+  mutate(txt_short_clean = gsub("[^[:alpha:][:space:][:digit:]]", " ", txt_short),
+                            txt_short_clean = str_squish(txt_short_clean))
+
+# get context around "footnotes"
+appendix_context <- get_context(x = amicus$txt_short, target = "appendix", 
+                                 window = 5, valuetype = "fixed",
+                                 case_insensitive = T, hard_cut = F, verbose = F)
+
+appendix_context <- brief_names %>%
+  left_join(., appendix_context, by = "docname")
+```
+
+Look for *1a
+
+```{r}
+appendix_context %>% filter(grepl("* 1a", context))
+```
+
+```{r}
+amicus %>% filter(grepl("\\* 1a appendix|*", txt_short)) #%>% select(brief)
+```
+
 # Remove footnotes instances
-
-Process:
-
-0. Check if "footnotes" is within three words of "omitted" -> in this case, do not remove any text.
-1. Ignore instances of "footnotes" in our exceptions:
-    * 861810659757"
-    * 861821999947 (ignore first instance, second instance is footnotes)
-    * 861823138310
-    * 861811382099
-    * 861820447683
-2. If "footnotes" is referenced one time, remove all text after this reference
-3. If "footnotes" is mentioned more than once, remove text after the first reference
 
@@
 ```{r}
-box_write(amicus,
-          file_name = "shortened-amicus-brief-text.csv",
-          dir_id = 145990409196)
+#box_write(amicus,
+#          file_name = "shortened-amicus-brief-text.csv",
+#          dir_id = 145990409196)
 ```

### 2022-01-19 data-cleaning/footnotes_appendix.Rmd
adding appendix/footnotes research

---
title: "Removing footnotes and appendix"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(tidytext)
#library(conText)

# data
# data/processed amicus files/shortened-amicus-brief-text.csv
amicus <- box_read("880862059511")
# data/processed amicus files/amicus summary.xlsx
alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
  select(case, brief, id, alternative) %>% 
  filter(!is.na(alternative))
```

# Purpose

To pare down amicus text by removing unnecessary/irrelevant text.

1) Remove text BEFORE "Summary of Argument" keyword.

2) Remove text AFTER "Appendix" keyword

# Remove after "Summary of Argument"

For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document. This represents the point at which the brief starts discussing their argument. We don't need text prior to this, as it's mainly intro information about the case and/or the authors. If "summary of argument" text doesn't exist (only in the case of a few pdfs), use the `alternative_rmv` df to find where to start reading the text.

alternate removal strings

```{r}
alternate_rmv %>% select(id,alternative)
```

Remove text before summary of argument (already done)

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>% 
  mutate(txt_full = str_to_lower(txt_full),
         txt_full = str_squish(txt_full),
         txt_short = case_when(
           grepl("summary of argument", txt_full) ~ 
             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
           grepl("summary of the argument", txt_full) ~
             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", 
                                     x = txt_full),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           T ~ ""),
         txt_short = str_squish(txt_short))
```

Check none are missed

```{r}
amicus %>% filter(txt_short == "") %>% select(-txt_full)
```

Check a few by running this line a few times.

```{r}
#amicus %>% sample_n(1) %>% pull(txt_short)
```

# Check instances of "Appendix" or "Footnotes"

Use footnotes when present. If not footnotes, use appendix. If neither: check. There are 154 docs with neither

# Remove appendices instances

From undergrad assistant: "I have found that often, the appendix will start with an asterisk (usually *1A Appendix). The Appendix also almost always immediately precedes the footnotes."

We need to:

1. find instances of "*1A Appendix" in the text 
2. Check that this only occurs 1x in a doc. 
3a. If 2) is true, then remove text after these instances.
3b. If 2) is false, further inspect the text (may require manual removal)
4. If it does not occur at all, check for the marker for footnotes (see next section). 
5a. If footnote marker exists, remove all text after
5b. If footnote marker does not exist, then manually inspect text. If there are footnotes/appendix, insert flag into text: "MNOPQRST" (w/o quotes) and remove all text after that flag.

## 1. find instances of "*1A Appendix" in the text

```{r}
a <- amicus %>%
  mutate(txt_short = str_squish(txt_short),
    appendix = str_count(txt_short, "appendix"),
    appendix_1a = str_count(txt_short, "\\*1a appendix"),
    footnotes = str_count(txt_short, "footnotes"))
```

## 2. Check that this only occurs 1x in a doc.

```{r}
table(a$appendix)
```

```{r}
table(a$appendix_1a)
```

There are only 55 documents that mention 1a appendix, but 295 that mention an appendix.This means if we remove text after `1a appendix` this covers 55 documents leaving 240 documents mentioning `appendix` left to deal with.

## 3a. If 2) is true, then remove text after these instances.s

This is preliminary code to remove text after `*1a appendix`.

```{r}
amicus_clean <- amicus %>% mutate(
         txt_short = str_squish(txt_short),
         txt_short = case_when(
           grepl("\\*1a appendix", txt_short) ~ 
             gsub(pattern = "\\*1a appendix.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

```{r}
amicus_clean %>% filter(txt_short == "")
```

## 3b. If 2) is false, further inspect the text (may require manual removal)

There were no documents that mentioned *1a appendix more than once so we can be confident that they were referring to the actual appendix. However, now there are 267 documents that contain `appendix` to deal with. Some of these include the documents above that already had the appendix remove so the real number of documents we need to remove is less if we just handle dealing with them in the same code chunk like lines 128-136.

```{r}
a_clean <- amicus_clean %>%
  mutate(txt_short = str_squish(txt_short),
    appendix = str_count(txt_short, "appendix"))

table(a_clean$appendix)
```

## 4. If it does not occur at all, check for the marker for footnotes (see next section).

When all text after the appendix is removed, this will include any footnotes as the appendix precedes the footnotes. We now only need to remove the footnotes from additional documents that did not have an appendix.

```{r}
a_f <- a %>% filter(appendix_1a == 0 & appendix == 0)

table(a_f$footnotes)
```

There are 263 documents containing `footnotes` that don't mention `appendix`.

I could not get your `get_context` code to work but I know from my previous research and some manual inspection that the following logic should work for removing footnotes. The footnotes are not referenced for the the footnotes section except to mention that something was omitted from the footnotes therefore removing or ignoring those instances, we can remove text after the first instance of the word `footnotes`.

1. ignore/remove these instances:
    * `footnotes omitted` or
    * 3 words from omitted
2. Use first finding of the word `footnotes` and remove text after that

We can also use some of your logic instead. The code below is pretty much what we need, but need to combined with logic above to only perform this on documents that didn't have appendix.

```{r}
#remove text with omitted within 3 words of footnotes
amicus_clean <- amicus_clean %>% mutate(
         txt_short = case_when(
           grepl('(footnotes (\\w+\\s){0,3}omitted)|(omitted (\\w+\\s){0,3}footnotes)', txt_short) ~ 
             gsub(pattern = '(footnotes (\\w+\\s){0,3}omitted)|(omitted (\\w+\\s){0,3}footnotes)',
                  replacement = "", x = txt_short),
           T ~ txt_short)
          )

#remove text after footnotes
amicus_clean <- amicus_clean %>% mutate(
         txt_short = str_squish(txt_short),
         txt_short = case_when(
           grepl("footnotes", txt_short) ~ 
             gsub(pattern = "footnotes.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

## more exploration

I wanted to look back at the full text before capitalization was removed becuase I noticed that many times an appendix might be referenced in text but when it is full caps like `APPENDIX` it references the actual appendix.

```{r}
amicus_full <- box_read("863216279471")
```

```{r}
amicus_ends_full <- amicus_full %>%
  mutate(txt_full = str_squish(txt_full),
    appendix = str_count(txt_full, "APPENDIX"),
         appendix_1a = str_count(txt_full, "\\*1A APPENDIX"))

a <- amicus_ends_full %>% select(case, brief, id, appendix, appendix_1a)

table(a$appendix)
```

```{r}
table(a$appendix_1a)
```

Only 53 instances contain `*1A APPENDIX` while 202 contain the word `APPENDIX`.

There were 55 that contained `*1a appendix` without caps so I think it would be good to ignore cases in this instance but `appendix` is mentioned in 295 docs so filtering down to the 202 with `APPENDIX` and handling the 93 remaining might be useful. I also didn't check for `Appendix` vs `appendix` but cases might help us narrow down here.

```{r}
amicus_lower <- amicus_full %>% mutate(txt_full = str_to_lower(txt_full))

amicus_lower_ends <- amicus_lower %>%
  mutate(txt_full = str_squish(txt_full),
    appendix = str_count(txt_full, "appendix"),
         appendix_1a = str_count(txt_full, "\\*1a appendix"))

a_lower <- amicus_lower_ends %>% select(case, brief, id, appendix, appendix_1a)

table(a_lower$appendix)
```

```{r}
table(a_lower$appendix_1a)
```

### 2022-01-20 data-cleaning/footnotes_appendix.Rmd
notes

@@
 
+**Already done to the shortened-amicus csv file, skip this**
+
 For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document.
@@
 ```{r}
-alternate_rmv %>% select(id,alternative)
+#alternate_rmv %>% select(id,alternative)
 ```
 
-Remove text before summary of argument (already done)
+Remove text before summary of argument (already done in shortened-amicus-text csv, not raw text csv.)
 
@@
 amicus <- amicus %>% 
-  mutate(txt_full = str_to_lower(txt_full),
+  mutate(txt_full = str_to_lower(txt_short),
          txt_full = str_squish(txt_full),
@@
     appendix = str_count(txt_short, "appendix"),
-    appendix_1a = str_count(txt_short, "\\*1a appendix"),
+    appendix_1a = str_count(txt_short, "\\*1a appendix|1a appendix|1 a appendix|\\*1a"),
     footnotes = str_count(txt_short, "footnotes"))
@@
 There are only 55 documents that mention 1a appendix, but 295 that mention an appendix.This means if we remove text after `1a appendix` this covers 55 documents leaving 240 documents mentioning `appendix` left to deal with.
+
+```{r}
+a %>% filter(brief== "Gonzales v Carhart. Amici Brief for Respondents (feminist), by Constitutional Law Professors et al.docx")
+```
+
+```{r}
+a %>% filter(appendix_1a==0) %>% select(brief) %>% sample_n(1)
+```
 
@@
 We can also use some of your logic instead. The code below is pretty much what we need, but need to combined with logic above to only perform this on documents that didn't have appendix.
+
+**We don't need to worry about the 'omitted footnote' language in the text. Remove text after 'footnotes counsel of record' or 'footnotes 1' (see github issue)**
 

### 2022-01-25 data-cleaning/footnotes_appendix.Rmd
#1 started fresh to remove text

--- 2022-01-19 data-cleaning/footnotes_appendix.Rmd
@@
 ---
-title: "Removing footnotes and appendix"
+title: "Removing footnotes and appendices"
 author: "Sarah Torrence"
@@
 library(tidytext)
-#library(conText)
 
 # data
-# data/processed amicus files/shortened-amicus-brief-text.csv
-amicus <- box_read("880862059511")
+# data/processed amicus files/raw-amicus-brief-text.csv
+amicus <- box_read("863216279471")
 # data/processed amicus files/amicus summary.xlsx
@@
   filter(!is.na(alternative))
+#data/processed amicus files/footnotes-confirmed.csv
+footnotes_ids <- box_read("908607927934")
 ```
@@
 
-# Remove after "Summary of Argument"
+# Remove before "Summary of Argument"
 
@@
 amicus <- amicus %>%
-  mutate(txt_full = str_to_lower(txt_full),
-         txt_full = str_squish(txt_full),
+  mutate(txt_full = str_squish(txt_full),
          txt_short = case_when(
-           grepl("summary of argument", txt_full) ~ 
-             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
-           grepl("summary of the argument", txt_full) ~
-             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
+           id == 861820795454 ~ gsub(pattern = ".*summary \\[\\*9\\] of the argument", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           grepl("summary of argument|Summary of Argument|SUMMARY OF ARGUMENT", txt_full,
+                 ignore.case = TRUE) ~
+             gsub(pattern = ".*summary of argument|.*Summary of Argument|.*SUMMARY OF ARGUMENT",
+                  replacement = "",
+                  x = txt_full, ignore.case = TRUE),
+           grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
+             gsub(pattern = ".*summary of the argument", replacement = "",
+                  x = txt_full, ignore.case = TRUE),
            id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "",
-                                     x = txt_full),
-           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
-           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
-           T ~ ""),
+                                     x = txt_full, ignore.case = TRUE),
+           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           #this line can be changed to T ~ '' once the raw brief file is updated
+           T ~ txt_full),
          txt_short = str_squish(txt_short))
@@
 
-# Check instances of "Appendix" or "Footnotes"
+# Removing Appendices
 
-Use footnotes when present. If not footnotes, use appendix. If neither: check. There are 154 docs with neither
+## Remove *1A Appendix
 
-# Remove appendices instances
+Whenever `*1A Appendix` shows up in the text, this is referring to the start of the appendix. We want to remove all text after this phrase from the briefs that contain this phrase.
 
-From undergrad assistant: "I have found that often, the appendix will start with an asterisk (usually *1A Appendix). The Appendix also almost always immediately precedes the footnotes."
-
-We need to:
-
-1. find instances of "*1A Appendix" in the text 
-2. Check that this only occurs 1x in a doc. 
-3a. If 2) is true, then remove text after these instances.
-3b. If 2) is false, further inspect the text (may require manual removal)
-4. If it does not occur at all, check for the marker for footnotes (see next section). 
-5a. If footnote marker exists, remove all text after
-5b. If footnote marker does not exist, then manually inspect text. If there are footnotes/appendix, insert flag into text: "MNOPQRST" (w/o quotes) and remove all text after that flag.
-
-## 1. find instances of "*1A Appendix" in the text
+### find instances of "*1A Appendix" in the text
 
 ```{r}
-a <- amicus %>%
+amicus <- amicus %>%
   mutate(txt_short = str_squish(txt_short),
-    appendix = str_count(txt_short, "appendix"),
-    appendix_1a = str_count(txt_short, "\\*1a appendix"),
-    footnotes = str_count(txt_short, "footnotes"))
+    appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix|\\*IA APPENDIX"))
 ```
 
-## 2. Check that this only occurs 1x in a doc.
+Check that this only occurs 1x in a doc.
 
 ```{r}
-table(a$appendix)
+table(amicus$appendix_1a)
 ```
 
-```{r}
-table(a$appendix_1a)
-```
-
-There are only 55 documents that mention 1a appendix, but 295 that mention an appendix.This means if we remove text after `1a appendix` this covers 55 documents leaving 240 documents mentioning `appendix` left to deal with.
-
-## 3a. If 2) is true, then remove text after these instances.s
-
-This is preliminary code to remove text after `*1a appendix`.
+Since this phrase only occurs once in the briefs in which it is present, we can just remove all text after this text for those 56 briefs.
 
 ```{r}
-amicus_clean <- amicus %>% mutate(
+amicus <- amicus %>% mutate(
          txt_short = str_squish(txt_short),
          txt_short = case_when(
-           grepl("\\*1a appendix", txt_short) ~ 
-             gsub(pattern = "\\*1a appendix.*", replacement = "", x = txt_short),
+           grepl("\\*1a appendix|\\*ia appendix", txt_short, ignore.case = TRUE) ~ 
+             gsub(pattern = "\\*1a appendix.*|\\*ia appendix.*", replacement = "", x = txt_short,
+                  ignore.case = TRUE),
            T ~ txt_short),
@@
 
+Checking to make sure `*1A Appendix` references have been removed.
+
 ```{r}
-amicus_clean %>% filter(txt_short == "")
+a <- amicus %>%
+  mutate(appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix"))
+
+table(a$appendix_1a)
 ```
 
-## 3b. If 2) is false, further inspect the text (may require manual removal)
+## Handling APPENDIX A cases
 
-There were no documents that mentioned *1a appendix more than once so we can be confident that they were referring to the actual appendix.
-However, now there are 267 documents that contain `appendix` to deal with.
-Some of these include the documents above that already had the appendix remove so the real number of documents we need to remove is less if we just handle dealing with them in the same code chunk like lines 128-136.
+From some manual inspection, it looks like when `APPENDIX A` is mentioned in all caps that is it referring to the first section of the appendix.
+
+Let's see how many documents have `APPENDIX A` in them.
 
 ```{r}
-a_clean <- amicus_clean %>%
-  mutate(txt_short = str_squish(txt_short),
-    appendix = str_count(txt_short, "appendix"))
+amicus <- amicus %>% filter(appendix_1a == 0) %>%
+  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))
 
-table(a_clean$appendix)
+table(amicus$appendix_a)
 ```
 
-## 4. If it does not occur at all, check for the marker for footnotes (see next section).
+`APPENDIX A` occurs in 56 briefs that did not already have the appendix removed.
 
-When all text after the appendix is removed, this will include any footnotes as the appendix precedes the footnotes.
-We now only need to remove the footnotes from additional documents that did not have an appendix.
+We want to manually look at some of the briefs that mention `APPENDIX A` to make sure it really is at the beginning of the appendix.
 
 ```{r}
-a_f <- a %>% filter(appendix_1a == 0 & appendix == 0)
-
-table(a_f$footnotes)
+amicus %>% filter(appendix_a > 0) %>% select(id, appendix_a)
 ```
 
-There are 263 documents containing `footnotes` that don't mention `appendix`.
-
-I could not get your `get_context` code to work but I know from my previous research and some manual inspection that the following logic should work for removing footnotes.
-The footnotes are not referenced for the the footnotes section except to mention that something was omitted from the footnotes therefore removing or ignoring those instances, we can remove text after the first instance of the word `footnotes`.
-
-1. ignore/remove these instances:
-    * `footnotes omitted` or
-    * 3 words from omitted
-2. Use first finding of the word `footnotes` and remove text after that
-
-We can also use some of your logic instead. The code below is pretty much what we need, but need to combined with logic above to only perform this on documents that didn't have appendix.
+After checking 10 briefs that mention `APPENDIX A` once and the 1 brief that mentions it twice, all first instances refer to the beginning of the appendix.
+Therefore, we can remove all text after `APPENDIX A`.
 
 ```{r}
-#remove text with omitted within 3 words of footnotes
-amicus_clean <- amicus_clean %>% mutate(
+amicus <- amicus %>% mutate(
          txt_short = case_when(
-           grepl('(footnotes (\\w+\\s){0,3}omitted)|(omitted (\\w+\\s){0,3}footnotes)', txt_short) ~ 
-             gsub(pattern = '(footnotes (\\w+\\s){0,3}omitted)|(omitted (\\w+\\s){0,3}footnotes)',
-                  replacement = "", x = txt_short),
-           T ~ txt_short)
-          )
-
-#remove text after footnotes
-amicus_clean <- amicus_clean %>% mutate(
-         txt_short = str_squish(txt_short),
-         txt_short = case_when(
-           grepl("footnotes", txt_short) ~ 
-             gsub(pattern = "footnotes.*", replacement = "", x = txt_short),
+           appendix_1a == 0 &
+           grepl("APPENDIX A", txt_short) ~ 
+             gsub(pattern = "APPENDIX A.*", replacement = "", x = txt_short),
            T ~ txt_short),
@@
 
-## more exploration
-
-I wanted to look back at the full text before capitalization was removed becuase I noticed that many times an appendix might be referenced in text but when it is full caps like `APPENDIX` it references the actual appendix.
+Checking to make sure `APPENDIX A` references have been removed.
 
 ```{r}
-amicus_full <- box_read("863216279471")
+a <- amicus %>% filter(appendix_1a == 0) %>%
+  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))
+
+table(a$appendix_a)
 ```
 
+## Handling other forms of appendix
+
 ```{r}
-amicus_ends_full <- amicus_full %>%
-  mutate(txt_full = str_squish(txt_full),
-    appendix = str_count(txt_full, "APPENDIX"),
-         appendix_1a = str_count(txt_full, "\\*1A APPENDIX"))
+amicus <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>% 
+  mutate(appendix = str_count(txt_short, "APPENDIX"))
 
-a <- amicus_ends_full %>% select(case, brief, id, appendix, appendix_1a)
+table(amicus$appendix)
+```
+
+There are still 86 briefs that mention `APPENDIX`. We want to manually look at some of the briefs that mention `APPENDIX` to see if they refer to the beginning of the appendix
+
+```{r}
+amicus %>% filter(appendix > 1) %>% select(id, appendix)
+```
+
+I manually checked all briefs with more than one reference of `APPENDIX` and the first instance of each is referring to the beginning of the appendix and I also randomly checked many briefs with only 1 reference so we can remove all text after this.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           appendix_1a == 0 & appendix_a == 0 &
+           grepl("APPENDIX", txt_short) ~ 
+             gsub(pattern = "APPENDIX.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `APPENDIX` references have been removed.
+
+```{r}
+a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>%
+  mutate(appendix = str_count(txt_short, "APPENDIX"))
 
@@
 ```{r}
-table(a$appendix_1a)
+a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>%
+  mutate(Appendix = str_count(txt_short, "Appendix"),
+         appendix_all = str_count(txt_short, "appendix"))
+
+table(a$Appendix)
 ```
 
-Only 53 instances contain `*1A APPENDIX` while 202 contain the word `APPENDIX`.
-
-There were 55 that contained `*1a appendix` without caps so I think it would be good to ignore cases in this instance but `appendix` is mentioned in 295 docs so filtering down to the 202 with `APPENDIX` and handling the 93 remaining might be useful.
-I also didn't check for `Appendix` vs `appendix` but cases might help us narrow down here.
+There are 83 briefs remaining that mention `Appendix`.
 
 ```{r}
-amicus_lower <- amicus_full %>% mutate(txt_full = str_to_lower(txt_full))
+table(a$appendix_all)
+```
 
-amicus_lower_ends <- amicus_lower %>%
-  mutate(txt_full = str_squish(txt_full),
-    appendix = str_count(txt_full, "appendix"),
-         appendix_1a = str_count(txt_full, "\\*1a appendix"))
+There are 18 briefs remaining that mention `appendix`.
 
-a_lower <- amicus_lower_ends %>% select(case, brief, id, appendix, appendix_1a)
+In taking a further look at some of these briefs, there is not really a good pattern to remove the rest of the appendices at scale.
 
-table(a_lower$appendix)
+# Removing Footnotes
+
+First we want to convert all the text to lower case.
+
+```{r}
+amicus <- amicus %>% mutate(txt_short = str_to_lower(txt_short))
+```
+
+Now we want to check the mentions of `footnotes` in the briefs.
+
+```{r}
+amicus <- amicus %>%
+  mutate(footnotes = str_count(txt_short, "footnotes"))
+
+table(amicus$footnotes)
+```
+
+There are 345 briefs that mention footnotes.
+
+After manual inspection, we noticed many instances of footnotes that refer to the actual footnotes section are `footnotes counsel of record` and `footnotes 1`.
+We want to check their mentions in the briefs.
+
+```{r}
+amicus <- amicus %>%
+  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+         footnotes_1 = str_count(txt_short, "footnotes 1"))
+
+table(amicus$footnotes_cor)
 ```
@@
 ```{r}
-table(a_lower$appendix_1a)
+table(amicus$footnotes_1)
 ```
+
+We want to remove instance of `footnotes counsel of record` or `footnotes 1` that are in the list of footnotes ids.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           grepl("footnotes counsel of record", txt_short)
+           & (id %in% footnotes_ids$id) ~ 
+             gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
+           grepl("footnotes 1", txt_short)
+           & (id %in% footnotes_ids$id | id == '861814132010') ~ 
+             gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `footnotes counsel of record` and `footnotes 1` references have been removed.
+
+```{r}
+a <- amicus %>%
+  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+         footnotes_1 = str_count(txt_short, "footnotes 1"))
+
+table(a$footnotes_1)
+```
+
+```{r}
+table(a$footnotes_cor)
+```
+
+Now let's see how many remaining briefs mention footnotes.
+
+```{r}
+a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0) %>% 
+  mutate(footnotes = str_count(txt_short, "footnotes"))
+
+table(a$footnotes)
+```
+
+There are 149 briefs remaining that mention `footnotes`.

### 2022-01-25 data-cleaning/00-scrape-amicus-text.Rmd
add intro phrase checks

@@
 
+Check that our files contain "summary of (the) argument: this is the phrase that indicates the start of the text we want to analyze.
+
+```{r}
+amicus_txt %>% 
+  mutate(txt_full = str_squish(txt_full),
+         summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
+  group_by(summary) %>% 
+  summarize(n=n())
+```
+
+Which files do not? -- should just be the 3 that we have manual adjustments recorded for.
+
+```{r}
+amicus_txt %>% 
+  mutate(txt_full = str_squish(txt_full),
+         summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
+  filter(!summary) %>% 
+  select(brief)
+```
+
+Final column names
+
+```{r}
+amicus_txt %>% colnames()
+```
+
 # 3. Write file to Box
@@
 box_write(amicus_txt,
-          file_name = "shortened-amicus-brief-text.csv",
+          file_name = "raw-amicus-brief-text.csv",
           dir_id = '145990409196')

### 2022-01-26 data-cleaning/footnotes_appendix.Rmd
updated shortening text code #1

@@
                                      x = txt_full, ignore.case = TRUE),
-           #this line can be changed to T ~ '' once the raw brief file is updated
-           T ~ txt_full),
+           T ~ ''),
          txt_short = str_squish(txt_short))
@@
 Let's see how many documents have `APPENDIX A` in them.
-
 ```{r}
-amicus <- amicus %>% filter(appendix_1a == 0) %>%
-  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))
+amicus$appendix_a <- ifelse(amicus$appendix_1a < 1, str_count(amicus$txt_short, "APPENDIX A"), 0)
 
@@
 ```{r}
-amicus <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>% 
-  mutate(appendix = str_count(txt_short, "APPENDIX"))
+amicus$appendix <- ifelse(amicus$appendix_1a < 1 & amicus$appendix_a < 1, 
+                            str_count(amicus$txt_short, "APPENDIX"), 0)
 
@@
 
-There are 345 briefs that mention footnotes.
+There are 352 briefs that mention footnotes.
 
@@
 
+There also seems to be a pattern of `footnotes *` to reference the footnotes section. Let's see how many of this reference are in the briefs.
+
+```{r}
+amicus$footnotes_star <- ifelse(amicus$footnotes_cor < 1 & amicus$footnotes_1 < 1,
+                                str_count(amicus$txt_short, "footnotes \\*"), 0)
+
+table(amicus$footnotes_star)
+```
+
+There are 94 briefs that mention `footnotes *` where the footnotes have not yet been removed. We can remove all text after this string as well.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           grepl("footnotes \\*", txt_short) ~ 
+             gsub(pattern = "footnotes \\*.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `footnotes *` references have been removed.
+
+```{r}
+a <- amicus %>%
+  mutate(footnotes_star = str_count(txt_short, "footnotes \\*"))
+
+table(a$footnotes_star)
+```
+
 Now let's see how many remaining briefs mention footnotes.
@@
 ```{r}
-a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0) %>% 
+a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
+                        appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
   mutate(footnotes = str_count(txt_short, "footnotes"))
@@
 
-There are 149 briefs remaining that mention `footnotes`.
+There are 47 briefs remaining that mention `footnotes`.
+
+Now let's see how many remaining briefs mention appendices.
+
+```{r}
+a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
+   mutate(appendix_all = str_count(txt_short, "appendix"))
+
+table(a$appendix_all)
+```
+
+There are only 52 briefs remaining that mention an appendix that have not already had their appendix removed.
+
+Hoe many briefs had neither an appendix or footnotes removed?
+
+```{r}
+amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0 &
+                   footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0) %>% count()
+```
+253 briefs had neither an appendix or footnotes removed.
+
+Now we want to save the new shortened version of the text into a csv.
+
+```{r}
+#amicus <- amicus %>% select(case, brief, id, txt_short)
+
+#box_write(amicus,
+#          file_name = "shortened-amicus-brief-text.csv",
+#          dir_id = 145990409196)
+```

### 2022-01-26 data-cleaning/01-shorten-amicus-text.Rmd
footnotes confirmed file
updating file name

--- 2021-11-10 data-cleaning/01-shorten-amicus-text.Rmd
@@
 ---
-title: "Amicus Word Count"
-author: "Amanda Konet"
+title: "Shorten Amicus Text"
+author: "Sarah Torrence and Amanda Konet"
 date: "`r Sys.Date()`"
@@
 # data
-# data/processed amicus files/shortened-amicus-brief-text.csv
-amicus <- box_read("880862059511")
+# data/processed amicus files/raw-amicus-brief-text.csv
+amicus <- box_read("863216279471")
 # data/processed amicus files/amicus summary.xlsx
@@
 
-1) Remove text AFTER "Summary of Argument" keyword.
+1) Remove text BEFORE "Summary of Argument" keyword.
 
@@
 ```{r}
-alternate_rmv %>% select(id,alternative)
+#alternate_rmv %>% select(id,alternative)
 ```
-Shorten
+
+Remove text before summary of argument (already done in shortened-amicus-text csv, not raw text csv.)
 
@@
 amicus <- amicus %>%
-  mutate(txt_full = str_to_lower(txt_full),
-         txt_full = str_squish(txt_full),
+  mutate(txt_full = str_squish(txt_full),
          txt_short = case_when(
-           grepl("summary of argument", txt_full) ~ 
-             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
-           grepl("summary of the argument", txt_full) ~
-             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
-           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", x = txt_full),
-           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
-           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
-           T ~ ""),
+           id == 861820795454 ~ gsub(pattern = ".*summary \\[\\*9\\] of the argument", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           grepl("summary of argument|Summary of Argument|SUMMARY OF ARGUMENT", txt_full,
+                 ignore.case = TRUE) ~
+             gsub(pattern = ".*summary of argument|.*Summary of Argument|.*SUMMARY OF ARGUMENT",
+                  replacement = "",
+                  x = txt_full, ignore.case = TRUE),
+           grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
+             gsub(pattern = ".*summary of the argument", replacement = "",
+                  x = txt_full, ignore.case = TRUE),
+           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "",
+                                     x = txt_full, ignore.case = TRUE),
+           T ~ ''),
          txt_short = str_squish(txt_short))
@@
 
-# Remove text after "Appendix" or "Footnotes"
+# Removing Appendices
 
-Use footnotes when present. If not footnotes, use appendix. If neither: check. There are 154 docs with neither
+## Remove *1A Appendix
+
+Whenever `*1A Appendix` shows up in the text, this is referring to the start of the appendix. We want to remove all text after this phrase from the briefs that contain this phrase.
+
+### find instances of "*1A Appendix" in the text
 
 ```{r}
-amicus_ends <- amicus %>%
-  mutate(appendix = str_count(txt_short, "appendix"),
-         appendices = str_count(txt_short, "appendices"),
-         footnotes = str_count(txt_short, "footnotes"))
-
-amicus_ends <- amicus_ends %>% select(case, brief, id, appendix, footnotes)
-
-#box_write(amicus_ends,
-#          file_name = "amicus appendix and footnotes counts.csv",
-#          dir_id = 145990409196)
+amicus <- amicus %>%
+  mutate(txt_short = str_squish(txt_short),
+    appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix|\\*IA APPENDIX"))
 ```
 
-# Save
-
-Original text saved, just added new txt_short col
+Check that this only occurs 1x in a doc.
 
 ```{r}
-amicus <- amicus %>% select(-txt_full)
-amicus %>% colnames
+table(amicus$appendix_1a)
+```
+
+Since this phrase only occurs once in the briefs in which it is present, we can just remove all text after this text for those 56 briefs.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = str_squish(txt_short),
+         txt_short = case_when(
+           grepl("\\*1a appendix|\\*ia appendix", txt_short, ignore.case = TRUE) ~ 
+             gsub(pattern = "\\*1a appendix.*|\\*ia appendix.*", replacement = "", x = txt_short,
+                  ignore.case = TRUE),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `*1A Appendix` references have been removed.
+
+```{r}
+a <- amicus %>%
+  mutate(appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix"))
+
+table(a$appendix_1a)
+```
+
+## Handling APPENDIX A cases
+
+From some manual inspection, it looks like when `APPENDIX A` is mentioned in all caps that is it referring to the first section of the appendix.
+
+Let's see how many documents have `APPENDIX A` in them.
+```{r}
+amicus$appendix_a <- ifelse(amicus$appendix_1a < 1, str_count(amicus$txt_short, "APPENDIX A"), 0)
+
+table(amicus$appendix_a)
+```
+
+`APPENDIX A` occurs in 56 briefs that did not already have the appendix removed.
+
+We want to manually look at some of the briefs that mention `APPENDIX A` to make sure it really is at the beginning of the appendix.
+
+```{r}
+amicus %>% filter(appendix_a > 0) %>% select(id, appendix_a)
+```
+
+After checking 10 briefs that mention `APPENDIX A` once and the 1 brief that mentions it twice, all first instances refer to the beginning of the appendix.
+Therefore, we can remove all text after `APPENDIX A`.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           appendix_1a == 0 &
+           grepl("APPENDIX A", txt_short) ~ 
+             gsub(pattern = "APPENDIX A.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `APPENDIX A` references have been removed.
+
+```{r}
+a <- amicus %>% filter(appendix_1a == 0) %>%
+  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))
+
+table(a$appendix_a)
+```
+
+## Handling other forms of appendix
+
+```{r}
+amicus$appendix <- ifelse(amicus$appendix_1a < 1 & amicus$appendix_a < 1, 
+                            str_count(amicus$txt_short, "APPENDIX"), 0)
+
+table(amicus$appendix)
+```
+
+There are still 86 briefs that mention `APPENDIX`. We want to manually look at some of the briefs that mention `APPENDIX` to see if they refer to the beginning of the appendix
+
+```{r}
+amicus %>% filter(appendix > 1) %>% select(id, appendix)
+```
+
+I manually checked all briefs with more than one reference of `APPENDIX` and the first instance of each is referring to the beginning of the appendix and I also randomly checked many briefs with only 1 reference so we can remove all text after this.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           appendix_1a == 0 & appendix_a == 0 &
+           grepl("APPENDIX", txt_short) ~ 
+             gsub(pattern = "APPENDIX.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `APPENDIX` references have been removed.
+
+```{r}
+a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>%
+  mutate(appendix = str_count(txt_short, "APPENDIX"))
+
+table(a$appendix)
 ```
@@
 ```{r}
-box_write(amicus,
-          file_name = "shortened-amicus-brief-text.csv",
-          dir_id = 145990409196)
+a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>%
+  mutate(Appendix = str_count(txt_short, "Appendix"),
+         appendix_all = str_count(txt_short, "appendix"))
+
+table(a$Appendix)
 ```
+
+There are 83 briefs remaining that mention `Appendix`.
+
+```{r}
+table(a$appendix_all)
+```
+
+There are 18 briefs remaining that mention `appendix`.
+
+In taking a further look at some of these briefs, there is not really a good pattern to remove the rest of the appendices at scale.
+
+# Removing Footnotes
+
+First we want to convert all the text to lower case.
+
+```{r}
+amicus <- amicus %>% mutate(txt_short = str_to_lower(txt_short))
+```
+
+Now we want to check the mentions of `footnotes` in the briefs.
+
+```{r}
+amicus <- amicus %>%
+  mutate(footnotes = str_count(txt_short, "footnotes"))
+
+table(amicus$footnotes)
+```
+
+There are 352 briefs that mention footnotes.
+
+After manual inspection, we noticed many instances of footnotes that refer to the actual footnotes section are `footnotes counsel of record` and `footnotes 1`.
+We want to check their mentions in the briefs.
+
+```{r}
+amicus <- amicus %>%
+  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+         footnotes_1 = str_count(txt_short, "footnotes 1"))
+
+table(amicus$footnotes_cor)
+```
+
+```{r}
+table(amicus$footnotes_1)
+```
+
+We want to remove instance of `footnotes counsel of record` or `footnotes 1` that are in the list of footnotes ids.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           grepl("footnotes counsel of record", txt_short)
+           & (id %in% footnotes_ids$id) ~ 
+             gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
+           grepl("footnotes 1", txt_short)
+           & (id %in% footnotes_ids$id | id == '861814132010') ~ 
+             gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `footnotes counsel of record` and `footnotes 1` references have been removed.
+
+```{r}
+a <- amicus %>%
+  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+         footnotes_1 = str_count(txt_short, "footnotes 1"))
+
+table(a$footnotes_1)
+```
+
+```{r}
+table(a$footnotes_cor)
+```
+
+There also seems to be a pattern of `footnotes *` to reference the footnotes section. Let's see how many of this reference are in the briefs.
+
+```{r}
+amicus$footnotes_star <- ifelse(amicus$footnotes_cor < 1 & amicus$footnotes_1 < 1,
+                                str_count(amicus$txt_short, "footnotes \\*"), 0)
+
+table(amicus$footnotes_star)
+```
+
+There are 94 briefs that mention `footnotes *` where the footnotes have not yet been removed. We can remove all text after this string as well.
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           grepl("footnotes \\*", txt_short) ~ 
+             gsub(pattern = "footnotes \\*.*", replacement = "", x = txt_short),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure `footnotes *` references have been removed.
+
+```{r}
+a <- amicus %>%
+  mutate(footnotes_star = str_count(txt_short, "footnotes \\*"))
+
+table(a$footnotes_star)
+```
+
+Now let's see how many remaining briefs mention footnotes.
+
+```{r}
+a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
+                        appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
+  mutate(footnotes = str_count(txt_short, "footnotes"))
+
+table(a$footnotes)
+```
+
+There are 47 briefs remaining that mention `footnotes`.
+
+Now let's see how many remaining briefs mention appendices.
+
+```{r}
+a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
+   mutate(appendix_all = str_count(txt_short, "appendix"))
+
+table(a$appendix_all)
+```
+
+There are only 52 briefs remaining that mention an appendix that have not already had their appendix removed.
+
+Hoe many briefs had neither an appendix or footnotes removed?
+
+```{r}
+amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0 &
+                   footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0) %>% count()
+```
+253 briefs had neither an appendix or footnotes removed.
+
+Now we want to save the new shortened version of the text into a csv.
+
+```{r}
+#amicus <- amicus %>% select(case, brief, id, txt_short)
+
+#box_write(amicus,
+#          file_name = "shortened-amicus-brief-text.csv",
+#          dir_id = 145990409196)
+```

### 2022-01-26 data-cleaning/01-shorten-amicus-text.Rmd
identified ids where no text removed close #1

@@
 
+```{r}
+#saving these ids to a csv
+footnotes_not_removed <- a %>% filter(footnotes > 0) %>% select(id)
+
+#box_write(footnotes_not_removed,
+#          file_name = "footnotes-not-removed.csv",
+#          dir_id = 145990409196)
+```
+
 Now let's see how many remaining briefs mention appendices.
@@
 
-There are only 52 briefs remaining that mention an appendix that have not already had their appendix removed.
+There are only 62 briefs remaining that mention an appendix that have not already had their appendix removed.
+
+```{r}
+#saving these ids to a csv
+appendix_not_removed <- a %>% filter(appendix_all > 0) %>% select(id)
+
+#box_write(appendix_not_removed,
+#          file_name = "appendix-not-removed.csv",
+#          dir_id = 145990409196)
+```
 

### 2022-02-06 data-cleaning/01-shorten-amicus-text.Rmd
finished final footnote/app removal, close #9

@@
 
+We manually went in and added the string "mnopqrst" to all briefs in which 'footnotes' and/or 'appendix' was found but not removed.
+We can now removed all text after this random string.
+There are two exceptions below that due to being pdfs that we could not edit, we will handle separately.
+
+Case | Brief Name | ID | Text 
+-- | -- | -- | --
+WWH v Hellerstedt | Whole Women's Health v Hellerstedt.
+Amicus brief for Respondents by Physicians with Experience Treating Women in Rural or Emergency Settings.pdf | 861822669887 | Listing of Amici Physicians with Experience Treating Women in Rural or Emergency Settings
+WWH v Hellerstedt | Whole Women's Health v Hellerstedt. Amicus brief for Respondents by Right to Life Advocates, Inc.pdf | 861824109102 | App. 1
+
+```{r}
+counts <- amicus %>%
+  mutate(manual = str_count(txt_short, 'mnopqrst'))
+
+table(counts$manual)
+```
+
+```{r}
+amicus <- amicus %>% mutate(
+         txt_short = case_when(
+           grepl("mnopqrst", txt_short) ~ 
+             gsub(pattern = "mnopqrst.*", replacement = "", x = txt_short),
+           id == 861822669887 ~ gsub(pattern = "a-1 appendix.*", 
+                    replacement = "", x = txt_short, ignore.case = TRUE),
+           id == 861824109102 ~ gsub(pattern = "App. 1.*", 
+                    replacement = "", x = txt_short, ignore.case = TRUE),
+           T ~ txt_short),
+         txt_short = str_squish(txt_short))
+```
+
+Checking to make sure we did removed this text:
+
+```{r}
+counts <- amicus %>%
+  mutate(manual = str_count(txt_short, 'mnopqrst'))
+
+table(counts$manual)
+```
+
+```{r}
+#amicus %>% filter(id == 861822669887) %>% pull(txt_short)
+```
+
 Now we want to save the new shortened version of the text into a csv.
@@
 ```{r}
-#amicus <- amicus %>% select(case, brief, id, txt_short)
-
-#box_write(amicus,
+# amicus <- amicus %>% select(case, brief, id, txt_short)
+# 
+# box_write(amicus,
 #           file_name = "shortened-amicus-brief-text.csv",

### 2022-02-13 eda/calculate_label_density.Rmd
code for #10

---
title: "Create Label Density"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

The purpose of this script is to find briefs with high label density based on words and phrases that are used frequently in feminist and opposition frames, or arguments. We will do this through a dictionary of frames and the words/phrases associated with those frames in which we will search for these terms within each chunk of text from briefs. Label density will be defined as the total number of times terms associated with each frame is used within the chunk of text.

The end goal is to find the top 5 text chunks with the highest label density for each frame.

## Load Packages

```{r include=FALSE}
# Load packages 
library(boxr) # accessing box API
library(tidyverse) # reading data
library(quanteda) # text mining
box_auth()
```

## Load Data

```{r}
amicus_chunks <- box_read("915435467229")
frames <- box_read("914901620274")
```

## Create Dictionary

We are only focusing on the following frames so I will filter out the rest.

* feminist briefs ("fem" in brief title): 
    + undue burden (law_undueBurdenII)
    + women's rights (law_womanRights)
    + women's citizenship (womanCitizenship)
    + compulsory motherhood (compulsoryMotherhood)
* opposition briefs: 
    + morality (morality)
    + abortion negative (abortionNegativeII)
    + psychological harm (psy_harm)
    + fetus (actor_fetus)
* both types: 
    + evidence (evidence_combine)
    + health (health)

We want to separate these into a fem dictionary and opp dictionary as we only want to search for fem terms in fem briefs and opp terms in opp briefs. We will include `evidence_combine` and `health` in both dictionaries as we want to search for related terms in both fem and opp briefs.

```{r}
#frames to keep
fem_frames <- c('law_undueBurdenII', 'law_womanRights', 'womanCitizenship', 'compulsoryMotherhood', 'evidence_combine', 'health')

opp_frames <- c('morality', 'abortionNegativeII', 'psy_harm', 'actor_fetus', 'evidence_combine', 'health')

#filter for only these frames
fem_df <- frames %>% filter(code %in% fem_frames) %>% select(code, word_cleaned) %>% unique()

opp_df <- frames %>% filter(code %in% opp_frames) %>% select(code, word_cleaned) %>% unique()
```

Here are a couple functions we will use to create dictionaries with frames as keys and associated terms as values.

```{r}
# Get terms associated with each frames
getFrames <- function(frame){ 
  frames %>%
    filter(code == frame) %>%
    select(word_cleaned)
    }

#create dictionary
create_dict <- function(frame_df){

    # Initialize list
    searchFrames <- list()

    # Get unique frames
    frames <- unique(frame_df$code)

    # Pull words for each frame and save in list
    for(i in 1:length(frames)){ 
      searchFrames[i] <- getFrames(frames[i])
    }

    # Name items in list
    names(searchFrames) <- frames

    frameDict <- dictionary(searchFrames)
    return(frameDict)
}
```

Using the above functions to create a fem and opp dictionary.

```{r}
fem_dict <- create_dict(fem_df)
opp_dict <- create_dict(opp_df)
```

## Create Corpus

Now that we have dictionaries of search terms, we need to create a corpus to search through for fem and opp.

```{r}
#function to create a corpus
create_corpus <- function(df){

    brief_corp <- df$text %>%
      corpus()

    # Add meta data to corpus
    docvars(brief_corp, "brief_v1") <- df$V1 
    docvars(brief_corp, "brief_case") <- df$case
    docvars(brief_corp, "brief_id") <- df$id
    docvars(brief_corp, "brief_name") <- df$brief

    # Name documents in corpus
    docnames(brief_corp) <- df$V1
    return(brief_corp)
}

#creating the fem and opp corpus
fem_chunks <- amicus_chunks %>% filter(fem_brief == 1)
fem_corp <- create_corpus(fem_chunks)

opp_chunks <- amicus_chunks %>% filter(fem_brief == 0)
opp_corp <- create_corpus(opp_chunks)
```

Now we can tokenize each corpus. Removing punctuation and numbers will increase the number of term counts (something Amanda previously discovered).

```{r}
# Tokenize brief chunks
fem_toks <- tokens(fem_corp, remove_punct = TRUE, remove_numbers = TRUE)
opp_toks <- tokens(opp_corp, remove_punct = TRUE, remove_numbers = TRUE)
```

Here we can create a summary data frame of each chunk where we will add the frequency of each frame to later.

```{r}
create_summary <- function(corp, chunks){
    # Generate summary of corpus
    corp_summary <- summary(object = corp, 
                          n = nrow(chunks), # default is 100, we need all observations 
                          showmeta = TRUE) %>% # add meta data to summary
      as.data.frame()
    return(corp_summary)
}

#creating summary for fem and opp
fem_summary <- create_summary(fem_corp, fem_chunks)
opp_summary <- create_summary(opp_corp, opp_chunks)
```

## Generate Frame Frequencies

Now we can use the dictionary and tokens to find the frequency of each frame within each chunk of text and add all this information together with the summary information above in a clean data frame.

```{r}
#get the frequency of each frame and add to summary data frame
get_freqs <- function(tokens, dict, summary_df){
        #searching chunks for frames
        df <- tokens_lookup(tokens, dictionary = dict, nested_scope = "dictionary",
                              case_insensitive = FALSE, valuetype = "fixed") %>% dfm()

        #creating data frame of summary info and frequencies
        df <- df %>% convert(to = "data.frame") %>% 
            rename(brief_v1 = doc_id) %>% 
            left_join(summary_df, by = "brief_v1") %>% 
            select(-Text, -Types, -Tokens, -Sentences)
        return(df)
}

#convert v1 to character for joining purposes
fem_summary$brief_v1 <- as.character(fem_summary$brief_v1)
opp_summary$brief_v1 <- as.character(opp_summary$brief_v1)

#call frequency function on fem and opp
fem <- get_freqs(fem_toks, fem_dict, fem_summary)
opp <- get_freqs(opp_toks, opp_dict, opp_summary)
```

The final step is to add back fem and opp into one large data frame with all chunks of text and label density.

```{r}
df_frames_freq <- bind_rows(fem, opp)

amicus_chunks$V1 <- as.character(amicus_chunks$V1)

df_frames_freq <- df_frames_freq %>% left_join(amicus_chunks, by = c('brief_v1' = 'V1')) %>% 
    select(V1 = brief_v1, case, brief_name, id, fem_brief, text, compulsorymotherhood, evidence_combine, health, law_undueburdenii, law_womanrights, womancitizenship, abortionnegativeii, actor_fetus, morality, psy_harm)
```

We also want a boolean value of whether a frame was used at all in each chunk. If a frame was used we will encode a value of 1, if not, a value of 0.

```{r}
create_bool <- function(df, variables){
    for (var in variables){
        df[paste0(var,'_bool')] <- ifelse(df[var] > 0, 1, 0)
    }
    return(df)
}

v <- c('compulsorymotherhood', 'evidence_combine', 'health', 'law_undueburdenii',
       'law_womanrights', 'womancitizenship', 'abortionnegativeii', 'actor_fetus', 
       'morality', 'psy_harm')
df_frames_freq <- create_bool(df_frames_freq, v)
```

## Saving results

```{r}
box_write(df_frames_freq, dir_id = "154895322313", "amicus_chunks_frames_density.csv") 
```

# Finding High Label Density Chunks

Now we can find the top 5 chunks with the highest label density for each of the frames. If

```{r}
#create data frame with 0 rows and 26 columns
df <- data.frame(matrix(ncol = 26, nrow = 0))

#provide column names
colnames(df) <- c("V1","case","brief_name","id","fem_brief","text","compulsorymotherhood",
                  "evidence_combine","health","law_undueburdenii","law_womanrights",
                  "womancitizenship","abortionnegativeii","actor_fetus","morality",
                  "psy_harm","compulsorymotherhood_bool", "evidence_combine_bool",
                  "health_bool","law_undueburdenii_bool", "law_womanrights_bool",
                  "womancitizenship_bool", "abortionnegativeii_bool", "actor_fetus_bool",
                  "morality_bool","psy_harm_bool")

df_na <- df_frames_freq
df_na[is.na(df_na)] <- 0
for (var in v){
    x <- tail(df_na[order(df_na[var]),var],5) %>% unique
    for (i in 1:length(x)){
        y <- df_frames_freq[df_frames_freq[var] == x[i],]
        df <- rbind(df, y)
    }
}

df <- df %>% unique()
```

## Save the Results

```{r}
box_write(df, dir_id = "154895322313", "highest_label_density_chunks.csv")
```

### 2022-02-14 reference-files/search-briefs.Rmd
rename

---
title: "Amicus II: Searching briefs"
output: html_document
---

# Load packages

```{r include=FALSE}
# Load packages 
library(boxr) # accessing box API
library(tidyverse) # reading data
library(quanteda) # text mining
box_auth()
```

# Load Data 
```{r}
briefTextDF <- read_csv("../-processed-data/stop_words_removed/a2-step-2-preprocess-data-brief-text-cleaned.csv")
searchTerms <- read_csv("../-processed-data/stop_words_removed/a2-step-2-preprocess-search-terms-cleaned.csv")
```

# Duplicate Brief

Filter out duplicate June v. Russo Briefs

```{r}
briefTextDF <- briefTextDF %>% 
  filter(!grepl("2,556", ignore.case = T, brief_name))
```

Ensure incorrect use of fact(s), report(s/ing/ed)

```{r}
briefTextDF <- briefTextDF %>%
  mutate(
    brief_text_clean = case_when(
      brief_case_clean == "City of Akron v Akron Center for Rep Health" ~ gsub(
        pattern = " fact | fact\"|\"fact\"|facts",
        replacement = "",
        x = brief_text_clean,
        ignore.case = T
      ),
      brief_case_clean %in% c(
        "Planned Parenthood v Ashcroft",
        "Thornburgh v American Council of OBGYNs"
      ) ~
        gsub(
          pattern = "report|reports|reporting|reported",
          replacement = "",
          x = brief_text_clean,
          ignore.case = T
        ),
      TRUE ~ brief_text_clean
    )
  )
```

# Tokenizing and weighting terms

## Create corpus

In order to generate the frame frequencies, we'll begin by creating a corpus, `amicusCorp`. The corpus is like a file cabinent - it contains all of the texts in our dataset. The one we're creating below contains the preprocessed amicus brief text, `briefTextDF$brief_text_clean`.

Just like when you file away documents in real life, it's important to label items so that you can easily group and categorize them during your analysis. In text mining, these labels/variables are referred to as **meta data**. We'll label the texts in our corpus using the `docvars()` and `docnames()` functions.

Another way to understand how these functions work is imagining that we're moving all of the important variables in our original data frame, `briefTextDF`, to the corpus, `briefCorp`.

```{r}
brief_corp <- briefTextDF$brief_text_clean %>%
  corpus()

# Add meta data to corpus
docvars(brief_corp, "brief_case") <- briefTextDF$brief_case_clean # case name cleaned
docvars(brief_corp, "brief_name") <- briefTextDF$brief_name # brief
docvars(brief_corp, "brief_id") <- briefTextDF$brief_id # file id
docvars(brief_corp, "brief_type") <- briefTextDF$brief_type # party vs amicus
docvars(brief_corp, "brief_party") <- ifelse(briefTextDF$brief_fem == TRUE, "fem", "opp") # feminist or opponent

# Name documents in corpus
docnames(brief_corp) <- briefTextDF$brief_name

summary(brief_corp) %>% head()
```

## Create frame dictionary

This dictionary will be used to filter out frame words from paragraphs when counting word frequency.

```{r}
# Remove duplicates
searchTerms <- searchTerms %>%
  mutate(word = word_cleaned) %>%
  select(abb, word) %>%
  unique()

# Get words associated with frames
getFrames <- function(frame){ 
  searchTerms %>%
    filter(abb == frame) %>%
    select(word)
  }

# Initialize list
searchFrames <- list()

# Get unique frames
frames <- unique(searchTerms$abb)

# Pull words for each frame and save in list
for(i in 1:length(frames)){ 
  searchFrames[i] <- getFrames(frames[i])
}

# Name items in list
names(searchFrames) <- frames

frameDict <- dictionary(searchFrames)

# Check output
frameDict
```

# Look up frames

**Note on arguments in `tokens()` function**: removing punctuation and numbers from terms increases counts. See `amicus-exploring-counting-frames` script to go over evidence.

```{r}
# Tokenize briefs
toks <- tokens(brief_corp, remove_punct = TRUE, remove_numbers = TRUE)
```

## Create brief summary statistics

The `brief_corp_summary` data frame contains the summary statistics of all the briefs in our corpus, `brief_corp`. The one thing it's missing is the number of tokens (i.e. words) in each brief.

The `summary()` function takes 3 arguments:

* **object**: the corpus object (`brief_corp`)
* **n**: the number of observations; the default is 100, but since we want the summary for all of the texts in our corpus, we'll set the value to `nrow(briefTextDF)` since the number of rows (calculated using the function `nrow()`) in the `briefTextDF` is equal to the total number of observations (i.e. briefs) in our corpus.
* **showmeta**: we'll set this value equal to TRUE in order to include the metadata we created earlier.

You'll notice that the `brief_corp` data frame has a column `Tokens` - it's the number of tokens (i.e. words) **before** removing punctuation and digits from the briefs. We'll compare these values to the values we create in the `word_ct` column in a few.

```{r}
# Generate summary of amicusCorp
brief_corp_summary <- summary(object = brief_corp, 
                      n = nrow(briefTextDF), # default is 100, we need all observations 
                      showmeta = TRUE) %>% # add meta data to summary
  as.data.frame()

# Look at first 6 observations 
tail(brief_corp_summary)
```

Now it's time to find out how many words are in the briefs after we tokenize them and remove the punctuation and digits. We can do this by using the `ntokens()` function - this function gets the counts of tokens (total words/features) in our `toks` object.

The `nToks` data frame contains to columns: 
* **brief_name**: the name of the brief associated with the `ntoken(toks)` object (i.e. value in `brief_n_words`); this column allows us to join the data frame with the `amicusCorpSummary` data frame. 
* **brief_n_words**: the number of tokens (i.e. words) in each brief **after** removing the punctuation and digits from the briefs.

We'll join this information to `amicusCorpSummary` to create the data frame `briefInfo`.

```{r}
# Total number of tokens (before pulling frame words)
nToks <- data.frame(brief_name = names(ntoken(toks)), 
                     word_ct = ntoken(toks))

# Look at first 6 observations
head(nToks)
```

```{r}
brief_info <- brief_corp_summary %>%
  left_join(nToks, by = c("brief_name")) %>%
  select(brief_case, brief_name, brief_party, brief_type, word_ct, brief_id)

head(brief_info)
```

### OPTIONAL: Comparing word count before/after tokenizing briefs

We can compare the word count before removing the puncutation and digits to the word count after removing the puncutation and digits by running the code chunk below.

```{r}
# Compare word counts
# compare_brief_n_words <- amicusCorpSummary %>%
#  select(brief_name, 
#         brief_n_words_raw = Tokens) %>% # number of tokens before removing punctuation and digits 
#  left_join(nToks, by = c("brief_name")) %>% 
#  select(brief_name, brief_n_words_raw, brief_n_words) %>%
#  mutate(same_number = brief_n_words == brief_n_words_raw) # are word counts the same
```

If the value in the column `same_number` is TRUE, then the brief word count did not change after removing the punctuation and digits. 
If the value in the column `same_number` is FALSE, then the brief word count changed (it decreased) after removing the punctuation and digits.

We can use the `count(same_number)` to count the number of observations that are TRUE and FALSE in the `same_number` column, and based on the output, all 670 word counts changed after removing the punctuation and digits.

```{r}
# Did any word counts stay the same? Nope
# compare_brief_n_words %>%
#   count(same_number)
```

Taking it one more step, we can look at how the word count values changed - we'd expect them to decrease after removing the puncutation and digits, but let's double check by running one more test:

```{r}
# Did any word counts increase after removing punctuation and digits? Nope (whew!)
# compare_brief_n_words %>%
#   mutate(greater_number = brief_n_words > brief_n_words_raw) %>% 
#   filter(greater_number == TRUE)
```

## Generate frame frequencies

Now that we've created our `brief_info` data frame, it's time to generate the frame frequencies and attach the data frames together.

The `brief_frames_raw` data frame contains the raw frame frequencies joined with the `brief_info` data frame. The resulting dataframe of this step will be one row per case per frame, with a column for the count of that frame. This will make it very easy to generate the frame frequencies per Holly's specifications, which is:

(# of words/phrases for a particular frame) / (# of all words in the brief)

```{r}
# Search for frames
brief_dfm <- tokens_lookup(toks, dictionary = frameDict, nested_scope = "dictionary", case_insensitive = FALSE, valuetype = "fixed") %>%
  dfm()

# Generate raw frequencies
brief_frames_raw <- brief_dfm %>%
  convert(to = "data.frame") %>%
  rename(brief_name = doc_id) %>%
  left_join(brief_info, by = "brief_name") %>% # join with brief_info
  # remove "purpose of performance" counts from "purpose" counts
  mutate(p_new = p - pop) %>% 
  select(brief_case, brief_id, brief_name, brief_type, brief_party, word_ct, an:wc)

# Check out first 6 observations 
head(brief_frames_raw, 10)
```
**Update 4/22/21**: Remove instances of word usage from the evidence experts frame that we don't want to count.

For Thornburgh, remove counts of the words "fact(s)" and "evidence" from the opponent/antiabortion party brief. Per github issue #92, 6+14 instances of the eeII frame must be subtracted

```{r}
brief_frames_raw <- brief_frames_raw %>%
  mutate(eeii = ifelse(
    grepl("Thornburgh", brief_case) &
      brief_type == "Party" & brief_party == "opp",
    eeii - (6 + 14),
    eeii
  ))

#brief_frames_raw %>%
#  filter(grepl("Thornburgh", brief_case), brief_type == "Party", brief_party == "opp") %>% 
#  select(brief_case, brief_type, brief_party, eeii)
```

For City of Akron, remove the counts of "fact" from select amicus (opp + fem briefs) found in step 3b.

```{r}
akron_cases <- c("City of Akron v Akron Center for Rep Health. Amici Brief for Petitioner, by United Families Foundation and Women Exploited.docx", "City of Akron v Akron Center for Rep Health. Amici Brief for Respondent (feminist), by American College of OBGYNs et al.docx", "City of Akron v Akron Center for Rep Health. Amici Brief for Respondent (feminist), by Planned Parenthood Federation of America et al.docx", "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Catholic League for Religious and Civil Rights.docx", "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Feminists for Life.docx", "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Legal Defense Fund for Unborn Children.docx", "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Womenkind, Inc.docx", "City of Akron v Akron Center for Rep Health. Amicus Brief for Respondent (feminist), by Certain Religious Organizations.docx", "City of Akron v Akron Center for Rep Health. Amicus Brief for Respondent (feminist), by the American Public Health Association.docx")

#brief_frames_raw %>% 
#  filter(brief_name %in% akron_cases) %>% 
#  select(brief_name, eeii)

brief_frames_raw <- brief_frames_raw %>% 
  mutate(eeii = case_when(
    brief_name == "City of Akron v Akron Center for Rep Health. Amici Brief for Petitioner, by United Families Foundation and Women Exploited.docx" ~ eeii - 1,
    brief_name == "City of Akron v Akron Center for Rep Health. Amici Brief for Respondent (feminist), by American College of OBGYNs et al.docx" ~ eeii - 2,
    brief_name == "City of Akron v Akron Center for Rep Health. Amici Brief for Respondent (feminist), by Planned Parenthood Federation of America et al.docx" ~ eeii - 2,
    brief_name == "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Catholic League for Religious and Civil Rights.docx" ~ eeii - 2,
    brief_name == "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Feminists for Life.docx" ~ eeii - 2,
    brief_name == "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Legal Defense Fund for Unborn Children.docx" ~ eeii - 6,
    brief_name == "City of Akron v Akron Center for Rep Health. Amicus Brief for Petitioner, by Womenkind, Inc.docx" ~ eeii - 1,
    brief_name == "City of Akron v Akron Center for Rep Health. Amicus Brief for Respondent (feminist), by Certain Religious Organizations.docx" ~ eeii - 1,
    brief_name == "City of Akron v Akron Center for Rep Health. Amicus Brief for Respondent (feminist), by the American Public Health Association.docx" ~ eeii - 1,
    T ~ eeii
  ))
```

Get frame frequencies

```{r}
# Generate frame frequencies 
brief_frames_freq <- brief_frames_raw %>% 
  pivot_longer(c(an:wc), names_to = "frame", values_to = "frame_ct") %>% 
  mutate(frame_freq = frame_ct/word_ct) %>% 
  select(-frame_ct) %>% 
  pivot_wider(names_from = "frame", values_from = frame_freq)

brief_frames_freq %>% head(10)
```

## Raw counts + freq

Dataframe with raw counts and frequencies

```{r}
brief_frames <- brief_frames_raw %>% 
  left_join(., brief_frames_freq, 
            by = c("brief_case", "brief_id", "brief_name", "brief_type", "brief_party", "word_ct"), 
            suffix = c("_raw", "_freq")) %>% 
  select(brief_case:word_ct, sort(colnames(.)))

brief_frames %>% head(10)
```

Summary by case

```{r}
# Total word count of briefs by case
brief_frames %>%
  group_by(brief_case) %>%
  summarise(total_brief_words = sum(word_ct)) 
```

## Save results

```{r}
# Save files
write_csv(brief_frames_raw, "../-processed-data/stop_words_removed/a2-step-3-search-briefs-raw-freq.csv")
write_csv(brief_frames_freq,"../-processed-data/stop_words_removed/a2-step-3-search-briefs-ter-freq.csv")
write_csv(brief_frames, "../-processed-data/stop_words_removed/a2-step-3-search-briefs-full-freq.csv")

# all stops removed folder
#box_write(brief_frames, dir_id = "126163615802", "search-briefs-full-freq.csv")

# group a stops folder
box_write(brief_frames, dir_id = "126482779345", "search-briefs-full-freq.csv")

rm(list = ls())
```

### 2022-02-14 reference-files/bert_extras.py

@@ -1,0 +1,16 @@
+# pretrained model
+bert = AutoModel.from_pretrained('bert-base-uncased')
+
+# associated tokenizer
+tokenizer = AutoTokenizer.from_pretrained('bert-base-cased')
+
+# batch_sentences is a list
+batch = tokenizer(batch_list[0], padding=True, truncation=True, return_tensors="pt")
+print(batch)
+
+from transformers import BertTokenizer, BertModel
+tokenizer = BertTokenizer.from_pretrained('bert-base-uncased')
+model = BertModel.from_pretrained("bert-base-uncased")
+text = "Replace me by any text you'd like."
+encoded_input = tokenizer(text, return_tensors='pt')
+output = model(**encoded_input)

### 2022-02-15 eda/calculate_label_density.Rmd
updated descriptions
sorting out labeled amicus file

@@
 
-Now we can find the top 5 chunks with the highest label density for each of the frames. If
+Now we can find the top 5 chunks with the highest label density for each of the frames. If there are more than 5 chunks with the highest label density, then all are added to the final data frame.
 
@@
 ```{r}
-box_write(df, dir_id = "154895322313", "highest_label_density_chunks.csv")
+#box_write(df, dir_id = "154895322313", "highest_label_density_chunks.csv")
 ```
+
+# Label Distribution in Manually Labeled Dataset
+
+Read in labeled dataset
+
+```{r}
+labeled_amicus <- box_read("913003480881") %>% 
+  janitor::clean_names()
+```
+
+## Distribution
+
+Get an idea of the distribution of labels that exist in current dataset
+
+```{r}
+labeled_amicus %>%
+  separate_rows(., hm_label_code_s, sep = "; ", convert = FALSE) %>% 
+  select(case, text, hm_label_code_s) %>% 
+  group_by(hm_label_code_s) %>% 
+  summarize(n=n()) %>% arrange(-n)
+```
+
+## Extract text and "true" labels
+
+Note that some of the texts were split in half in order to avoid going over token limit of transformers.
+These are denoted as "top" or "bottom" and we can get that split by getting the len of each text and taking the first or second half.
+In cases where the split is not in half, the top or bottom text have been entered.
+
+```{r}
+labeled_amicus <- labeled_amicus %>% 
+  mutate(manual_divide = ifelse(!is.na(divided_1) | !is.na(divided_2), 1, 0))
+
+# d1
+d1_am <- labeled_amicus %>% filter(!is.na(divided_1)) %>% 
+  select(case:fem, -text, divided_1,d1_label_code) %>% 
+  rename(text = divided_1,label = d1_label_code)
+```
+
+```{r}
+labeled_amicus %>% 
+  filter(!is.na(divided_2) & !is.na(divided_1))
+```

### 2022-02-16 eda/calculate_label_density.Rmd
clean up HM labeled amicus file

@@
 ```{r}
+# rmv texts w/o labels & indicate which texts were manually split
 labeled_amicus <- labeled_amicus %>% 
-  mutate(manual_divide = ifelse(!is.na(divided_1) | !is.na(divided_2), 1, 0))
+  mutate(manual_divide = ifelse(!is.na(divided_1) | !is.na(divided_2), 1, 0)) %>% 
+  filter(hm_label_code_s != "no labels") %>% 
+  mutate(divided_1 = ifelse(id == 861816856607, text, divided_1))
 
-# d1
-d1_am <- labeled_amicus %>% filter(!is.na(divided_1)) %>% 
-  select(case:fem, -text, divided_1,d1_label_code) %>% 
-  rename(text = divided_1,label = d1_label_code)
+top <- labeled_amicus %>% 
+  filter(excerpt_divided_if_yes_top_or_bottom_coded %in% c("top", "all(short)")) %>% 
+  select(case:fem, -text, text = divided_1, hm_label_code_s)
+
+bottom <- labeled_amicus %>% 
+  filter(excerpt_divided_if_yes_top_or_bottom_coded == "bottom") %>% 
+  select(case:fem, -text, text = divided_2, hm_label_code_s)
+
+not_div <- labeled_amicus %>% 
+  filter(excerpt_divided_if_yes_top_or_bottom_coded == "not divided") %>% 
+  select(case:fem, hm_label_code_s)
+
+labeled_amicus_final <- rbind(top, bottom, not_div)
 ```
 
+We now have a dataframe with only the following columns, with one row per labeled text.
+
 ```{r}
-labeled_amicus %>% 
-  filter(!is.na(divided_2) & !is.na(divided_1))
+labeled_amicus_final %>% colnames()
 ```
+
+Write to Box
+
+```{r}
+#box_write(labeled_amicus_final, dir_id = "154895322313", "labeled_amicus.csv")
+```

### 2022-02-16 eda/calculate_label_density.Rmd
change col name

@@
   filter(excerpt_divided_if_yes_top_or_bottom_coded %in% c("top", "all(short)")) %>% 
-  select(case:fem, -text, text = divided_1, hm_label_code_s)
+  select(case:fem, -text, text = divided_1, label = hm_label_code_s)
 
@@
   filter(excerpt_divided_if_yes_top_or_bottom_coded == "bottom") %>% 
-  select(case:fem, -text, text = divided_2, hm_label_code_s)
+  select(case:fem, -text, text = divided_2, label = hm_label_code_s)
 
@@
   filter(excerpt_divided_if_yes_top_or_bottom_coded == "not divided") %>% 
-  select(case:fem, hm_label_code_s)
+  select(case:fem, label = hm_label_code_s)
 

### 2022-02-24 data-cleaning/03b-evaluation-dataset.Rmd
create final eval dataset close #11

---
title: "Create final evaluation dataset"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(tidytext)

```

# Create evaluation set

After manual and automatic labeling (with manual validation), we can merge the two datasets to create one final evaluation dataset.

The final dataset should have the following columns in this order:

case (str; name of case)
brief (str; name of brief)
id (str/int; brief id)
fem_brief (int; 1 if brief written in support of feminist position; 0 o.w.)
text (str; text chunk of brief)
label (str; label with multiple labels separated by comma)

# Automatic label set

The automatic dataset has the correct rows/columns

```{r}
auto_label <- box_read("919813766996")
auto_label %>% head()
```

The only thing we must do is make sure that there is only one row per text (aka, concatenate texts with multiple labels into one row). If you run the code below, you will notice this does not result in any concatenations, so we don't need to save this code and can move on.

```{r}
auto_label %>% 
  group_by(case, brief, id, fem_brief, text) %>% 
  mutate(label = paste0(label, collapse = ", ")) %>% 
  unique()
```

# Manual label set

We need to change the "fem" column and figure out how to handle texts with multiple labels.

```{r}
manu_label <- box_read("919747295261")
manu_label %>% head()
```

Fix fem col

```{r}
manu_label <- manu_label %>% 
  mutate(fem = fem*1) %>% 
  rename(fem_brief = fem)

table(manu_label$fem_brief)
```

For the labels we need to deal with the following: multiple labels and labels with (1) attached to them. These are instances where Dr. McCammon only found 1 reference to the frame. I will be removing these labels to avoid adding noise to the data. We can add them back later if we decide to add more noise to the data... but after much deliberation I think the point of this dataset is to illustrate clear examples of each of the frames and determine whether our fine-tuned models can detect them.

First, check label distribution

```{r}
manu_label %>%
  separate_rows(., label, sep = "; ", convert = FALSE) %>% 
  select(case, text, label) %>% 
  group_by(label) %>% 
  summarize(n=n()) %>% arrange(-n)
```

To remove these, I'll start by expanding these columns to have one column per label. Below, w

```{r}
manu_label <- manu_label %>%
  separate_rows(., label, sep = "; ", convert = FALSE) %>%
  # clean up mismatches
  mutate(label = case_when(
    label == "women's health" ~ "health",
    label == "undue" ~ "undue burden",
    label == "rights" ~ "women's rights",
    label %in% c("reveal", "uncertainty") ~ "evidence",
    T ~ label
  )) %>% 
  # remove instances of (1) and frames we aren't concerned w/rn
  filter(!grepl("1", label),
         !(label %in% c("final authority", "intersectionality", "equal protection", "primary authority"))) %>%
  # collapse cols
  group_by(case, brief, id, fem_brief, text) %>% 
  mutate(label = paste0(label, collapse = ", ")) %>% 
  unique()
```

# Combine

```{r}
final_label <- rbind(auto_label, manu_label)
final_label %>% nrow()
```

Save to box

```{r}
box_write(final_label, dir_id = "154895322313", "evaluation_dataset.csv")
```

### 2022-03-14 data-cleaning/03b-evaluation-dataset.Rmd
add label indicator to eval_ds

@@
   mutate(label = paste0(label, collapse = ", ")) %>% 
-  unique()
+  unique() %>% 
+  nrow()
+```
+
+Add in column indicating that these texts were automatically labeled
+
+```{r}
+auto_label <- auto_label %>% mutate(manu_label = 0)
 ```
@@
 
-To remove these, I'll start by expanding these columns to have one column per label. Below, w
+To remove these, I'll start by expanding these columns to have one column per label.
+The inconsistent labels will be corrected and irrelevant information will be removed.
+At the end, we re-concatenate labels to have one row per case/brief/text.
+Also add column indicating these texts were manually labeled.
 
@@
   mutate(label = paste0(label, collapse = ", ")) %>% 
-  unique()
+  unique() %>% 
+  mutate(manu_label = 1)
 ```

### 2022-04-02 data-cleaning/04-create-walkover-brief-name.Rmd
started walkover of brief names

---
title: "Create Walkover of Brief Names"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(fuzzyjoin)

# data
# regressions/data for Amicus IV regressions/Amicus Author Organization Categorization
brief_info <- box_read("936715223606")

# data/processed amicus files/amicus_text_512.csv
amicus <- box_read("937207017356")
```

```{r}
brief_names <- brief_info %>% filter(`Row Type...9` == "Amicus Brief") %>% 
              select(`Amicus Brief`) %>% unique()

briefs_to_match <- amicus %>% select(brief) %>% unique()
```

Currently none of the names of briefs match between these two files.

```{r}
intersect(brief_names[["Amicus Brief"]], briefs_to_match[["brief"]])
```

It looks like the brief names in the file with text for topic modeling are a combination of case names and brief names. I want to remove the case portion and see if they match better with the brief names in the author information data.

1. Make everything lower case
2. Replace all v. with v
3. Remove .docx
4. Remove all text at beginning of string with `text v text. ` or `text v text - `
5. Remove `%2c`
6. Remove all punctuation and spacing

```{r}
#1
briefs_to_match$clean_names <- tolower(briefs_to_match$brief)
brief_names$clean_names <- tolower(brief_names$`Amicus Brief`)

#2
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, 'v\\.', 'v')

#3
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '\\.docx', '')

#4
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '([^v]*v[^\\.]*\\. )|([^v]*v[^-]*- )', '')

#5
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '%2c', '')

#6
briefs_to_match$clean_names <- str_replace_all(briefs_to_match$clean_names,
                                               '[^[:alnum:]]','')
brief_names$clean_names <- str_replace_all(brief_names$clean_names,
                                               '[^[:alnum:]]','')
```

Sorting by brief name.

```{r}
brief_names <- brief_names[order(brief_names$clean_names),]
briefs_to_match <- briefs_to_match[order(briefs_to_match$clean_names),]
```

After all of the cleaning I was only able to match 268 brief names.

```{r}
join <- brief_names %>% left_join(briefs_to_match, by = c("clean_names"))

table(is.na(join$brief))
```

### 2022-04-05 data-cleaning/04-create-walkover-brief-name.Rmd
create walkover for brief names

@@
 library(tidyverse)
-library(fuzzyjoin)
+
+# parallel processing
+library(R.utils)
+library(doParallel)
 
 # data
-# regressions/data for Amicus IV regressions/Amicus Author Organization Categorization
+# regressions/data for Amicus IV regressions/Amicus Author Organization Categorization.xlsx
 brief_info <- box_read("936715223606")
@@
 amicus <- box_read("937207017356")
+
+# data/author and amicus measures/amicus-level-measures.csv
+author_level <- box_read("861296487195")
+```
+
+Set the working directory for files to gets IDs for.
+
+```{r}
+box_setwd("99209523670")
 ```
@@
 ```{r}
-brief_names <- brief_info %>% filter(`Row Type...9` == "Amicus Brief") %>% 
-              select(`Amicus Brief`) %>% unique()
+# Get the IDs of all the case folders 
+case_folders <- box_ls() %>%
+  as.data.frame() %>% 
+  filter(type == "folder") %>% 
+  rename(case = name)
 
-briefs_to_match <- amicus %>% select(brief) %>% unique()
+case_folders %>% head(1)
 ```
 
-Currently none of the names of briefs match between these two files.
+For all of the folders, retrieve every file name and ID.
 
 ```{r}
-intersect(brief_names[["Amicus Brief"]], briefs_to_match[["brief"]])
+# number of cores available
+n_cores <- detectCores() - 1
+registerDoParallel(n_cores)
+
+# given a df of ids for SC folder, extract names and ids of all files in case folder
+# then, save
+all_file_names <- function(case_folder_ids) {
+
+  # get info for all files contained in each case folder
+  # stored in a list of lists
+  cases_ids_list <- mclapply(case_folder_ids$id,
+                                box_ls,
+                                mc.cores = n_cores)
+
+  # convert to list of df
+  cases_ids_list <- map(cases_ids_list, as.data.frame)
+
+  # get name of folder (this is case name)
+  cases_ids_list <- lapply(cases_ids_list, function(x) transform(x, case = sub(".*/", "", path)))
+
+  print("Created list of dfs; each element is a case folder")
+
+  # create iterator that will go through list element by element
+  it <- iter(cases_ids_list, by = "row")
+
+  # in each case folder, grab the name and id of the decision file
+  file_ids <-
+    foreach(i = it,
+            .combine = rbind,
+            .inorder = F) %dopar% {
+              i %>%
+                filter(grepl("amicus|amici", name, ignore.case = T)) %>%
+                select(case, name, id)
+            }
+  print("Obtained amicus file ids")
+
+  return(file_ids)
+}
+
+amicus_file_ids <- all_file_names(case_folders)
+
+doParallel::stopImplicitCluster()
 ```
 
-It looks like the brief names in the file with text for topic modeling are a combination of case names and brief names.
-I want to remove the case portion and see if they match better with the brief names in the author information data.
-
-1. Make everything lower case
-2. Replace all v. with v
-3. Remove .docx
-4. Remove all text at beginning of string with `text v text. ` or `text v text - `
-5. Remove `%2c`
-6. Remove all punctuation and spacing
+Join the different brief names into one dataframe.
 
 ```{r}
-#1
-briefs_to_match$clean_names <- tolower(briefs_to_match$brief)
-brief_names$clean_names <- tolower(brief_names$`Amicus Brief`)
+join_data <- author_level %>% select(id = BoxFileID, name_incorrect = AmicusBrief, CaseId)
+join_data$id <- as.character(join_data$id)
 
-#2
-briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, 'v\\.', 'v')
+join_data2 <- amicus_file_ids %>% select(id, name_correct = name)
 
-#3
-briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '\\.docx', '')
-
-#4
-briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '([^v]*v[^\\.]*\\. )|([^v]*v[^-]*- )', '')
-
-#5
-briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '%2c', '')
-
-#6
-briefs_to_match$clean_names <- str_replace_all(briefs_to_match$clean_names,
-                                               '[^[:alnum:]]','')
-brief_names$clean_names <- str_replace_all(brief_names$clean_names,
-                                               '[^[:alnum:]]','')
+data <- left_join(join_data, join_data2, by = c("id"))
 ```
 
-Sorting by brief name.
+```{r}
+table(is.na(data$name_correct))
+```
 
 ```{r}
-brief_names <- brief_names[order(brief_names$clean_names),]
-briefs_to_match <- briefs_to_match[order(briefs_to_match$clean_names),]
+data %>% filter(is.na(name_correct))
 ```
 
-After all of the cleaning I was only able to match 268 brief names.
+```{r}
+data[data$id == 592236091833,'name_correct'] <- 'Stenberg v Carhart. Amics Brief for Petitioner by Agudath Israel of America.docx'
+```
 
 ```{r}
-join <- brief_names %>% left_join(briefs_to_match, by = c("clean_names"))
+check_in_amicus <- amicus %>% left_join(data, by = c('brief' = 'name_correct'))
+june_russo_fix <- check_in_amicus %>% filter(is.na(name_incorrect)) %>%
+  select(brief) %>% unique()
+```
 
-table(is.na(join$brief))
+Write to csv
+
+```{r}
+box_write(data,
+           file_name = "walkover_brief_names.csv",
+           dir_id = 145990409196)
 ```

### 2022-04-07 data-cleaning/04-create-walkover-brief-name.Rmd
add june v russo fix

@@
 
+Add our updated brief id
+
 ```{r}
-check_in_amicus <- amicus %>% left_join(data, by = c('brief' = 'name_correct'))
-june_russo_fix <- check_in_amicus %>% filter(is.na(name_incorrect)) %>%
-  select(brief) %>% unique()
+amicus_current_ids <- amicus %>% select(brief, brief_id = id)
+final <- data %>% 
+  left_join(amicus_current_ids, c("name_correct" = "brief")) %>% 
+  select(new_id=brief_id, name_correct, name_incorrect, old_id = id)
+
+final %>% filter(is.na(new_id)) # this brief doesn't exist in our data ?
 ```
+
+## June v Russo
+
+Read in the June v Russo names from Holly's data file.
+
+```{r}
+jvr_incorrect <- box_read_excel("941695019313", sheet="final") 
+#jvr_incorrect %>% head()
+```
+
+Get the "correct" june v russo brief names
+
+```{r}
+jvr_correct <- amicus %>% filter(grepl("June", brief)) %>%
+  mutate(id = as.double(id)) %>% 
+  select(new_id=id,name_correct=brief)
+```
+
+Join the two
+
+```{r}
+jvr <- jvr_correct %>% left_join(jvr_incorrect, c("new_id"="brief_id"))
+
+jvr <- jvr %>% 
+  mutate(old_id = 0) %>% 
+  select(new_id, name_correct, name_incorrect=amicus, old_id)
+```
+
+Add to final df
+
+```{r}
+final <- final %>% rbind(jvr) %>%
+  distinct(new_id, name_correct, name_incorrect, old_id)
+```
+
+## Save
 

### 2022-04-08 data-cleaning/06-add-amicus-measures.Rmd
code to add amicus measures

---
title: "Add Amicus Measures"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(janitor)

# data
# regressions/data for Amicus IV regressions/Amicus Author Organization Categorization.xlsx
brief_info <- box_read("936715223606")

# data/processed amicus files/amicus_text_clean_512.csv
amicus <- box_read("939714323391")

# data/processed amicus files/walkover_brief_names.csv
walkover <- box_read("941154488137")
```

We need to grab only the amicus brief information from the `brief_info`file, select the variables we care about and impute NAs with 0.

Variable to select:

forgau, antauo, chcauf, lifauo, govauf, govauo, sg, racauf, racauo, medauf, medauo, mpeauf, mpeauo, legauf, legauo, relauf, relauo, LGBauf, forgauf, aclauf, aclauo, sgauf, sgauo

```{r}
col_name <- names(brief_info)[1:12]
brief_info <- brief_info %>%
  row_to_names(row_number = 1)
colnames(brief_info)[1:12] <- col_name
colnames(brief_info)[177] <- 'emppf2'
colnames(brief_info)[5] <- 'amicus_id'

brief_info <- brief_info %>% filter(`Row Type` == 'Amicus Brief') %>% select(Case, 
              amicus_id, `Amicus Brief`, forgau, antauo, chcauf, lifauo, govauf,                     govauo, sg, racauf, racauo, medauf, medauo, mpeauf, mpeauo, legauf, 
               legauo, relauf, relauo, LGBauf, forgauf, aclauf, aclauo, sgauf, sgauo)

#impute all na with 0
brief_info[is.na(brief_info)] = 0
```

```{r}
walkover$CaseId <-  as.character(walkover$CaseId)
walk_measures <- walkover %>% left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))

amicus <- amicus %>% left_join(walk_measures, by = c("id" = "new_id"))
```

Save as a csv.

**remove any unneeded columns here before saving**

```{r}
box_write(amicus,
           file_name = "amicus_text_512_measures.csv",
           dir_id = 145990409196)
```

### 2022-04-08 data-cleaning/04-create-walkover-brief-name.Rmd
write correct df to box

--- 2022-04-05 data-cleaning/04-create-walkover-brief-name.Rmd
@@
 ```{r}
-join_data <- author_level %>% select(id = BoxFileID, name_incorrect = AmicusBrief, CaseId)
+# select id's from author data
+join_data <- author_level %>%
+  select(id = BoxFileID, name_incorrect = AmicusBrief, CaseId, AmBriefID)
+
 join_data$id <- as.character(join_data$id)
@@
 
+Add our updated brief id
+
 ```{r}
-check_in_amicus <- amicus %>% left_join(data, by = c('brief' = 'name_correct'))
-june_russo_fix <- check_in_amicus %>% filter(is.na(name_incorrect)) %>%
-  select(brief) %>% unique()
+amicus_current_ids <- amicus %>% select(brief, brief_id = id)
+final <- data %>% 
+  left_join(amicus_current_ids, c("name_correct" = "brief")) %>% 
+  select(new_id=brief_id, case_code = CaseId, brief_code = AmBriefID,
+         name_correct, name_incorrect, old_id = id)
+
+final %>% filter(is.na(new_id)) # this brief doesn't exist in our data ?
+final %>% head()
 ```
+
+## June v Russo
+
+Read in the June v Russo names from Holly's data file.
+
+```{r}
+jvr_incorrect <- box_read_excel("941695019313", sheet="final") %>% 
+  mutate(brief_id = as.character(brief_id))
+jvr_incorrect %>% head()
+```
+
+Get the "correct" june v russo brief names
+
+```{r}
+jvr_correct <- amicus %>% filter(grepl("June", brief)) %>%
+  mutate(id = as.character(id)) %>% 
+  select(new_id=id,name_correct=brief)
+```
+
+Join the two
+
+```{r}
+jvr <- jvr_correct %>% left_join(jvr_incorrect, c("new_id"="brief_id"))
+
+jvr <- jvr %>% 
+  mutate(old_id = 0,
+         case_code = 999999) %>% 
+  select(new_id, case_code, brief_code, name_correct, name_incorrect=amicus, old_id)
+```
+
+Add to final df
+
+```{r}
+final <- final %>% rbind(jvr) %>%
+  distinct(new_id, case_code, brief_code, name_correct, name_incorrect, old_id)
+```
+
+Check
+
+```{r}
+final %>% nrow()
+```
+
+## Save
 
@@
 ```{r}
-box_write(data,
+box_write(final,
            file_name = "walkover_brief_names.csv",

### 2022-04-08 data-cleaning/06-add-amicus-measures.Rmd
join segment vars close #15

@@
 
+# change june v russo to case id = 999999
+brief_info <- brief_info %>%
+  mutate(Case = ifelse(is.na(Case), "999999", Case))
+
 #impute all na with 0
@@
 
+Join to amicus data
+
 ```{r}
-walkover$CaseId <-  as.character(walkover$CaseId)
+walkover$case_code <-  as.character(walkover$case_code)
 walk_measures <- walkover %>% left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))
@@
 
+Remove unnecessary columns
+
+```{r}
+final <- amicus %>% 
+  select(case, id, brief, brief_party, forgau:sgauo, text) %>% 
+  janitor::clean_names()
+```
+
+Check
+
+```{r}
+final %>% head()
+```
+
 Save as a csv.
 
-**remove any unneeded columns here before saving**
-
 ```{r}
-box_write(amicus,
-           file_name = "amicus_text_512_measures.csv",
+box_write(final,
+           file_name = "amicus_text_clean_512_vars.csv",
            dir_id = 145990409196)

### 2022-04-09 data-cleaning/04-create-walkover-brief-name.Rmd
add missing brief

@@
 
-# data/processed amicus files/amicus_text_512.csv
-amicus <- box_read("937207017356")
+# data/processed amicus files/amicus_clean_512_no_stride.csv
+amicus <- box_read("942789542605")
 
@@
 
+Add missing case
+
+```{r}
+missing <- data.frame(new_id = 861822082999, case_code = 100,
+           brief_code = 31,
+           name_correct = "Planned Parenthood of Southeastern Pennsylvania v Casey. Amici Brief for Petitioners (feminist), by Pennsylvania Coalition against Domestic Violence & others - pared.DOCX",
+           name_incorrect = "Amicus Brief for Petitioners (feminist), by |Pennsylvania Coalition Against Domestic Violence & others",
+           old_id = 000000)
+
+final <- final %>% rbind(missing)
+```
+
 Check
@@
 ```{r}
-final %>% nrow()
+final %>% distinct(new_id) %>% nrow()
 ```

### 2022-04-11 data-cleaning/05-add-amicus-measures.Rmd
mv + rnm

--- 2022-04-08 data-cleaning/06-add-amicus-measures.Rmd
@@
 
-# data/processed amicus files/amicus_text_clean_512.csv
-amicus <- box_read("939714323391")
+# data/processed amicus files/amicus_clean_512_no_stride.csv
+amicus <- box_read("942789542605")
 
@@
 walkover$case_code <-  as.character(walkover$case_code)
-walk_measures <- walkover %>% left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))
+walk_measures <- walkover %>%
+  left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))
 
@@
 ```
+Ensure no NAs
+
+```{r}
+final %>% select_if(function(x) any(is.na(x))) %>% 
+  summarise_each(funs(sum(is.na(.))))
+```
+
+Missing this brief. I don't see it in Holly's data?
+
+```{r}
+amicus %>% filter(id == 861822406799) %>% distinct(brief) %>% pull(brief)
+```
 
@@
 box_write(final,
-           file_name = "amicus_text_clean_512_vars.csv",
+           file_name = "amicus_clean_512_no_stride_vars.csv",
            dir_id = 145990409196)

### 2022-04-11 eda/common-words-by-frame.Rmd
mv + rnm

---
title: "Top 10 Words by Frame"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)

# data
# data/labeled amicus/amicus_label_density/framing_dictionary.csv
frame_dict <- box_read("914901620274")

# data/processed amicus files/amicus_text_512.csv
amicus <- box_read("937207017356")
```

The purpose of this file is to find the top 10 most common words for each frame list below.

```{r}
search_terms <- c("abortionNegativeII", "actor_couple", "actor_fetus", "actor_physician", "compulsoryII", "compulsoryMotherhood", "evidence experts II", "evidence_uncertainty", "evidence_med_authority", "evidence_research", "evidence_reveal", "evidence_uncertainty", "favorChildbirth", "health", "intersectionality", "law_undueBurdenII", "law_womanRights", "morality", "psy_harm", "womanCitizenship")

frame_dict <- frame_dict %>% filter(code %in% search_terms)
```

Here I iterate through all the words in the frame dictionary and count the number of times they show up in the corpus. I then add this count as a column to the frame dictionary.

```{r}
counts <- c()
for (i in 1:nrow(frame_dict)){
  count <- sum(str_count(amicus$text, frame_dict$word_cleaned[i]))
  counts <- append(counts, count)
}

frame_dict <- cbind(frame_dict, counts)
```

Here I gather the top 10 most common words for a frame a put them in a dataframe.

```{r}
df <- data.frame(matrix(ncol = 2, nrow = 0))
x <- c("frame", "word_cleaned")
colnames(df) <- x

for (term in search_terms){
  top10 <- frame_dict %>% filter(code == term) %>% arrange(desc(counts)) %>% slice(1:10) %>% select(frame = code, word_cleaned)
  df <- rbind(df, top10)
}
```

Now I format the dataframe so that the most common words are in a list.

```{r}
df <- df %>% group_by(frame) %>% summarise(word_list = toString(word_cleaned))
```

Save as a csv.

```{r}
#box_write(df,
#           file_name = "common-words-by-frame.csv",
#           dir_id = 158755083103)
```

### 2022-04-18 data-cleaning/05-add-amicus-measures.Rmd
add missing brief
update
add vars to shortened amicus text

@@
 # data/processed amicus files/amicus_clean_512_no_stride.csv
-amicus <- box_read("942789542605")
+amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)
+# data/processed_amicus_files/amicus_clean_512_no_stride_split.csv
+#amicus <- box_read("946701865033")
+# data/processed_amicus_files/shortened_amicus_brief_text.csv
+amicus <- box_read("910635411098")
 
@@
 brief_info <- brief_info %>% filter(`Row Type` == 'Amicus Brief') %>% select(Case, 
-              amicus_id, `Amicus Brief`, forgau, antauo, chcauf, lifauo, govauf,                     govauo, sg, racauf, racauo, medauf, medauo, mpeauf, mpeauo, legauf, 
+              amicus_id, `Amicus Brief`, forgau, antauo, chcauf, lifauo, govauf,
+              govauo, sg, racauf, racauo, medauf, medauo, mpeauf, mpeauo, legauf, 
               legauo, relauf, relauo, LGBauf, forgauf, aclauf, aclauo, sgauf, sgauo)
@@
 
+If using shortened text file, add in brief_party
+
+```{r}
+amicus <- amicus %>% left_join(., amicus_party, by = "id")
+```
+
 Remove unnecessary columns
@@
 final <- amicus %>% 
-  select(case, id, brief, brief_party, forgau:sgauo, text) %>% 
+  select(case, id, brief, brief_party, forgau:sgauo, text = txt_short) %>% 
   janitor::clean_names()
@@
 
-Missing this brief. I don't see it in Holly's data?
-
-```{r}
-amicus %>% filter(id == 861822406799) %>% distinct(brief) %>% pull(brief)
-```
-
 Save as a csv.
@@
 box_write(final,
-           file_name = "amicus_clean_512_no_stride_vars.csv",
+           file_name = "shortened-amicus-text-vars.csv",
            dir_id = 145990409196)

### 2022-04-18 eda/capstone/capstone-report.Rmd
capstone report eda

---
title: "Capstone Graphs"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

# Box access
library(boxr)
box_auth()

# data manip
library(tidyverse)
library(janitor)

# plotting
library(ggplot2)
library(ggpubr)

# data
amicus <- box_read("942861514695")

# brief info + clean 
brief_info <- box_read("936715223606")

col_name <- names(brief_info)[1:12]
brief_info <- brief_info %>%
  row_to_names(row_number = 1)
colnames(brief_info)[1:12] <- col_name
colnames(brief_info)[177] <- 'emppf2'
colnames(brief_info)[5] <- 'amicus_id'

brief_info <- brief_info %>% filter(`Row Type` == 'Amicus Brief') %>% select(Case, 
              amicus_id, `Amicus Brief`, forgau, antauo, chcauf, lifauo, govauf,
              govauo, sg, racauf, racauo, medauf, medauo, mpeauf, mpeauo, legauf, 
              legauo, relauf, relauo, LGBauf, forgauf, aclauf, aclauo, sgauf, sgauo)

# change june v russo to case id = 999999
brief_info <- brief_info %>%
  mutate(Case = ifelse(is.na(Case), "999999", Case))

#impute all na with 0
brief_info[is.na(brief_info)] = 0

medauo <- readr::read_csv("~/Documents/Vanderbilt/SP_22/capstone/medauo_topics_clean_labels_bbu_rramicus.csv",
                          col_types = cols(X1 = col_skip()))

medauf <- readr::read_csv("~/Documents/Vanderbilt/SP_22/capstone/medauf_topics_clean_labels_bbu_rramicus.csv",
           col_types = cols(X1 = col_skip()))
```

# Capstone Graphics

# Amicus author type counts

```{r}
amicus %>% distinct(id, brief_party) %>% group_by(brief_party) %>% summarize(n=n())
```

```{r}
brief_info %>% select(forgau:sgauo) %>%
  mutate(across(where(is.character), as.numeric)) %>% 
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>% 
  pivot_longer(., cols = c(forgau:sgauo), names_to = "var", values_to = "ct") %>% 
  arrange(var)
```

# MLM fine-tuning

Side-by-side, one for BERT & one for legalBERT

BERT

```{r}
bert <- data.frame(
  epoch = c(1:10),
  train_loss = c(2.0341, 1.7881, 1.6970, 1.6328, 1.5919, 1.5602, 1.5221, 1.5135, 1.4917, 1.4859),
  val_loss = c(1.7515, 1.6616, 1.6061, 1.5662, 1.5362, 1.5193, 1.4984, 1.4988, 1.4755, 1.4671)
)
bert <- bert %>% mutate(train_perp = exp(train_loss), val_perp = exp(val_loss))
```

legalBERT

```{r}
legalbert <- data.frame(
  epoch = c(1:10),
  train_loss = c(1.021, 1.2272, 1.2467, 1.2149, 1.1855, 1.1674, 1.1508, 1.1386, 1.129, 1.1193),
  val_loss = c(1.3393, 1.2612, 1.2403, 1.2276, 1.2101, 1.2020, 1.893, 1.1870, 1.1794, 1.1759)
)
legalbert <- legalbert %>% 
  mutate(train_perp = exp(train_loss), val_perp = exp(val_loss))
#legalbert
```
Plot

```{r}
colors_line <- c("Train" = "#DC277F", "Validation" = "#658FFF")

bert_train <- bert %>% 
  ggplot(.,aes(x = epoch)) +
  geom_line(aes(y = train_perp, color = "Train")) +
  geom_point(aes(y = train_perp), color = "#DC277F", alpha = 0.8) + 
  geom_line(aes(y = val_perp, color = "Validation")) +
  geom_point(aes(y = val_perp), color = "#658FFF", alpha = 0.8) +
  scale_color_manual(values = colors_line) +
  coord_cartesian(ylim = c(0,8), xlim=c(1,10)) +
  scale_y_continuous(breaks = seq(0, 8, by = 1)) +
  scale_x_continuous(breaks = seq(1, 10, by = 1)) +
  labs(
    x = "Epoch",
    y = "Perplexity",
    color = "Dataset",
    title = "BERT MLM Fine-Tuning"
  ) +
  theme_minimal()

bert_train
```

```{r}
lb_train <- legalbert %>%
  ggplot(.,aes(x = epoch)) +
  geom_line(aes(y = train_perp, color = "Train")) +
  geom_point(aes(y = train_perp), color = "#DC277F", alpha = 0.8) + 
  geom_line(aes(y = val_perp, color = "Validation")) +
  geom_point(aes(y = val_perp), color = "#658FFF", alpha = 0.8) +
  scale_color_manual(values = colors_line) +
  coord_cartesian(ylim = c(0,8), xlim=c(1,10)) +
  scale_y_continuous(breaks = seq(0, 8, by = 1)) +
  scale_x_continuous(breaks = seq(1, 10, by = 1)) +
  labs(
    x = "Epoch",
    y = "Loss",
    color = "Loss Type",
    title = "Legal-BERT MLM Fine-Tuning"
  ) +
  theme_minimal() #+
  #theme(panel.grid.minor.x = element_blank())

lb_train
```

Together

```{r}
trains <- ggarrange(bert_train, lb_train, ncol=2, nrow=1, common.legend = TRUE, legend="bottom")
ggsave(filename = "training_results.png", trains, width = 8, height=3)
```

# Topic Modeling Results

## Medauo

new label
1 = fetus viability
2 = abortion ending human life 
3 = public funds not for abortion
4 = fetus having right to life, autonomy, personhood
5 = women's health / mortality from abortion

```{r}
medauo %>% 
```
Orig

```{r, fig.width=8px, fig.height=1px}
medauo_orig <- medauo %>% 
  ggplot(., aes(x=x, y=y, color=as.factor(label), size=Count)) +
  geom_point(alpha=0.6) +
  theme_minimal() +
  guides(size = "none") +
  labs(
    x = "Dimension 2", y = "Dimension 1",
    title = "Original Medical Org Arguments (opp)",
    color = "Label"
  )
ggsave("medauo_orig.png",medauo_orig,height = 4, width = 4)
getwd()
```

Adjusted

```{r}
medauo <- medauo %>% 
  mutate(label_correct = case_when(
    label == 1 ~ "Abortion Ends Human Life",#2,
    label == 3 & (topic_id %in% c(11,28)) ~ "Public Funds",#3,
    label == 3 & !(topic_id %in% c(11,28)) ~ "Fetus Personhood",#4,
    label == 4 & (topic_id %in% c(2,6)) ~ "Fetus Viability",#1,
    label == 5 ~ "Abortion Harms Health",#5,
    T ~ "none"
  ))
```

```{r}
medauo %>% filter(label_correct == "Abortion Ends Human Life")
```

```{r}
medauo_adj <- medauo %>% 
  filter(label_correct != "none") %>% 
  ggplot(., aes(x=x, y=y, color=as.factor(label_correct), size=Count)) +
  geom_point(alpha=0.6) +
  theme_minimal() +
  guides(size = "none") +
  labs(
    x = "Dimension 2", y = "Dimension 1",
    title = "Adjusted Medical Org Arguments (opp)",
    color = "Argument"
  )
ggsave("medauo_adj.png",medauo_adj,height = 4, width = 6)
medauo_adj
```

```{r}
medauo_graphs <- ggarrange(medauo_orig, medauo_adj, ncol=2, nrow=1, common.legend = FALSE)
ggsave(filename = "medauo_results.png", medauo_graphs, width = 6, height=3)
medauo_graphs
```

## Medauf

```{r}
medauf %>% 
  #filter(label %in% c(4, 8,9)) %>% 
  ggplot(., aes(x=x, y=y, color=as.factor(label), size=Count)) +
  geom_point(alpha=0.6) +
  theme_minimal() +
  guides(size = "none")
```

new labels

removing: 2, 7

1. public funding (medicaid); 13,17, 35, 38, 22; orig -1, 0
2. violence against abortion seekers; orig 1, 11
3. minor's rights; 9, 51, 58, 59; orig 4, 8 (notifying parents as bad, counseling, risks to teenage pregnancies)
4. Physician's admitting privileges; orig 5
5. health of abortion-seekers; orig 6, 12
6. abortion & contraceptives access (orig 9)

```{r}
medauf <- medauf %>% 
  mutate(label_correct = case_when(
    label %in% c(-1, 0) ~ "Support Public Funding (Medicaid)",
    label %in% c(1,11) ~ "Violence Against Abortion Seekers",
    label %in% c(4,8) & !(topic_id %in% c(1,25)) ~ "Minor's Rights",
    label == 5 ~ "Physicians Admitting Privileges",
    label %in% c(6, 12) ~ "Health of Abortion-Seekers",
    label == 9 ~ "Abortion/Contraceptives Access",
    T ~ "none"
  ))
```

New graph

```{r}
medauf_adj <- medauf %>% 
  filter(label_correct != "none") %>% 
  ggplot(., aes(x=x, y=y, color=as.factor(label_correct), size=Count)) +
  geom_point(alpha=0.6) +
  theme_minimal() +
  guides(size = "none") +
  labs(
    x = "Dimension 2", y = "Dimension 1",
    title = "Adjusted Medical Org Arguments (pro)",
    color = "Argument"
  )
medauf_adj
```

```{r}
ggsave("medauf_adj.png",medauf_adj,height = 4, width = 6)
```

```{r}
medauf %>% filter(label_correct == "Health of Abortion-Seekers")
```

### 2022-04-20 data-cleaning/07-generate-frame-measures.Rmd
close #22

---
title: "Generate Frame Measures"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

9:15

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)
library(tidyverse)
library(tidytext)
library(textclean)
library(tm)
library(stringi)
library(quanteda)

library(boxr)
box_auth()
```

# Purpose

To develop amicus- and frame-level measures of frame usage

# Data

Abortion frame terms:

```{r}
frame_terms <- box_read("947335700912", read_fun = readr::read_csv)
```

Amicus data:

```{r}
# abortion cases
amicus <- box_read("947307207905", read_fun = readr::read_csv)
```

# Amicus-Level Measures

Start by creating corpus

```{r}
amicus %>% head(5) 
```

```{r}
amicus_corp <- amicus$text_clean %>% corpus()

# Add meta data to corpus
docvars(amicus_corp, "case") <- amicus$case
docvars(amicus_corp, "brief") <- amicus$brief
docvars(amicus_corp, "id") <- amicus$id
docvars(amicus_corp, "brief_party") <- amicus$brief_party

summary(amicus_corp) %>% head()
```

## Create frame dictionary

This dictionary will be used to filter out frame words from paragraphs when counting word frequency.

```{r}
# Remove duplicates
frame_terms <- frame_terms %>%
  select(frame_code, word_clean) %>% 
  unique()

# Get words associated with frames
get_frames <- function(frame){ 
  frame_terms %>%
    filter(frame_code == frame) %>% 
    select(word_clean)
  }

# Initialize list
search_frames <- list()

# Get unique frames
frames <- unique(frame_terms$frame_code)

# Pull words for each frame and save in list
for(i in 1:length(frames)){ 
  search_frames[i] <- get_frames(frames[i])
}

# Name items in list
names(search_frames) <- frames

frame_dict <- dictionary(search_frames)

# Check output
#frame_dict
```

# Look up frames

**Note on arguments in `tokens()` function**: removing punctuation and numbers from terms increases counts. See `amicus-exploring-counting-frames` script to go over evidence.

```{r}
# Tokenize briefs
toks <- tokens(amicus_corp, remove_punct = TRUE, remove_numbers = TRUE)
```

## Create brief summary statistics

The `amicus_corp_summary` data frame contains the summary statistics of all the briefs in our corpus, `amicus_corp`. The one thing it's missing is the number of tokens (i.e. words) in each brief.

```{r}
# Generate summary of amicusCorp
amicus_corp_summary <- summary(object = amicus_corp, 
                      n = nrow(amicus), # default is 100, we need all observations 
                      showmeta = TRUE) %>% # add meta data to summary
  as.data.frame()

# check
tail(amicus_corp_summary)
```

Calculate total number of words in each brief. Join with the amicus_corp_summary

```{r}
# Total number of tokens (before pulling frame words)
nToks <- data.frame(Text = names(ntoken(toks)), 
                     word_ct = ntoken(toks))

# Look at first 6 observations
head(nToks)
```

```{r}
amicus_info <- amicus_corp_summary %>%
  left_join(nToks, by = c("Text")) %>% 
  rename(doc_id=Text)

head(amicus_info)
```

## Generate frame frequencies

Now that we've created our `amicus_info` data frame, it's time to generate the frame frequencies.

(# of words/phrases for a particular frame) / (# of all words in the brief)

```{r}
# Search for frames
amicus_dfm <- tokens_lookup(toks, dictionary = frame_dict, nested_scope = "dictionary",
                         case_insensitive = FALSE, valuetype = "fixed") %>% dfm()

# Generate raw frequencies
amicus_frames_raw <- amicus_dfm %>%
  convert(to = "data.frame") %>%
  left_join(amicus_info, by = "doc_id") %>% 
  janitor::clean_names()

# Check out first 6 observations 
head(amicus_frames_raw, 10)
```

Get frame frequencies - These are calculated by dividing the frame count by the word count.

```{r}
# Generate frame frequencies 
amicus_frames_freq <- amicus_frames_raw %>% 
  pivot_longer(c(abortion_different:womens_rights),
               names_to = "frame", values_to = "frame_ct") %>% 
  mutate(frame_freq = frame_ct/word_ct) %>% 
  select(-frame_ct, -word_ct) %>% 
  pivot_wider(names_from = "frame", values_from = frame_freq)

amicus_frames_freq %>% head(10)
```

## Raw counts + freq

Dataframe with raw counts and frequencies

```{r}
amicus_frames <- amicus_frames_raw %>% 
  select(doc_id:womens_rights, word_ct) %>% 
  left_join(., amicus_frames_freq, 
            by = c("doc_id"), 
            suffix = c("_raw", "_freq")) %>% 
  select(-c(types:sentences)) %>% 
  select(case:brief_party, word_ct, sort(colnames(.))) %>% 
  janitor::clean_names()

amicus_frames %>% head(10)
```

Save

```{r}
box_write(amicus_frames,
           file_name = "amicus-level-frame-measures.csv",
           dir_id = 161199725595)
```

# Case-Level Measures

To generate case-level measures:

1. For each amicus type, sum up the frame frequencies measure for all amicus
2. Divide by the number of briefs for that type
3. Do for all cases

```{r}
amicus_frames <- amicus_frames %>% select(-c(case, brief, brief_party))
```

## Sum up frequencies by amicus type

First, add in amicus type vars

```{r}
sum_amicus <- amicus %>% select(case, id, forgau:sgauo) %>% 
  pivot_longer(., cols = c(forgau:sgauo), names_to = "author_type", values_to = "value") %>% 
  left_join(., amicus_frames, by = "id") %>%
  select(case, id, author_type, value, contains("freq")) %>% 
  filter(value == 1)

sum_amicus %>% head()
```
Then, sum up values by case, amicus type

```{r}
sum_amicus <- sum_amicus %>% 
  select(-value) %>% 
  group_by(case, author_type) %>% 
  summarize(across(contains("freq"), ~ sum(.x, na.rm = TRUE)))

sum_amicus %>% head(5)
```

## Number of briefs per amicus author type per case

Pivot the df and select only rows where value is 1 (indicating that the case has an amicus brief with that author type)

```{r}
case_cts <- amicus %>% select(case, forgau:sgauo) %>% 
  pivot_longer(., cols = c(forgau:sgauo), names_to = "author_type", values_to = "value") %>% 
  filter(value == 1)
```

Then, group by case, type and count the number of rows for each

```{r}
case_cts <- case_cts %>% group_by(case, author_type) %>% summarize(n=n())
case_cts %>% head()
```

## Divide summed frequencies by brief count for final measure

```{r}
case_frames <- sum_amicus %>% left_join(., case_cts, by = c("case", "author_type")) %>% 
  mutate(across(contains("freq"), ~.x/n))
```

Save

```{r}
box_write(case_frames,
           file_name = "case-level-frame-measures.csv",
           dir_id = 161199725595)
```

### 2022-04-20 data-cleaning/07-generate-frame-measures.Rmd
verified

@@
 ---
-
-9:15
 
@@
 Start by creating corpus
-
-```{r}
-amicus %>% head(5) 
-```
 
@@
   pivot_longer(., cols = c(forgau:sgauo), names_to = "author_type", values_to = "value") %>% 
+  filter(value == 1) %>% 
   left_join(., amicus_frames, by = "id") %>%
-  select(case, id, author_type, value, contains("freq")) %>% 
-  filter(value == 1)
+  select(case, id, author_type, value, contains("freq"))
 
@@
 ```
+```{r}
+sum_amicus %>% filter(case == "Anders v Floyd" | case == "Ayotte v. PP")
+```
+
 Then, sum up values by case, amicus type

### 2022-04-20 data-cleaning/08-create-regression-data.Rmd
close #25

---
title: "Create Regression Data"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)

library(tidyverse)
library(boxr)
box_auth()

case_level <- box_read("947450386335")
justice_level <- box_read("947810760828")
```

# Purpose

To create regression data for Amicus IV. The dependent variable is justicevot. The controls are: justicemq, justicefem, nonftyp2, lcdisdirfem. The independent vars are the framing measures.

# Refactor case-level data

Currently, case_level has one row per frame per case. We want one row per case.

```{r}
case_level <- case_level %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
  pivot_wider(., c(case,author_type),
              names_from = author_type,
              values_from=c(abortion_different:womens_rights),
              names_glue = "{author_type}_{.value}") %>% 
  select(case, sort(colnames(.)))

case_level %>% head(5)
```

# Select vars from justice-level file

```{r}
justice_level <- justice_level %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem,
         nonftyp2, lcdisdirfem)

justice_level %>% head(5)
```

# Merge

First, clean up case names for easier matching.

```{r}
justice_level <- justice_level %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte v Planned Parenthood of Northern New England" ~ "Ayotte v PP",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenthood of Southeastern Pennsylvania v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth" ~ "PP v Danforth",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Joseph Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Thornburgh v American College of Obstetricians and Gynecologists LDEF" ~
             "Thornburgh v American College of OBGYNs",
           case == "Whole Womens Health v Hellerstedt" ~ "WWH v Hellerstedt",
           T ~ case
         ))

case_level <- case_level %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
        case = str_replace_all(case, "(,|’|'|\\)|\\()", ""))
```

Then, join & rearrange

```{r}
final <- case_level %>% 
  left_join(., justice_level, by = "case") %>% 
  select(case, ddate2:lcdisdirfem, everything())
```

# Save

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data.xlsx",
          dir_id = 158993526875)
```

### 2022-04-21 modeling/amicus_type/medauf.Rmd
close #23

---
title: "Medauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read("948366662469") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models. Technically, we should...?

```{r}
data_scale <- data %>%           # Applying functions of dplyr
  mutate(across(c(where(is.numeric), -justicevot, -id), ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0.5: women's future life
* .1: abortion different, bad law

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_abortion_different,
              family = binomial, data = data_scale,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-21 modeling/amicus_type/medauo.Rmd
close #23

---
title: "Medauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read("948366662469") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models. Technically, we should...?

```{r}
data_scale <- data %>%           # Applying functions of dplyr
  mutate(across(c(where(is.numeric), -justicevot, -id), ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0.5: compulsory_motherhood, morality&relig, protesters
* .1: undue burden

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_abortion_different,
              family = binomial, data = data_scale,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-21 modeling/base-models.Rmd
close #23

---
title: "Base Model"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()
```

# Multilevel Modeling

In this file, we use multilevel modeling to test whether frames articulated in amicus briefs have an effect on justice votes.

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read("947772227392") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Step 0: Calculate the Interclass Correlation Coefficient (ICC)

ICC is the ratio of between-gropu variance to the total variance. This is the proportion of total variance in the outcome that is accounted for by the grouping. In this case, the groups are justices. This value should be ~ 0.3 or higher. If it's 0, that means no variation is accounted for by the justices and we shouldn't be doing MLM.

Because our outcome is binary (yes/no), we use glmer (generalized mixed model) and specify the binomial family.

```{r}
resnull <- glmer(justicevot ~ (1|id)+1 ,family = "binomial", data = data)  
summary(resnull)
```
We are good to proceed

```{r}
calc_ICC <-function(Model.Name) {
  tau.Null<-as.numeric(lapply(summary(Model.Name)$varcor, diag))
  sigma.Null <- as.numeric(attr(summary(Model.Name)$varcor, "sc")^2)
  ICC.Null <- tau.Null/(tau.Null+sigma.Null)
  return(ICC.Null)
} 
calc_ICC(resnull)
```

# Base Model

(1 | group) + predictors = random intercept for each level in the group
(0 | group) + predictors = fixed intercept 
(1 | group) + (1 | predictor) + predictors = random intercept and random slope for predictor. the remaining predictors are fixed.

Here, we use justicevot ~ (1 | id) + predictors. This means we want a random intercept that changes for each justice. The formula would be: $$justicevot_{ij} = \beta_{0j} + \beta_1(justicemq_{ij}) +...+\epsilon_{ij}$$

with $$\beta_{0j} = \gamma_{00} + \mu_{0j}$$
and this equation, but one $$\beta_1 = \gamma_{10}$$

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
summary(mod1)
```

### 2022-04-22 modeling/amicus_type/aclauf.Rmd
close #26

---
title: "Aclauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/aclauo.Rmd
close #26

---
title: "Aclauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/antauo.Rmd
close #26

---
title: "Antauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(antauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                antauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/chcauf.Rmd
close #26

---
title: "Chcauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(chcauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05: standing
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/forgauf.Rmd
close #26

---
title: "Forgauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(forgauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10: standing

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                forgauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/govauf.Rmd
close #26

---
title: "Govauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(govauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/govauo.Rmd
close #26

---
title: "Govauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(govauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/legauf.Rmd
close #26

---
title: "Legauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(legauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/legauo.Rmd
close #26

---
title: "Legauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(legauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                legauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/base-models.Rmd
close #26

@@
 box_auth()
+
+# data id
+amicus_only <- "948366662469"
+full_cases <- "948832669583"
+
+#**Note: The data used in these models is *the full set* of abortion cases. Cases *without* amici are included and their frame measures are all 0s.**
 ```
@@
 ```{r}
-data <- box_read("947772227392") %>% 
+data <- box_read(amicus_only) %>% 
   filter(justicevot != "NA") %>% 
@@
          justicefem = as.factor(justicefem),
+         cirsplit = as.factor(cirsplit),
          nonftyp2 = as.factor(nonftyp2)) %>% 
@@
 ```
-We are good to proceed
+ICC for model with no covariates
 
@@
 
-# Base Model
+# Base Model (lcdisdirfem)
 
@@
 ```{r}
-mod1 <- glmer(justicevot ~
+base_mod <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem,
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-summary(mod1)
+summary(base_mod)
 ```
+
+ICC for base model
+
+```{r}
+calc_ICC(base_mod)
+```
+
+# Base Model 2 (cirsplit)
+
+Use cirsplit instead of lcdisdirfem
+
+```{r}
+base_mod_2 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + nonftyp2 + cirsplit,
+              family = binomial, data = data,  
+              nAGQ = 1, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+summary(base_mod_2)
+```
+
+ICC for base model
+
+```{r}
+calc_ICC(base_mod_2)
+```

### 2022-04-22 modeling/amicus_type/lgbauf.Rmd
close #27

---
title: "Lgbauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(lg_bauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lg_bauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/lifauo.Rmd
close #27

---
title: "Lifauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(lifauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05: physician negative, privacy
* 0.10: fetus, final authority,

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/medauo.Rmd
close #27

@@
 box_auth()
+
+amicus_only <- "948366662469"
+full_cases <- "948832669583"
 ```
@@
 ```{r}
-data <- box_read("948366662469") %>% 
+data <- box_read(full_cases) %>% 
   filter(justicevot != "NA") %>% 
@@
 data <- case_ids %>% left_join(., data, by = "case")
-data %>% head(1) %>% select(case:justicefem)
+#data %>% head(1) %>% select(case:justicefem)
 ```
@@
 
-Remove cols where all values are NA. Not sure if we will do this or not in models. Technically, we should...?
+Remove cols where all values are NA. Not sure if we will do this or not in models.
 
@@
 
-* 0.5: compulsory_motherhood, morality&relig, protesters
-* .1: undue burden
+* 0:
+* 0.01
+* 0.05:
+* .1:
 
@@
                 medauo_abortion_different,
-              family = binomial, data = data_scale,  
+              family = binomial, data = data,  
               nAGQ = 0, control=glmerControl(
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_physician,
+                medauo_standing,
               family = binomial, data = data,  

### 2022-04-22 modeling/amicus_type/mpeauf.Rmd
close #27

---
title: "Mpeauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10: bad law, physician, physician negative

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/mpeauo.Rmd
close #27

---
title: "Mpeauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0: compulsory motherhood
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/racauf.Rmd
close #27

---
title: "Racauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0: compulsory motherhood
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/racauo.Rmd
close #27

---
title: "Racauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/relauf.Rmd
close #27

---
title: "Relauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10: privacy

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/relauo.Rmd
close #27

---
title: "Relauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0: compulsory motherhood
* 0.01:
* 0.05: women's health
* 0.10: evidence, informed consent, physician,

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/sgauf.Rmd
close #27

---
title: "Sgauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10:

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 modeling/amicus_type/sgauo.Rmd
close #27

---
title: "Sgauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10: women's health

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                sgauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-22 data-cleaning/08-create-regression-data.Rmd
diff reg files

@@
          justiceid, justicevot, justicemq, justicefem,
-         nonftyp2, lcdisdirfem)
+         nonftyp2, lcdisdirfem, cirsplit)
 
@@
 ```{r}
-final <- case_level %>% 
-  left_join(., justice_level, by = "case") %>% 
-  select(case, ddate2:lcdisdirfem, everything())
+# start with justice_level bc this df has cases that the case_level does not
+# these cases don't have amicus briefs, which is why they aren't in our data
+final <- justice_level %>% 
+  left_join(., case_level, by = "case") %>% 
+  select(case, ddate2:cirsplit, everything())
+
+# use this code if we don't want to include cases w/o amici
+#final <- case_level %>% 
+#  left_join(., justice_level, by = "case") %>% 
+#  select(case, ddate2:cirsplit, everything())
 ```
@@
 ```{r}
+amicus_only <- "amicus-iv-regression-data.csv"
+full <- "amicus-iv-regression-data-all-cases.csv"
 box_write(final,
-          file_name = "amicus-iv-regression-data.xlsx",
+          file_name = full,
           dir_id = 158993526875)

### 2022-04-24 data-cleaning/08-create-regression-data.Rmd
one measure per frame

@@
 
-case_level <- box_read("947450386335")
+case_amici_level <- box_read("947450386335")
 justice_level <- box_read("947810760828")
@@
 ```{r}
-case_level <- case_level %>% 
+case_level <- case_amici_level %>% 
   rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
@@
 ```
+
+# One measure per frame
+
+Instead of looking at measures by author type, look at aggregation of measures.
+
+```{r}
+case_amici_level <- case_amici_level %>% 
+  mutate(case = str_replace(case, 'v\\.', 'v'),
+        case = str_replace_all(case, "(,|’|'|\\)|\\()", ""))
+
+# sum up frequencies by frame
+case_amici_level <- case_amici_level %>% group_by(case) %>% 
+  summarize(across(contains("freq"), ~ sum(.x, na.rm = TRUE)))
+
+final <- case_amici_level %>% 
+  left_join(., justice_level, by = "case") %>% 
+  select(case, ddate2:cirsplit, everything())
+```
+
+Save
+
+```{r}
+box_write(final,
+          file_name = "amicus-iv-regression-data-frame-by-case-amici-only.csv",
+          dir_id = 158993526875)
+```

### 2022-04-24 modeling/frame-per-case.Rmd
one measure per frame

---
title: "Frames Across all Author Types"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

#amicus_only <- "948366662469"
#full_cases <- "948832669583"
frame_by_case <- "949410651748"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(frame_by_case) %>% 
  filter(justicevot != "NA") %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(abortion_different:womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models. Uncomment if scaling data

```{r}
data <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data <- janitor::remove_empty(data, which = "cols")
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01:
* 0.05:
* 0.10: abortion different, bad law

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-04-26 data-cleaning/08-create-regression-data.Rmd
add anders, small changes close #29

@@
 
+Cases to exclude and keep:
+
+Exclude: Anders, Connecticut v Menillo, Guste, Hartigan, Joseph Mazurek, Benten, Lambert, Leavitt, Poe v Gerstein
+
+Include: Bellotti 1976, Singleton v Wulff
+
 # Refactor case-level data
@@
 justice_level <- justice_level %>% 
+  filter(
+    !grepl("Menillo|Guste|Hartigan|Mazurek|Benten|Lambert|Leavitt|Gerstein", casename)) %>% 
   select(case = casename, ddate2,
          justiceid, justicevot, justicemq, justicefem,
-         nonftyp2, lcdisdirfem, cirsplit)
+         nonftyp2, lcdisdirfem, cirsplit,
+         cfemam, coppam, pfemam, poppam)
 
@@
            case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
+           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
            case == "Hill et al v Colorado" ~ "Hill v Colorado",
@@
   left_join(., case_level, by = "case") %>% 
-  select(case, ddate2:cirsplit, everything())
+  select(case, ddate2:poppam, everything())
 
@@
 ```{r}
-amicus_only <- "amicus-iv-regression-data.csv"
-full <- "amicus-iv-regression-data-all-cases.csv"
+#amicus_only <- "amicus-iv-regression-data.csv"
+#full <- "amicus-iv-regression-data-all-cases.csv"
+final_case <- "amicus-iv-regression-data-final-cases.csv"
 box_write(final,
-          file_name = full,
+          file_name = final_case,
           dir_id = 158993526875)
@@
 box_write(final,
-          file_name = "amicus-iv-regression-data-frame-by-case-amici-only.csv",
+          file_name = "amicus-iv-regression-data-frame-by-case-final-cases.csv",
           dir_id = 158993526875)
 ```
+
+# Two measures per frame: fem and opp
+
+Instead of looking at use of frame across all amici, separate into fem and opp, and then aggregate
+
+```{r}
+case_amici_level <- case_amici_level %>% 
+  mutate(case = str_replace(case, 'v\\.', 'v'),
+        case = str_replace_all(case, "(,|’|'|\\)|\\()", ""))
+
+# sum up frequencies by frameXparty
+case_party_level <- case_amici_level %>% 
+  mutate(party = ifelse(grepl("auf", author_type), "fem", "opp")) %>% 
+  group_by(case, party) %>% 
+  summarize(across(contains("freq"), ~ sum(.x, na.rm = TRUE)))
+
+# reorg
+case_party_level <- case_party_level %>% 
+  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
+  pivot_wider(., c(case,party),
+              names_from = party,
+              values_from=c(abortion_different:womens_rights),
+              names_glue = "{party}_{.value}") %>% 
+  select(case, sort(colnames(.)))
+
+final <- justice_level %>% 
+  left_join(., case_party_level, by = "case") %>% 
+  select(case, ddate2:poppam, everything())
+```
+
+Save
+
+```{r}
+box_write(final,
+          file_name = "amicus-iv-regression-data-frame-by-party-case-final-cases.csv",
+          dir_id = 158993526875)
+```

### 2022-04-27 modeling/amicus_type/chcauf.Rmd
close #30

@@
 library(lme4)
+library(kableExtra)
+library(broom.mixed)
 library(boxr)
@@
 full_cases <- "948832669583"
+final_cases <- "949901868853"
 ```
@@
 ```{r}
-data <- box_read(full_cases) %>% 
+data <- box_read(final_cases) %>% 
   filter(justicevot != "NA") %>% 
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(chcauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(chcauf_abortion_different:chcauf_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, pfemam, chcauf_abortion_different:chcauf_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('chcauf')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('chcauf')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.10: 
+* 0.20:
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_abortion_different,
+                chcauf_abortion_different + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
 
-# Abortion Immoral
+# Abortion Regret
 
 ```{r}
-mod2 <- glmer(justicevot ~
+mod3 <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_abortion_immoral,
+                chcauf_abortion_regret + pfemam,
               family = binomial, data = data,  
@@
 
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_bad_law,
+                chcauf_bad_law + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_compulsory_motherhood,
+                chcauf_compulsory_motherhood + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_compulsory_motherhood_ii,
+                chcauf_compulsory_motherhood_ii + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_evidence,
+                chcauf_evidence + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
 ```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
-```
-
-\newpage
-
-# Fetus
-
-```{r}
-mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_fetus,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod11)
-```
-
-\newpage
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_final_authority,
+                chcauf_final_authority + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_morality_religion,
+                chcauf_morality_religion + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_overturn_roe,
+                chcauf_overturn_roe + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_privacy,
+                chcauf_privacy + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_standing,
+                chcauf_standing + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_uncertainty,
+                chcauf_uncertainty + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_undue_burden,
+                chcauf_undue_burden + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_untruthful,
+                chcauf_untruthful + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_womens_future_life,
+                chcauf_womens_future_life + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_womens_health,
+                chcauf_womens_health + pfemam,
               family = binomial, data = data,  
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_womens_rights,
+                chcauf_womens_rights + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod27)

### 2022-04-27 modeling/amicus_type/forgauf.Rmd
close #30

@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(forgauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(forgauf_abortion_different:forgauf_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, pfemam, forgauf_abortion_different:forgauf_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('forgauf')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('forgauf')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.01:
-* 0.05:
-* 0.10: standing
+* 0.05: standing
+* 0.10: women's health
+* 0.20: abortion different, bad law, morality and religion
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_abortion_different,
+                forgauf_abortion_different + pfemam,
               family = binomial, data = data,  
@@
 
-# Abortion Immoral
+# Abortion Regret
 
 ```{r}
-mod2 <- glmer(justicevot ~
+mod3 <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_abortion_immoral,
+                forgauf_abortion_regret + pfemam,
               family = binomial, data = data,  
@@
 
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_bad_law,
+                forgauf_bad_law + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_compulsory_motherhood,
+                forgauf_compulsory_motherhood + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_compulsory_motherhood_ii,
+                forgauf_compulsory_motherhood_ii + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_evidence,
+                forgauf_evidence + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
 ```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
-```
-
-\newpage
-
-# Fetus
-
-```{r}
-mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_fetus,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod11)
-```
-
-\newpage
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_final_authority,
+                forgauf_final_authority + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_morality_religion,
+                forgauf_morality_religion + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_overturn_roe,
+                forgauf_overturn_roe + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_privacy,
+                forgauf_privacy + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_standing,
+                forgauf_standing + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_uncertainty,
+                forgauf_uncertainty + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_undue_burden,
+                forgauf_undue_burden + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_untruthful,
+                forgauf_untruthful + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_womens_future_life,
+                forgauf_womens_future_life + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_womens_health,
+                forgauf_womens_health + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_womens_rights,
+                forgauf_womens_rights + pfemam,
               family = binomial, data = data,  

### 2022-04-27 modeling/amicus_type/lifauo.Rmd
close #30

@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(lifauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(lifauo_abortion_different:lifauo_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, poppam, lifauo_abortion_different:lifauo_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('lifauo')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('lifauo')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.01:
-* 0.05: physician negative, privacy
-* 0.10: fetus, final authority,
+* 0.05: 
+* 0.10: final authority, privacy
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_abortion_different,
+                lifauo_abortion_different + poppam,
               family = binomial, data = data,  
@@
 
-# Abortion Immoral
+# Abortion Regret
 
 ```{r}
-mod2 <- glmer(justicevot ~
+mod3 <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_abortion_immoral,
+                lifauo_abortion_regret + poppam,
               family = binomial, data = data,  
@@
 
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_bad_law,
+                lifauo_bad_law + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_compulsory_motherhood,
+                lifauo_compulsory_motherhood + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_compulsory_motherhood_ii,
+                lifauo_compulsory_motherhood_ii + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_evidence,
+                lifauo_evidence + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
 ```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
-```
-
-\newpage
-
-# Fetus
-
-```{r}
-mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_fetus,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod11)
-```
-
-\newpage
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_final_authority,
+                lifauo_final_authority + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_morality_religion,
+                lifauo_morality_religion + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_overturn_roe,
+                lifauo_overturn_roe + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_privacy,
+                lifauo_privacy + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_standing,
+                lifauo_standing + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_uncertainty,
+                lifauo_uncertainty + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_undue_burden,
+                lifauo_undue_burden + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_untruthful,
+                lifauo_untruthful + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_womens_future_life,
+                lifauo_womens_future_life + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_womens_health,
+                lifauo_womens_health + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_womens_rights,
+                lifauo_womens_rights + poppam,
               family = binomial, data = data,  

### 2022-04-27 modeling/amicus_type/medauf.Rmd
close #30

@@
 library(boxr)
+library(kableExtra)
+library(broom.mixed)
 box_auth()
+
+amicus_only <- "948366662469"
+full_cases <- "948832669583"
+final_cases <- "949901868853"
 ```
@@
 ```{r}
-data <- box_read("948366662469") %>% 
+data <- box_read(final_cases) %>% 
   filter(justicevot != "NA") %>% 
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(medauf_abortion_different:medauf_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 
-Remove cols where all values are NA. Not sure if we will do this or not in models. Technically, we should...?
+Remove cols where all values are NA. Not sure if we will do this or not in models.
 
 ```{r}
-data_scale <- data %>%           # Applying functions of dplyr
-  mutate(across(c(where(is.numeric), -justicevot, -id), ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, pfemam, medauf_abortion_different:medauf_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('medauf')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('medauf')) %>% colnames()
+#setdiff(total_cols, remaining_cols)
 ```
@@
 
-* 0.5: women's future life
-* .1: abortion different, bad law
+* 0:
+* 0.01:
+* 0.05: women's future life
+* 0.10: abortion different, bad law
+* 0.20: standing
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_abortion_different,
-              family = binomial, data = data_scale,  
+                medauf_abortion_different + pfemam,
+              family = binomial, data = data,  
               nAGQ = 0, control=glmerControl(
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
 
-# Abortion Immoral
+# Abortion Regret
 
 ```{r}
-mod2 <- glmer(justicevot ~
+mod3 <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_abortion_immoral,
+                medauf_abortion_regret + pfemam,
               family = binomial, data = data,  
@@
 
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_bad_law,
+                medauf_bad_law + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_compulsory_motherhood,
+                medauf_compulsory_motherhood + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_compulsory_motherhood_ii,
+                medauf_compulsory_motherhood_ii + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_evidence,
+                medauf_evidence + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
 ```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
-```
-
-\newpage
-
-# Fetus
-
-```{r}
-mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_fetus,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod11)
-```
-
-\newpage
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_final_authority,
+                medauf_final_authority + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_morality_religion,
+                medauf_morality_religion + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_overturn_roe,
+                medauf_overturn_roe + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_privacy,
+                medauf_privacy + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_physician,
+                medauf_standing + pfemam,
               family = binomial, data = data,  
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_uncertainty,
+                medauf_uncertainty + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_undue_burden,
+                medauf_undue_burden + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_untruthful,
+                medauf_untruthful + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_womens_future_life,
+                medauf_womens_future_life + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_womens_health,
+                medauf_womens_health + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_womens_rights,
+                medauf_womens_rights + pfemam,
               family = binomial, data = data,  

### 2022-04-27 modeling/amicus_type/medauo.Rmd
close #30

@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(medauo_abortion_different:medauo_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%           # Applying functions of dplyr
-  mutate(across(c(where(is.numeric), -justicevot, -id), ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, poppam, medauo_abortion_different:medauo_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('medauo')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('medauo')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.01
-* 0.05:
-* .1:
+* 0.05: morality/relig, protest
+* 0.10: abortion regret
+* 0.20: compulsory motherhood, undue burden, women's health
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_abortion_different,
+                medauo_abortion_different + poppam,
               family = binomial, data = data,  
@@
 
-# Abortion Immoral
+# Abortion Regret
 
 ```{r}
-mod2 <- glmer(justicevot ~
+mod3 <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_abortion_immoral,
+                medauo_abortion_regret + poppam,
               family = binomial, data = data,  
@@
 
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_bad_law,
+                medauo_bad_law + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_compulsory_motherhood,
+                medauo_compulsory_motherhood + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_compulsory_motherhood_ii,
+                medauo_compulsory_motherhood_ii + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_evidence,
+                medauo_evidence + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
 ```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
-```
-
-\newpage
-
-# Fetus
-
-```{r}
-mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_fetus,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod11)
-```
-
-\newpage
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_final_authority,
+                medauo_final_authority + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_morality_religion,
+                medauo_morality_religion + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_overturn_roe,
+                medauo_overturn_roe + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_privacy,
+                medauo_privacy + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_standing,
+                medauo_standing + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_uncertainty,
+                medauo_uncertainty + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_undue_burden,
+                medauo_undue_burden + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_untruthful,
+                medauo_untruthful + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_womens_future_life,
+                medauo_womens_future_life + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_womens_health,
+                medauo_womens_health + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_womens_rights,
+                medauo_womens_rights + poppam,
               family = binomial, data = data,  

### 2022-04-27 modeling/amicus_type/relauo.Rmd
close #30

@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('relauo')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```
@@
 
-* 0: compulsory motherhood
+* 0: 
 * 0.01:
-* 0.05: women's health
-* 0.10: evidence, informed consent, physician,
+* 0.05: abortion regret
+* 0.10: evidence
+* 0.20: bad law, compulsory motherhood, women's health
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_abortion_different,
+                relauo_abortion_different + poppam,
               family = binomial, data = data,  
@@
 
-# Abortion Immoral
+# Abortion Regret
 
 ```{r}
-mod2 <- glmer(justicevot ~
+mod3 <- glmer(justicevot ~
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_abortion_immoral,
+                relauo_abortion_regret + poppam,
               family = binomial, data = data,  
@@
 
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_bad_law,
+                relauo_bad_law + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_compulsory_motherhood,
+                relauo_compulsory_motherhood + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_compulsory_motherhood_ii,
+                relauo_compulsory_motherhood_ii + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_evidence,
+                relauo_evidence + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
 ```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
-```
-
-\newpage
-
-# Fetus
-
-```{r}
-mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_fetus,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod11)
-```
-
-\newpage
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_final_authority,
+                relauo_final_authority + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_morality_religion,
+                relauo_morality_religion + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_overturn_roe,
+                relauo_overturn_roe + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_privacy,
+                relauo_privacy + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_standing,
+                relauo_standing + poppam,
               family = binomial, data = data,  
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_uncertainty,
+                relauo_uncertainty + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_undue_burden,
+                relauo_undue_burden + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_untruthful,
+                relauo_untruthful + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_future_life,
+                relauo_womens_future_life + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_health,
+                relauo_womens_health + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_rights,
+                relauo_womens_rights + poppam,
               family = binomial, data = data,  

### 2022-04-27 modeling/base-models.Rmd
close #30

@@
 full_cases <- "948832669583"
-
-#**Note: The data used in these models is *the full set* of abortion cases. Cases *without* amici are included and their frame measures are all 0s.**
+final_cases <- "949901868853"
 ```
@@
 ```{r}
-data <- box_read(amicus_only) %>% 
+data <- box_read(final_cases) %>% 
   filter(justicevot != "NA") %>% 

### 2022-04-27 modeling/fem-frame-per-case.Rmd
close #30

--- 2022-04-27 modeling/amicus_type/relauo.Rmd
@@
 ---
-title: "Relauo Amicus Brief Models"
+title: "Frames Across all Fem Author Types"
 author: "Amanda Konet"
@@
 output: pdf_document
+df_print: kable
 ---
@@
 library(lme4)
+library(broom.mixed)
 library(kableExtra)
-library(broom.mixed)
 library(boxr)
@@
 
-amicus_only <- "948366662469"
-full_cases <- "948832669583"
-final_cases <- "949901868853"
+#amicus_only <- "948366662469"
+#full_cases <- "948832669583"
+#frame_by_party <- "949813266093"
+final_by_party <- "949904531983"
 ```
@@
 ```{r}
-data <- box_read(final_cases) %>% 
+data <- box_read(final_by_party) %>% 
   filter(justicevot != "NA") %>% 
@@
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0)))
+  mutate(across(c(fem_abortion_different:opp_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 data <- data %>%
-  select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>% 
+  select(case:cirsplit, pfemam, fem_abortion_different:fem_womens_rights) %>% 
   mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
@@
 
-total_cols <- data %>% select(contains('relauo')) %>% colnames()
+total_cols <- data %>% select(contains('fem')) %>% colnames()
 data <- janitor::remove_empty(data, which = "cols")
-remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
+remaining_cols <- data %>% select(contains('fem')) %>% colnames()
 setdiff(total_cols, remaining_cols)
@@
 * 0.01: 
-* 0.05: abortion regret
-* 0.10: evidence
-* 0.20: bad law, compulsory motherhood, women's health
+* 0.05: 
+* 0.10: abortion different
+* 0.20: bad law, physician negative
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_abortion_different + poppam,
+                fem_abortion_different + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_abortion_regret + poppam,
+                fem_abortion_regret + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_bad_law + poppam,
+                fem_bad_law + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_compulsory_motherhood + poppam,
+                fem_compulsory_motherhood + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_compulsory_motherhood_ii + poppam,
+                fem_compulsory_motherhood_ii + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_evidence + poppam,
+                fem_evidence + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_final_authority + poppam,
+                fem_final_authority + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_morality_religion + poppam,
+                fem_morality_religion + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_overturn_roe + poppam,
+                fem_overturn_roe + pfemam,
               family = binomial, data = data,  
@@
 
+# Physician
+
+```{r}
+mod16 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                fem_physician + pfemam,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod16,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod16)
+```
+
+\newpage
+
+# Physician Negative
+
+```{r}
+mod17 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                fem_physician_negative + pfemam,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod17,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod17)
+```
+
+\newpage
+
 # Privacy
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_privacy + poppam,
+                fem_privacy + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_standing + poppam,
+                fem_standing + pfemam,
               family = binomial, data = data,  
@@
 
-summary(mod20)
+summary(mod15)
 ```
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_uncertainty + poppam,
+                fem_uncertainty + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_undue_burden + poppam,
+                fem_undue_burden + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_untruthful + poppam,
+                fem_untruthful + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_future_life + poppam,
+                fem_womens_future_life + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_health + poppam,
+                fem_womens_health + pfemam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_rights + poppam,
+                fem_womens_rights + pfemam,
               family = binomial, data = data,  

### 2022-04-27 modeling/opp-frame-per-case.Rmd
close #30

--- 2022-04-27 modeling/fem-frame-per-case.Rmd
@@
 ---
-title: "Frames Across all Fem Author Types"
+title: "Frames Across all Opp Author Types"
 author: "Amanda Konet"
@@
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(fem_abortion_different:opp_womens_rights), ~replace_na(.x, 0)))
+  mutate(across(c(opp_abortion_different:opp_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 data <- data %>%
-  select(case:cirsplit, pfemam, fem_abortion_different:fem_womens_rights) %>% 
+  select(case:cirsplit, poppam, opp_abortion_different:opp_womens_rights) %>% 
   mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
@@
 * 0.05: 
-* 0.10: abortion different
-* 0.20: bad law, physician negative
+* 0.10: 
+* 0.20: bad law, women's future life
 
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_abortion_different + pfemam,
+                opp_abortion_different + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_abortion_regret + pfemam,
+                opp_abortion_regret + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_bad_law + pfemam,
+                opp_bad_law + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_compulsory_motherhood + pfemam,
+                opp_compulsory_motherhood + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_compulsory_motherhood_ii + pfemam,
+                opp_compulsory_motherhood_ii + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_evidence + pfemam,
+                opp_evidence + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_final_authority + pfemam,
+                opp_final_authority + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_morality_religion + pfemam,
+                opp_morality_religion + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_overturn_roe + pfemam,
+                opp_overturn_roe + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_physician + pfemam,
+                opp_physician + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_physician_negative + pfemam,
+                opp_physician_negative + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_privacy + pfemam,
+                opp_privacy + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_standing + pfemam,
+                opp_standing + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_uncertainty + pfemam,
+                opp_uncertainty + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_undue_burden + pfemam,
+                opp_undue_burden + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_untruthful + pfemam,
+                opp_untruthful + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_womens_future_life + pfemam,
+                opp_womens_future_life + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_womens_health + pfemam,
+                opp_womens_health + poppam,
               family = binomial, data = data,  
@@
                 (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                fem_womens_rights + pfemam,
+                opp_womens_rights + poppam,
               family = binomial, data = data,  

### 2022-04-27 eda/capstone/capstone-report.Rmd
capstone pres update

@@
 library(ggpubr)
+#library(extrafont)
+#font_import()
+#loadfonts(device = "all")
+
+library(showtext)
+font_add_google(name = "Quattrocento Sans")
 
@@
 ```{r}
+# turn on showtext
+
+```
+
+```{r}
+showtext_auto()
 medauf_adj <- medauf %>% 
-  filter(label_correct != "none") %>% 
+  filter(label_correct != "none", label_correct != "Violence Against Abortion Seekers") %>%
+  mutate(Count = Count) %>% 
   ggplot(., aes(x=x, y=y, color=as.factor(label_correct), size=Count)) +
@@
   theme_minimal() +
-  guides(size = "none") +
+  guides(size = "none",
+         color=guide_legend(nrow=3, byrow=TRUE)) +
   labs(
     x = "Dimension 2", y = "Dimension 1",
-    title = "Adjusted Medical Org Arguments (pro)",
+    title = "Medical Organizations' Arguments (Proponents)",
     color = "Argument"
-  )
+  ) +
+  theme(legend.title=element_text(size=16, family = "Quattrocento Sans"),
+        legend.text=element_text(size=16, family = "Quattrocento Sans"),
+        legend.position="bottom", legend.direction="vertical",
+        title = element_text(size=14, family = "Quattrocento Sans"),
+        axis.text = element_text(size=12, family = "Quattrocento Sans"),
+        axis.title = element_text(size=12, family = "Quattrocento Sans"))
 medauf_adj
@@
 ```{r}
-ggsave("medauf_adj.png",medauf_adj,height = 4, width = 6)
+ggsave("medauf_adj.png",medauf_adj,height = 7, width = 9)
 ```

### 2022-05-02 data-cleaning/07-generate-frame-measures.Rmd
fix missing data

@@
 # abortion cases
-amicus <- box_read("947307207905", read_fun = readr::read_csv)
+amicus <- box_read("947307207905", read_fun = readr::read_csv) %>% 
+  mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))
 ```
@@
 ```
-```{r}
-sum_amicus %>% filter(case == "Anders v Floyd" | case == "Ayotte v. PP")
-```
 

### 2022-05-02 data-cleaning/08-create-regression-data.Rmd
fix missing data

@@
 ```
+Pared down for review:
+
+* women's frames (women's health, rights, future life, compulsory motherhood I and II, abortion regret)
+
+* law frames (bad law, undue burden, overturn roe, privacy, standing, final authority)
+
+* morality & religion
+
+* evidence frames (evidence, uncertainty, untruthful)
+
+```{r}
+final_pared <- final %>% 
+  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
+  select(case:cirsplit,
+         abortion_different,
+         abortion_regret, womens_health, womens_rights, womens_future_life,
+         compulsory_motherhood, compulsory_motherhood_ii,
+         bad_law, undue_burden, overturn_roe, privacy, standing, final_authority,
+         morality_religion,
+         evidence, uncertainty, untruthful) %>% 
+  filter(case != "Hartigan v Zbaraz") %>%
+  filter(!is.na(justicevot)) %>% 
+  select(-c(justiceid:justicefem)) %>% 
+  select(case, ddate2, nonftyp2:cirsplit, sort(colnames(.))) %>% 
+  distinct()
+```
+
+Save
+
+```{r}
+box_write(final,
+          file_name = "frame freq by case (pared).xlsx",
+          dir_id = 158993526875)
+```
 

### 2022-05-02 modeling/amicus_type/aclauo.Rmd
updates

@@
 ```{r}
-data <- box_read(full_cases) %>% 
+data <- box_read(amicus_only) %>% 
   filter(justicevot != "NA") %>% 
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(aclauo_abortion_different:aclauo_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, aclauo_abortion_different:aclauo_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('aclauo')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('aclauo')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.05:
-* 0.10:
+* 0.10: untruthful
 
@@
 
-```{r}
+```{r, eval=F}
 mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                1 + (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                 aclauo_abortion_different,
               family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+              nAGQ = 0)#, control=glmerControl(check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
 
@@
               family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+              nAGQ = 0)#, control=glmerControl(check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
 
@@
 
-```{r}
+```{r, eval=F}
 mod3 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod5 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod6a <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod6b <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod10 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod11 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod13 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod15 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod22 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod27 <- glmer(justicevot ~

### 2022-05-02 modeling/amicus_type/antauo.Rmd
updates

@@
          nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(antauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+  mutate(across(c(antauo_abortion_different:antauo_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
+data <- data %>%
   mutate(across(c(where(is.numeric), -justicevot, -id),
@@
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+data <- janitor::remove_empty(data, which = "cols")
 ```
@@
 * 0.01:
-* 0.05:
+* 0.05: bad law, intersectionality, uncertainty
 * 0.10:
@@
 
-```{r}
+```{r, eval=F}
 mod1 <- glmer(justicevot ~

### 2022-05-02 modeling/amicus_type/mpeauo.Rmd
updates

@@
 
-* 0: compulsory motherhood
+* 0: 
 * 0.01:
-* 0.05:
-* 0.10:
+* 0.05: morality/relig, women's future life (-), 
+* 0.10: state interest
 

### 2022-05-02 modeling/amicus_type/racauf.Rmd
updates

@@
 
-* 0: compulsory motherhood
+* 0: 
 * 0.01:
-* 0.05:
-* 0.10:
+* 0.05: untruthful
+* 0.10: protest, standing
 

### 2022-05-02 eda/abortion-cases-frames-plots.Rmd
misc

---
title: "abortion cases"
author: "Amanda Konet"
date: "`r date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
box_auth()
```

```{r}
df <- box_read("949904531983", read_fun = readr::read_csv)
```

# Abortion Negative II

```{r}
df %>% 
  select(case, ddate2, ) %>% 
  mutate(title = "Word/Phrase Count for Abortion Negative II Frame",
         year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, decision_date), y = anii_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Abortion Negative II Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# actor_couple

```{r}
dec_frames %>% 
  select(case, decision_date, ac_freq) %>% 
  mutate(title = "Word/Phrase Count for Actor Couple Frame",
         year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = ac_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Actor Couple Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# actor_fetus

```{r}
dec_frames %>% 
  select(case, decision_date, af_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = af_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Actor Fetus Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# actor_physician

```{r}
dec_frames %>% 
  select(case, decision_date, ap_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = ap_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Actor Physician Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# compulsoryII

```{r}
dec_frames %>% 
  select(case, decision_date, c2_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = c2_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Compulsory II Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# compulsoryMotherhood

```{r}
dec_frames %>% 
  select(case, decision_date, cm_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = cm_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Compulsory Motherhood Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# favorChildbirth

```{r}
dec_frames %>% 
  select(case, decision_date, fc_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = fc_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Favor Childbirth Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# health

```{r}
dec_frames %>% 
  select(case, decision_date, he_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = he_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Health Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# intersectionality

```{r}
dec_frames %>% 
  select(case, decision_date, in_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = in_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Intersectionality Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# morality

```{r}
dec_frames %>% 
  select(case, decision_date, mo_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = mo_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Morality Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# psy_harm

```{r}
dec_frames %>% 
  select(case, decision_date, ph_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = ph_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Psycological Harm Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

\newpage

# womanCitizenship

```{r}
dec_frames %>% 
  select(case, decision_date, wc_freq) %>% 
  mutate(year = lubridate::year(decision_date)) %>% 
  ggplot(., aes(x = reorder(case, year), y = wc_freq)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Case",
    y = "Frequency of frame words/phrases in decision (divided by total word count)",
    title = "Word/Phrase Count for Woman Citizenship Frame"
  ) + 
  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(
    # grid lines + background
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", size = 0.1),
    panel.border = element_blank(),
    plot.background = element_rect(color = "#eaeaea", size = 0.4),
    axis.line = element_line(color = "#eaeaea", size = 0.4),
    # facet format
    panel.spacing = unit(0, "pt"), 
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(color = "#afafaf", size = 7.4),
    # axis title
    axis.title = element_text(color = "#666666", size = 8),
    # axis text
    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
    axis.text.y = element_text(color = "darkgray", size = 7),
    # axis ticks
    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
    axis.ticks.y = element_blank(),
    # title
    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
  )
```

### 2022-05-02 eda/paper-graphics.Rmd
misc

---
title: "Paper Visualizations"
author: "Amanda Konet"
date: "`r date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
box_auth()

df <- box_read("949901868853", read_fun = readr::read_csv)
```

# Cases per Year

```{r}
num_cases <- df %>%  distinct(case, decision_date=ddate2) %>% 
  group_by(decision_date) %>% 
  summarize(n = n())

num_cases %>% 
  ggplot(., aes(x = decision_date, y = n)) +
  geom_line() + 
  labs(
    x = "Decision Year",
    y = "Count of Amici",
    title = "Number of Amici per Case"
  ) +
  theme_minimal()
```

# Number of Amici by Case

Data

```{r}
num_amici <- df %>% 
  distinct(year = lubridate::year(ddate2), cfemam, coppam) %>% 
  group_by(year) %>% 
  summarize(cfemam = mean(cfemam), coppam = mean(coppam))
```

Plot

```{r}
amici_ct_plt <- num_amici %>% 
  ggplot(., aes(x = year)) +
  geom_line(aes(y = cfemam, linetype = "Feminist")) + 
  geom_line(aes(y = coppam, linetype = "Opponent")) + 
  scale_linetype_manual("Party", values=c("Feminist" = 1,"Opponent" = 2)) + 
  coord_cartesian(ylim = c(0, 50)) +
  labs(
    x = "Decision Year",
    y = "Average Number of Amici",
    title = "Annual Average Number of Amici for Abortion Cases"
  ) + 
  theme_minimal() +
  theme(
    title = element_text(size = 10)
  )

amici_ct_plt
```
Check spike
```{r}
df %>% filter(lubridate::year(ddate2) == 1989) %>% distinct(case, ddate2, cfemam, coppam)
```

### 2022-05-02 modeling/fem-opp-evidence.Rmd
misc

---
title: "Fem and Opp Evidence Frames"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

#amicus_only <- "948366662469"
#full_cases <- "948832669583"
#frame_by_party <- "949813266093"
final_by_party <- "949904531983"
```

# Data

Frames: evidence, uncertainty, untruthful, undue burden after 1992

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_by_party) %>% 
  filter(justicevot != "NA") %>% 
  filter(lubridate::year(ddate2) > 1992) %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(fem_abortion_different:opp_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, poppam,
         contains("evidence"), contains("uncertainty"),
         contains("undue"), contains("untruthful")) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('fem')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('fem')) %>% colnames()
setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01: 
* 0.05: 
* 0.10: abortion different

\newpage

# Evidence (fem)

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                fem_evidence + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

# Uncertainty (fem)

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                fem_uncertainty + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden (fem)

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                fem_undue_burden + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful (fem)

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                fem_untruthful + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Evidence (opp)

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                opp_evidence + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

# Uncertainty (opp)

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                opp_uncertainty + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden (opp)

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                opp_undue_burden + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful (opp)

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem +
                opp_untruthful + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

### 2022-05-02 modeling/frame-parties-case.Rmd
misc

---
title: "Frames Across all Fem Author Types"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

#amicus_only <- "948366662469"
#full_cases <- "948832669583"
frame_by_party <- "949813266093"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(frame_by_party) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(fem_abortion_different:opp_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
normalize <- function(x, na.rm = TRUE) {
    return((x- min(x)) /(max(x)-min(x)))
}
data <- data %>%
  select(case:cirsplit, fem_abortion_different:opp_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                #~(scale(., center=T, scale=T))))
                ~normalize(.x)))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('fem')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('fem')) %>% colnames()
setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant:

* 0:
* 0.01: 
* 0.05: fem_abortion_different, fem_couple, fem_state_interest, opp_women's_future
* 0.10: opp_abortion_immoral, opp_equal_protection, fem_evidence, opp_privacy

\newpage

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_abortion_different + opp_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod1)
```

```{r, eval=F}
logit_prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
odds <- exp(-3.5029)
odds
odds / (1 + odds)
```

\newpage

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_abortion_immoral + opp_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

\newpage

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_anti_women + opp_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_bad_law + opp_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod4)
```

\newpage

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_bodily_integrity + opp_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

\newpage

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_compulsory_motherhood + opp_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6a)
```

\newpage

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_compulsory_motherhood_ii + opp_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod6b)
```

\newpage

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_couple + opp_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

\newpage

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_equal_protection + opp_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod9)
```

\newpage

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_favor_childbirth + opp_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_final_authority + opp_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod12)
```

\newpage

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_informed_consent + opp_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_intersectionality + opp_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_overturn_roe + opp_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod15)
```

\newpage

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_physician + opp_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

\newpage

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_physician_negative + opp_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod18)
```

\newpage

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_protesters + opp_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_standing + opp_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod20)
```

\newpage

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_state_interest + opp_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_uncertainty + opp_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_untruthful + opp_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod24)
```

\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod25)
```

\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                fem_womens_rights + opp_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod27)
```

### 2022-05-05 data-cleaning/09-scrape-litigant-text.Rmd
scrape litigant briefs

--- 2021-11-04 data-cleaning/00-scrape-amicus-text.Rmd
@@
 ---
-title: "Tidy Amicus Data"
-author: "Amanda Konet"
+title: "Litigant Framing Data"
+author: "Amanda Konet and Sarah Torrence"
 date: "`r Sys.Date()`"
@@
 
-There are ~40 folders in Amicus IV > data > amicus files.
-For each amicus file (denoted by files with "amicus" or "amici" in the file name), copy the file ID, file name, case name, and file text into a CSV.
+There are ~40 folders in Supreme Court > Sup Ct - Abortion Cases.
+For each amicus file (NOT denoted by files with "amicus”, “amici”, “decision”, “reply”, “appendix”, and “oral” in the file name), copy the file ID, file name, case name, and file text into a CSV.
 
@@
 
-Set working directory to amcius files folder
+Set working directory to  files folder
 
 ```{r}
-box_setwd("146066009084")
+box_setwd("6932017842")
 ```
@@
               i %>%
-                filter(grepl("amicus|amici", name, ignore.case = T)) %>%
+                filter(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T)) %>%
                 select(case, name, id)
             }
-  print("Obtained amicus file ids")
+  print("Obtained litigant file ids")
 
@@
 # run the function for Abortion and Sex Discrim folders
-amicus_file_ids <- all_file_names(case_folders)
+litigant_file_ids <- all_file_names(case_folders)
 
@@
 # save this file to data > processed amicus files
-amicus_file_ids %>% 
+litigant_file_ids %>% 
   right_join(., case_folders, "case") %>% 
   group_by(case) %>% 
-  summarize(n = sum(grepl("amicus|amici", name, ignore.case = T))) %>% 
+  summarize(n = sum(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T))) %>% 
   arrange(case) #%>% 
@@
 ```{r}
-amicus_file_ids %>% 
-  right_join(., case_folders, "case") %>% 
-  select(-id.y) %>% 
-  rename(id = id.x) %>% 
-  mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
-  box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
+# amicus_file_ids %>% 
+#   right_join(., case_folders, "case") %>% 
+#   select(-id.y) %>% 
+#   rename(id = id.x) %>% 
+#   mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
+#   box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
 ```
@@
 
-Obtain the raw text from each amicus brief. Note that we have two file types here: DOCX & PDF.
+Obtain the raw text from each amicus brief. Note that we have two file types here that we want: DOCX & PDF. All other duplicate folders and extra types can be filtered out.
 
@@
 ```{r}
-amicus_file_ids <- amicus_file_ids %>% 
+litigant_file_ids <- litigant_file_ids %>% 
   mutate(file_type = tolower(sub(".*\\.", "", name))) 
-amicus_file_ids %>% group_by(file_type) %>% summarize(n = n())
+litigant_file_ids %>% group_by(file_type) %>% summarize(n = n())
+```
+
+```{r}
+litigant_file_ids <- litigant_file_ids %>% filter(file_type == 'docx' | file_type == 'pdf')
 ```
@@
 # create iterator 
-itd <- iter(amicus_file_ids, by = "row")
+itd <- iter(litigant_file_ids, by = "row")
 
@@
   # grab text and concat to string
-  #txt <- box_read(
+  # txt <- box_read(
   #  file_id = id,
@@
   #    textreadr::read_document(x)
-  #)
+  # )
 
@@
 
+Check that our files contain "summary of (the) argument: this is the phrase that indicates the start of the text we want to analyze.
+
+```{r}
+# amicus_txt %>% 
+#   mutate(txt_full = str_squish(txt_full),
+#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
+#   group_by(summary) %>% 
+#   summarize(n=n())
+```
+
+Which files do not? -- should just be the 3 that we have manual adjustments recorded for.
+
+```{r}
+# amicus_txt %>% 
+#   mutate(txt_full = str_squish(txt_full),
+#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
+#   filter(!summary) %>% 
+#   select(brief)
+```
+
+Final column names
+
+```{r}
+amicus_txt %>% colnames()
+```
+
 # 3. Write file to Box
@@
 box_write(amicus_txt,
-          file_name = "shortened-amicus-brief-text.csv",
+          file_name = "raw-litigant-brief-text.csv",
           dir_id = '145990409196')

### 2022-05-09 eda/paper-graphics.Rmd
paper graphics

@@
 
+ggsave("graphics/avg_amici_time.png",amici_ct_plt, height = 5, width = 8)
 amici_ct_plt

### 2022-05-10 data-cleaning/00-scrape-amicus-text.Rmd
add litigant frames

@@
 case_folders %>% head(1)
+```
+
+If only getting specific folder, change here
+
+```{r}
+#case_folders <- case_folders %>% filter(case == "Gonzales v PP")
 ```
@@
 ```
+Scrape text
 
@@
 
+If adding in briefs, run below
+
+```{r}
+#full <- box_read("1029611016764")
+#full <- full %>% rbind(amicus_txt) %>% arrange(case)
+```
+
 # 3. Write file to Box

### 2022-05-10 data-cleaning/00b-scrape-litigant-text.Rmd
add litigant frames

--- 2022-05-05 data-cleaning/09-scrape-litigant-text.Rmd
@@
 There are ~40 folders in Supreme Court > Sup Ct - Abortion Cases.
-For each amicus file (NOT denoted by files with "amicus”, “amici”, “decision”, “reply”, “appendix”, and “oral” in the file name), copy the file ID, file name, case name, and file text into a CSV.
+For each litigant file (NOT denoted by files with "amicus”, “amici”, “decision”, “reply”, “appendix”, and “oral” in the file name), copy the file ID, file name, case name, and file text into a CSV.
 
@@
                 filter(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T)) %>%
-                select(case, name, id)
+                select(case, name, id, type)
             }
@@
   summarize(n = sum(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T))) %>% 
-  arrange(case) #%>% 
-  #box_write(., "amicus brief counts.xlsx", dir_id = "145990409196")
+  arrange(case)
 ```
 
-Save list of amicus file IDs on Box
+Save list of litigant file IDs on Box
 
 ```{r}
-# amicus_file_ids %>% 
+#litigant_file_ids %>% 
+  # only files
+#  filter(type == "file", name != ".DS_Store") %>% 
+  # add matching case
 #  right_join(., case_folders, "case") %>% 
-#   select(-id.y) %>% 
-#   rename(id = id.x) %>% 
+  # rename ids/type
+#  select(-id.y, -type.y) %>% 
+#  rename(id = id.x, type = type.x) %>% 
+  # name lower
 #  mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
-#   box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
+  # select final vars
+#  select(case, id, name, type) %>% 
+#  arrange(case) %>% 
+#  box_write(., "litigant-brief-file-ids.xlsx", dir_id = "162588272045")
 ```
@@
 ```
+Filter for only pdf and docx files
 
@@
 litigant_file_ids <- litigant_file_ids %>% filter(file_type == 'docx' | file_type == 'pdf')
+
+# filter for only briefs that need to be re-pulled
+litigant_file_ids <- litigant_file_ids %>% 
+  filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
 ```
+
+Read text
 
@@
 # get text of cases in parallel
-amicus_txt <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {
+litigant_txt <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {
 
@@
 
+Read in list of litigant file IDs, drop those that are marked "drop"
+
+```{r}
+drop_file_ids <- box_read("955323576728") %>% 
+  filter(drop == 1, !is.na(id)) %>% 
+  select(id)
+
+litigant_txt <- litigant_txt %>% filter(!(id %in% drop_file_ids$id))
+```
+
 Check that our files contain "summary of (the) argument: this is the phrase that indicates the start of the text we want to analyze.
@@
 ```{r}
-# amicus_txt %>% 
-#   mutate(txt_full = str_squish(txt_full),
-#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
-#   group_by(summary) %>% 
-#   summarize(n=n())
+litigant_txt %>% 
+   mutate(txt_full = str_squish(txt_full),
+          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
+   group_by(summary) %>% 
+   summarize(n=n())
 ```
 
-Which files do not? -- should just be the 3 that we have manual adjustments recorded for.
+Which files do not? -- should just be the 3 that we have manual adjustments recorded for. These have been manually changed/corrected.
 
 ```{r}
-# amicus_txt %>% 
-#   mutate(txt_full = str_squish(txt_full),
-#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
-#   filter(!summary) %>% 
-#   select(brief)
+ litigant_txt %>% 
+   mutate(txt_full = str_squish(txt_full),
+          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
+   filter(!summary) %>% 
+   select(brief)
 ```
 
-Final column names
+Add column for party
 
 ```{r}
-amicus_txt %>% colnames()
+litigant_txt <- litigant_txt %>% 
+  mutate(brief_party = ifelse(grepl("\\(feminist\\)", brief, ignore.case=T), 1, 0)) %>% 
+  select(case:id, brief_party, txt_full)
+```
+
+Check colnames 
+```{r}
+litigant_txt %>% colnames()
+```
+
+If adding cases adhoc, join now
+
+```{r}
+litigant_all <- box_read("955333134918") %>%
+  filter(!(brief %in% c("Bellotti v Baird (1976). Brief for Appellees (feminist).docx",
+                       "Colautti v. Franklin. Brief for Respondent (Feminist) - (labeled Beal v Franklin).pdf",
+                       "Doe v. Bolton Brief for Petitioners (Feminist).pdf",
+                       "Doe v. Bolton Brief for Respondents.pdf",
+                       "H.L. v Matheson. Brief for Appellant (feminist).docx",
+                       "United States v Vuitch. Brief for Appellant %28United States%29.docx",
+                       "United States v. Vuitch. Brief for Respondent (Feminist).pdf"))) %>% 
+  rbind(litigant_txt)
 ```
@@
 ```{r}
-box_write(amicus_txt,
+box_write(litigant_txt,
           file_name = "raw-litigant-brief-text.csv",
-          dir_id = '145990409196')
+          dir_id = '162588272045')
 ```

### 2022-05-10 data-cleaning/01b-shorten-litigant-text.Rmd
add litigant frames

--- 2022-01-26 data-cleaning/01-shorten-amicus-text.Rmd
@@
 ---
-title: "Shorten Amicus Text"
+title: "Shorten Litigant Text"
 author: "Sarah Torrence and Amanda Konet"
@@
 # data
-# data/processed amicus files/raw-amicus-brief-text.csv
-amicus <- box_read("863216279471")
-# data/processed amicus files/amicus summary.xlsx
-alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
-  select(case, brief, id, alternative) %>% 
-  filter(!is.na(alternative))
-#data/processed amicus files/footnotes-confirmed.csv
-footnotes_ids <- box_read("908607927934")
+# data/processed litigant files/raw-litigant-brief-text.csv
+litigant <- box_read("955333134918") %>% mutate(id = as.character(id))
 ```
@@
 
-To pare down amicus text by removing unnecessary/irrelevant text.
+To pare down litigant text by removing unnecessary/irrelevant text.
 
@@
 We don't need text prior to this, as it's mainly intro information about the case and/or the authors.
-If "summary of argument" text doesn't exist (only in the case of a few pdfs), use the `alternative_rmv` df to find where to start reading the text.
 
-alternate removal strings
-
-```{r}
-#alternate_rmv %>% select(id,alternative)
-```
-
-Remove text before summary of argument (already done in shortened-amicus-text csv, not raw text csv.)
+Remove text before summary of argument. Run 2x in the event of a table of contents.
 
@@
 # remove text after "summary of argument" if it exists
-amicus <- amicus %>%
+litigant <- litigant %>%
   mutate(txt_full = str_squish(txt_full),
          txt_short = case_when(
-           id == 861820795454 ~ gsub(pattern = ".*summary \\[\\*9\\] of the argument", replacement = "",
-                                     x = txt_full, ignore.case = TRUE),
-           grepl("summary of argument|Summary of Argument|SUMMARY OF ARGUMENT", txt_full,
-                 ignore.case = TRUE) ~
-             gsub(pattern = ".*summary of argument|.*Summary of Argument|.*SUMMARY OF ARGUMENT",
-                  replacement = "",
-                  x = txt_full, ignore.case = TRUE),
+           id %in% c(955404304453, 955405038378) ~ txt_full,
+           grepl("summary of argument", txt_full, ignore.case = TRUE) ~
+             gsub(pattern = ".*summary of argument",
+                  replacement = "", x = txt_full, ignore.case = TRUE),
            grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
-             gsub(pattern = ".*summary of the argument", replacement = "",
-                  x = txt_full, ignore.case = TRUE),
-           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "",
-                                     x = txt_full, ignore.case = TRUE),
-           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "",
-                                     x = txt_full, ignore.case = TRUE),
-           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "",
-                                     x = txt_full, ignore.case = TRUE),
-           T ~ ''),
+             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full, ignore.case = TRUE),
+           grepl("mnopqrst", txt_full, ignore.case = T) ~
+             gsub(pattern = ".*mnopqrst", replacement = "", x = txt_full, ignore.case = T),
+           T ~ txt_full),
          txt_short = str_squish(txt_short))
@@
 ```{r}
-amicus %>% filter(txt_short == "") %>% select(-txt_full)
+litigant %>% filter(txt_short == "") %>% select(-txt_full)
+#litigant %>% filter(txt_short == txt_full)
 ```
@@
 ```{r}
-#amicus %>% sample_n(1) %>% pull(txt_short)
+#litigant %>% sample_n(1) %>% pull(id, txt_short)
 ```
@@
 ```{r}
-amicus <- amicus %>%
+litigant <- litigant %>%
   mutate(txt_short = str_squish(txt_short),
@@
 ```{r}
-table(amicus$appendix_1a)
+table(litigant$appendix_1a)
 ```
@@
 ```{r}
-amicus <- amicus %>% mutate(
+litigant <- litigant %>% mutate(
          txt_short = str_squish(txt_short),
@@
 ```{r}
-a <- amicus %>%
+a <- litigant %>%
   mutate(appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix"))
@@
 ```{r}
-amicus$appendix_a <- ifelse(amicus$appendix_1a < 1, str_count(amicus$txt_short, "APPENDIX A"), 0)
+litigant$appendix_a <- ifelse(litigant$appendix_1a < 1, str_count(litigant$txt_short, "APPENDIX A"), 0)
 
-table(amicus$appendix_a)
+table(litigant$appendix_a)
 ```
 
-`APPENDIX A` occurs in 56 briefs that did not already have the appendix removed.
+`APPENDIX A` occurs in 2 briefs that did not already have the appendix removed.
 
@@
 ```{r}
-amicus %>% filter(appendix_a > 0) %>% select(id, appendix_a)
+litigant %>% filter(appendix_a > 0) %>% select(id, appendix_a)
 ```
@@
 ```{r}
-amicus <- amicus %>% mutate(
+litigant <- litigant %>% mutate(
          txt_short = case_when(
@@
 ```{r}
-a <- amicus %>% filter(appendix_1a == 0) %>%
+a <- litigant %>% filter(appendix_1a == 0) %>%
   mutate(appendix_a = str_count(txt_short, "APPENDIX A"))
@@
 ```{r}
-amicus$appendix <- ifelse(amicus$appendix_1a < 1 & amicus$appendix_a < 1, 
-                            str_count(amicus$txt_short, "APPENDIX"), 0)
+litigant$appendix <- ifelse(litigant$appendix_1a < 1 & litigant$appendix_a < 1, 
+                            str_count(litigant$txt_short, "APPENDIX"), 0)
 
-table(amicus$appendix)
+table(litigant$appendix)
 ```
 
-There are still 86 briefs that mention `APPENDIX`. We want to manually look at some of the briefs that mention `APPENDIX` to see if they refer to the beginning of the appendix
+We want to manually look at some of the briefs that mention `APPENDIX` to see if they refer to the beginning of the appendix. None mention appendix more than once, so we can skip below.
 
 ```{r}
-amicus %>% filter(appendix > 1) %>% select(id, appendix)
+litigant %>% filter(appendix > 1) %>% select(id, appendix)
 ```
@@
 ```{r}
-a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>%
+a <- litigant %>% filter(appendix_1a == 0 & appendix_a == 0) %>%
   mutate(appendix = str_count(txt_short, "APPENDIX"))
@@
 ```{r}
-a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>%
+a <- litigant %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>%
   mutate(Appendix = str_count(txt_short, "Appendix"),
@@
 ```{r}
-amicus <- amicus %>% mutate(txt_short = str_to_lower(txt_short))
+litigant <- litigant %>% mutate(txt_short = str_to_lower(txt_short))
 ```
@@
 ```{r}
-amicus <- amicus %>%
+litigant <- litigant %>%
   mutate(footnotes = str_count(txt_short, "footnotes"))
 
-table(amicus$footnotes)
+table(litigant$footnotes)
 ```
@@
 ```{r}
-amicus <- amicus %>%
-  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+litigant <- litigant %>%
+  mutate(footnotes_cor = str_count(txt_short, "footnotes \\* counsel of record"),
+         footnotes_cor2 = str_count(txt_short, "footnotes fn \\* counsel of record"),
          footnotes_1 = str_count(txt_short, "footnotes 1"))
 
-table(amicus$footnotes_cor)
+table(litigant$footnotes_cor)
+table(litigant$footnotes_cor2)
 ```
@@
 ```{r}
-table(amicus$footnotes_1)
+table(litigant$footnotes_1)
 ```
@@
 ```{r}
-amicus <- amicus %>% mutate(
+litigant <- litigant %>% mutate(
          txt_short = case_when(
-           grepl("footnotes counsel of record", txt_short)
-           & (id %in% footnotes_ids$id) ~ 
-             gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
-           grepl("footnotes 1", txt_short)
-           & (id %in% footnotes_ids$id | id == '861814132010') ~ 
+           grepl("footnotes \\* counsel of record", txt_short) ~ 
+             gsub(pattern = "footnotes \\* counsel of record.*", replacement = "", x = txt_short),
+            grepl("footnotes fn \\* counsel of record", txt_short) ~ 
+             gsub(pattern = "footnotes fn \\* counsel of record.*", replacement = "", x = txt_short),
+           grepl("footnotes 1", txt_short) ~ 
              gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
@@
 ```{r}
-a <- amicus %>%
+a <- litigant %>%
   mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+         footnotes_cor2 = str_count(txt_short, "footnotes \\* counsel of record"),
          footnotes_1 = str_count(txt_short, "footnotes 1"))
@@
 table(a$footnotes_cor)
+table(a$footnotes_cor2)
 ```
@@
 ```{r}
-amicus$footnotes_star <- ifelse(amicus$footnotes_cor < 1 & amicus$footnotes_1 < 1,
-                                str_count(amicus$txt_short, "footnotes \\*"), 0)
+litigant$footnotes_star <- ifelse(litigant$footnotes_cor < 1 & litigant$footnotes_1 < 1,
+                                str_count(litigant$txt_short, "footnotes \\*"), 0)
 
-table(amicus$footnotes_star)
+table(litigant$footnotes_star)
 ```
@@
 ```{r}
-a <- amicus %>%
+a <- litigant %>%
   mutate(footnotes_star = str_count(txt_short, "footnotes \\*"))
@@
 ```{r}
-a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
+a <- litigant %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
                         appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
@@
 ```{r}
-a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
+a <- litigant %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
    mutate(appendix_all = str_count(txt_short, "appendix"))
@@
 
-There are only 62 briefs remaining that mention an appendix that have not already had their appendix removed.
-
-```{r}
-#saving these ids to a csv
-appendix_not_removed <- a %>% filter(appendix_all > 0) %>% select(id)
-
-#box_write(appendix_not_removed,
-#          file_name = "appendix-not-removed.csv",
-#          dir_id = 145990409196)
-```
-
-Hoe many briefs had neither an appendix or footnotes removed?
-
-```{r}
-amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0 &
-                   footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0) %>% count()
-```
-253 briefs had neither an appendix or footnotes removed.
-
 Now we want to save the new shortened version of the text into a csv.
@@
 ```{r}
-#amicus <- amicus %>% select(case, brief, id, txt_short)
+ litigant <- litigant %>% select(case, brief, id, brief_party, txt_short)
 
-#box_write(amicus,
-#          file_name = "shortened-amicus-brief-text.csv",
-#          dir_id = 145990409196)
+ box_write(litigant,
+           file_name = "shortened-litigant-brief-text.csv",
+           dir_id = 162588272045)
 ```

### 2022-05-10 data-cleaning/05-add-amicus-measures.Rmd
add litigant frames

@@
 amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)
-# data/processed_amicus_files/amicus_clean_512_no_stride_split.csv
-#amicus <- box_read("946701865033")
+
 # data/processed_amicus_files/shortened_amicus_brief_text.csv

### 2022-05-10 data-cleaning/07b-generate-frame-measures-litigant.Rmd
add litigant frames

---
title: "Generate Frame Measures"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)
library(tidyverse)
library(tidytext)
library(textclean)
library(tm)
library(stringi)
library(quanteda)

library(boxr)
box_auth()
```

# Purpose

To develop litigant- and frame-level measures of frame usage

# Data

Abortion frame terms:

```{r}
frame_terms <- box_read("947335700912", read_fun = readr::read_csv)
```

Litigant data:

```{r}
# data/processed litigant files/clean-shortened-litigant-brief-text.csv
litigant <- box_read("955397555840") %>% 
  mutate(id = as.character(id)) %>% 
  mutate(brief_party = ifelse(id %in% c("955405762992", "199347141448", "56697932358", "296368043832"), 1, brief_party))
```

# Litigant-Level Measures

Start by creating corpus

```{r}
litigant_corp <- litigant$text_clean %>% corpus()

# Add meta data to corpus
docvars(litigant_corp, "case") <- litigant$case
docvars(litigant_corp, "brief") <- litigant$brief
docvars(litigant_corp, "id") <- litigant$id
docvars(litigant_corp, "brief_party") <- litigant$brief_party

summary(litigant_corp) %>% head()
```

## Create frame dictionary

This dictionary will be used to filter out frame words from paragraphs when counting word frequency.

```{r}
# Remove duplicates
frame_terms <- frame_terms %>%
  select(frame_code, word_clean) %>% 
  unique()

# Get words associated with frames
get_frames <- function(frame){ 
  frame_terms %>%
    filter(frame_code == frame) %>% 
    select(word_clean)
  }

# Initialize list
search_frames <- list()

# Get unique frames
frames <- unique(frame_terms$frame_code)

# Pull words for each frame and save in list
for(i in 1:length(frames)){ 
  search_frames[i] <- get_frames(frames[i])
}

# Name items in list
names(search_frames) <- frames

frame_dict <- dictionary(search_frames)

# Check output
#frame_dict
```

# Look up frames

**Note on arguments in `tokens()` function**: removing punctuation and numbers from terms increases counts.

```{r}
# Tokenize briefs
toks <- tokens(litigant_corp, remove_punct = TRUE, remove_numbers = TRUE)
```

## Create brief summary statistics

The `litigant_corp_summary` data frame contains the summary statistics of all the briefs in our corpus, `litigant_corp`. The one thing it's missing is the number of tokens (i.e. words) in each brief.

```{r}
# Generate summary of litigantCorp
litigant_corp_summary <- summary(object = litigant_corp, 
                      n = nrow(litigant), # default is 100, we need all observations 
                      showmeta = TRUE) %>% # add meta data to summary
  as.data.frame()

# check
tail(litigant_corp_summary)
```

Calculate total number of words in each brief. Join with the litigant_corp_summary

```{r}
# Total number of tokens (before pulling frame words)
nToks <- data.frame(Text = names(ntoken(toks)), 
                     word_ct = ntoken(toks))

# Look at first 6 observations
head(nToks)
```

```{r}
litigant_info <- litigant_corp_summary %>%
  left_join(nToks, by = c("Text")) %>% 
  rename(doc_id=Text)

head(litigant_info)
```

## Generate frame frequencies

Now that we've created our `litigant_info` data frame, it's time to generate the frame frequencies.

(# of words/phrases for a particular frame) / (# of all words in the brief)

```{r}
# Search for frames
litigant_dfm <- tokens_lookup(toks, dictionary = frame_dict, nested_scope = "dictionary",
                         case_insensitive = FALSE, valuetype = "fixed") %>% dfm()

# Generate raw frequencies
litigant_frames_raw <- litigant_dfm %>%
  convert(to = "data.frame") %>%
  left_join(litigant_info, by = "doc_id") %>% 
  janitor::clean_names()

# Check out first 6 observations 
head(litigant_frames_raw, 10)
```

Get frame frequencies - These are calculated by dividing the frame count by the word count.

```{r}
# Generate frame frequencies 
litigant_frames_freq <- litigant_frames_raw %>% 
  pivot_longer(c(abortion_different:womens_rights),
               names_to = "frame", values_to = "frame_ct") %>% 
  mutate(frame_freq = frame_ct/word_ct) %>% 
  select(-frame_ct, -word_ct) %>% 
  pivot_wider(names_from = "frame", values_from = frame_freq)

litigant_frames_freq %>% head(10)
```

## Raw counts + freq

Dataframe with raw counts and frequencies

```{r}
litigant_frames <- litigant_frames_raw %>% 
  select(doc_id:womens_rights, word_ct) %>% 
  left_join(., litigant_frames_freq, 
            by = c("doc_id"), 
            suffix = c("_raw", "_freq")) %>% 
  select(-c(types:sentences)) %>% 
  select(case:brief_party, word_ct, sort(colnames(.))) %>% 
  janitor::clean_names()

litigant_frames %>% head(10)
```

Save

```{r}
box_write(litigant_frames,
           file_name = "litigant-level-frame-measures.csv",
           dir_id = 162601154573)
```

# Case-Level Measures

We already have case-level measures. Just reorganize data for one row per case

```{r}
fem_frames <- litigant_frames %>% filter(brief_party == 1) %>% 
  rename_with(., .fn = ~ paste0("fem_", .x), contains("freq")|contains("raw")) %>% 
  select(case, contains("fem"))
opp_frames <- litigant_frames %>% filter(brief_party == 0) %>% 
  rename_with(., .fn = ~ paste0("opp_", .x), contains("freq")|contains("raw")) %>% 
  select(case, contains("opp"))

case_frames <- fem_frames %>% full_join(., opp_frames, by = "case")
```

Save

```{r}
box_write(case_frames,
           file_name = "case-level-frame-measures.csv",
           dir_id = 162601154573)
```

### 2022-05-10 data-cleaning/08-create-regression-data.Rmd
add litigant frames

@@
 
+# amici frames
 case_amici_level <- box_read("947450386335")
+
+# litigant frames (already one row per case)
+litigant_case_level <- box_read("955507061348") %>%
+  select(case, contains("freq")) %>% 
+  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x))
+
+# justice level data
 justice_level <- box_read("947810760828")
@@
 
-To create regression data for Amicus IV. The dependent variable is justicevot. The controls are: justicemq, justicefem, nonftyp2, lcdisdirfem. The independent vars are the framing measures.
+To create regression data for Amicus IV. The dependent variable is justicevot. The controls are: justicemq, justicefem, nonftyp2, lcdisdirfem, . The independent vars are the framing measures.
 
@@
   select(case = casename, ddate2,
-         justiceid, justicevot, justicemq, justicefem,
+         justiceid, justicevot, justicemq, justicefem, sgfem3,
          nonftyp2, lcdisdirfem, cirsplit,
@@
 
+litigant_case_level <- litigant_case_level %>% 
+  mutate(case = str_replace(case, 'v\\.', 'v'),
+         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
+         case = case_when(
+           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
+           case == "Ayotte v Planned Parenthood of Northern New England" ~ "Ayotte v PP",
+           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
+           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
+           case == "Hill et al v Colorado" ~ "Hill v Colorado",
+           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
+           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
+           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
+           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
+             "PP v Ashcroft",
+           case == "Planned Parenthood of Southeastern Pennsylvania v Casey" ~ "PP v Casey",
+           case == "Planned Parenthood of Central MO v Danforth" ~ "PP v Danforth",
+           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
+           case == "Joseph Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
+           case == "Schenck et al v Pro-Choice Network of Western NY" ~
+             "Schenck v Pro-Choice Network",
+           case == "Thornburgh v American College of Obstetricians and Gynecologists LDEF" ~
+             "Thornburgh v American College of OBGYNs",
+           case == "Whole Womens Health v Hellerstedt 2016" ~ "WWH v Hellerstedt",
+           T ~ case
+         ))
+
 case_level <- case_level %>% 
@@
   left_join(., case_level, by = "case") %>% 
+  left_join(., litigant_case_level, by = "case") %>% 
   select(case, ddate2:poppam, everything())

### 2022-05-10 data-cleaning/00-scrape-amicus-text.Rmd
add missing amicus + lit briefs

--- 2022-01-25 data-cleaning/00-scrape-amicus-text.Rmd
@@
 
+If only getting specific folder, change here
+
+```{r}
+#case_folders <- case_folders %>% filter(case == "Gonzales v PP")
+```
+
 For all of the folders, retrieve every file name and ID.
@@
 
-# run the function for Abortion and Sex Discrim folders
+# run the function for Abortion folders
 amicus_file_ids <- all_file_names(case_folders)
@@
 ```
+
+If only need to scrape briefs ad hoc, filter now
+
+```{r}
+amicus_file_ids <- amicus_file_ids %>% filter(id == "861822172835")
+```
+
+Scrape text
 
@@
 
+If adding in briefs, run below
+
+```{r}
+full <- box_read("863216279471")
+full <- full %>% rbind(amicus_txt) %>% arrange(case)
+```
+
 # 3. Write file to Box
@@
 ```{r}
-box_write(amicus_txt,
+box_write(full,
           file_name = "raw-amicus-brief-text.csv",

### 2022-05-10 data-cleaning/00b-scrape-litigant-text.Rmd
add missing amicus + lit briefs

@@
 
-Set working directory to  files folder
+Set working directory to litigant/amicus files folder
 
 ```{r}
-box_setwd("6932017842")
+box_setwd("146066009084")
 ```
@@
 litigant_file_ids <- litigant_file_ids %>% 
-  filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
+  #filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
+  filter(id == "861821337076")
 ```
@@
 litigant_all <- box_read("955333134918") %>%
-  filter(!(brief %in% c("Bellotti v Baird (1976). Brief for Appellees (feminist).docx",
-                       "Colautti v. Franklin. Brief for Respondent (Feminist) - (labeled Beal v Franklin).pdf",
-                       "Doe v. Bolton Brief for Petitioners (Feminist).pdf",
-                       "Doe v. Bolton Brief for Respondents.pdf",
-                       "H.L. v Matheson. Brief for Appellant (feminist).docx",
-                       "United States v Vuitch. Brief for Appellant %28United States%29.docx",
-                       "United States v. Vuitch. Brief for Respondent (Feminist).pdf"))) %>% 
+  #filter(!(brief %in% c("Bellotti v Baird (1976). Brief for Appellees (feminist).docx",
+  #                     "Colautti v. Franklin. Brief for Respondent (Feminist) - (labeled Beal v Franklin).pdf",
+  #                     "Doe v. Bolton Brief for Petitioners (Feminist).pdf",
+  #                     "Doe v. Bolton Brief for Respondents.pdf",
+  #                     "H.L. v Matheson. Brief for Appellant (feminist).docx",
+  #                     "United States v Vuitch. Brief for Appellant %28United States%29.docx",
+  #                     "United States v. Vuitch. Brief for Respondent (Feminist).pdf"))) %>% 
   rbind(litigant_txt)
@@
 ```{r}
-box_write(litigant_txt,
+box_write(litigant_all,
           file_name = "raw-litigant-brief-text.csv",

### 2022-05-10 data-cleaning/01-shorten-amicus-text.Rmd
add missing amicus + lit briefs

@@
 #data/processed amicus files/footnotes-confirmed.csv
-footnotes_ids <- box_read("908607927934")
+footnotes_ids <- box_read("908607927934") %>% rbind(861822172835)
 ```
@@
   mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+         footnotes_cor2 = str_count(txt_short, "footnotes \\* counsel of record"),
+         footnotes_cor3 = str_count(txt_short, "footnotes \\* fn counsel of record"),
          footnotes_1 = str_count(txt_short, "footnotes 1"))
@@
 ```{r}
-table(amicus$footnotes_1)
+table(amicus$footnotes_cor2)
+table(amicus$footnotes_cor3)
 ```
@@
          txt_short = case_when(
-           grepl("footnotes counsel of record", txt_short)
-           & (id %in% footnotes_ids$id) ~ 
+           grepl("footnotes \\* counsel of record", txt_short) ~ 
+             gsub(pattern = "footnotes \\* counsel of record.*", replacement = "", x = txt_short),
+           grepl("footnotes counsel of record", txt_short) ~ 
              gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
-           grepl("footnotes 1", txt_short)
-           & (id %in% footnotes_ids$id | id == '861814132010') ~ 
+           grepl("footnotes fn \\* counsel of record", txt_short) ~ 
+             gsub(pattern = "footnotes fn \\* counsel of record.*", replacement = "", x = txt_short),
+           grepl("footnotes 1", txt_short)  ~ 
              gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
@@
 a <- amicus %>%
-  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
+  mutate(footnotes_cor = str_count(txt_short, "footnotes \\* counsel of record"),
+         footnotes_fn_cor = str_count(txt_short, "footnotes fn \\* counsel of record"),
          footnotes_1 = str_count(txt_short, "footnotes 1"))
@@
 table(a$footnotes_1)
-```
-
-```{r}
 table(a$footnotes_cor)
+table(a$footnotes_fn_cor)
 ```
@@
 ```{r}
-# amicus <- amicus %>% select(case, brief, id, txt_short)
+ amicus <- amicus %>% select(case, brief, id, txt_short)
 # 
-# box_write(amicus,
-#           file_name = "shortened-amicus-brief-text.csv",
-#           dir_id = 145990409196)
+ box_write(amicus,
+           file_name = "shortened-amicus-brief-text.csv",
+           dir_id = 145990409196)
 ```

### 2022-05-10 data-cleaning/05-add-amicus-measures.Rmd
add missing amicus + lit briefs

@@
 # data/processed amicus files/amicus_clean_512_no_stride.csv
-amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)
+amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party) %>% 
+  mutate(id = as.character(id))
 
 # data/processed_amicus_files/shortened_amicus_brief_text.csv
-amicus <- box_read("910635411098")
+amicus <- box_read("910635411098") %>% mutate(id = as.character(id))
 
 # data/processed amicus files/walkover_brief_names.csv
-walkover <- box_read("941154488137")
+walkover <- box_read("941154488137") %>% mutate(new_id = as.character(new_id))
 ```
@@
 brief_info <- brief_info %>%
-  mutate(Case = ifelse(is.na(Case), "999999", Case))
+  mutate(Case = ifelse(is.na(Case), "999999", Case)) %>% 
+  mutate(`Amicus Brief` = ifelse(`Amicus Brief` == "Stenberg v Carhart. Amics Brief for Petitioner by Agudath Israel of America.docx",
+                                 "Stenberg v Carhart. Amicus Brief for Petitioner by Agudath Israel of America.docx",
+                                 `Amicus Brief`))
 
@@
 walk_measures <- walkover %>%
-  left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))
+  left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id")) %>% 
+  mutate(new_id = ifelse(old_id == "592236091833", "861822172835", new_id),
+         name_correct = ifelse(old_id == "592236091833", "Stenberg v Carhart. Amicus Brief for Petitioner by Agudath Israel of America.docx", name_correct))
 
@@
 ```{r}
-amicus <- amicus %>% left_join(., amicus_party, by = "id")
+amicus <- amicus %>% left_join(., amicus_party, by = "id") %>% 
+  mutate(brief_party = ifelse(id == "861822172835", 0, brief_party))
 ```

### 2022-05-10 data-cleaning/00b-scrape-litigant-text.Rmd
anders

@@
   #filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
-  filter(id == "861821337076")
+  #filter(id == "861821337076")
+  filter(id == "955826247752")
 ```
@@
   mutate(brief_party = ifelse(grepl("\\(feminist\\)", brief, ignore.case=T), 1, 0)) %>% 
+  mutate(brief_party = ifelse(id %in% c("955405762992", "199347141448", "56697932358", "296368043832"), 1, brief_party)) %>% 
   select(case:id, brief_party, txt_full)

### 2022-05-15 modeling/amicus_type/forgauf.Rmd
rm nonftyp

@@
 ---
-title: "Forgauf Amicus Brief Models"
+title: "forgauf Amicus Brief Models"
 author: "Amanda Konet"
@@
 library(lme4)
+library(boxr)
 library(kableExtra)
 library(broom.mixed)
-library(boxr)
 box_auth()
@@
          lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(forgauf_abortion_different:forgauf_womens_rights), ~replace_na(.x, 0)))
-```
+  mutate(across(c(forgauf_abortion_different:forgauf_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
   select(case:cirsplit, pfemam, forgauf_abortion_different:forgauf_womens_rights) %>%  
-  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                 ~(scale(., center=T, scale=T))))
@@
 remaining_cols <- data %>% select(contains('forgauf')) %>% colnames()
-setdiff(total_cols, remaining_cols)
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.01:
-* 0.05: standing
-* 0.10: women's health
-* 0.20: abortion different, bad law, morality and religion
-
-\newpage
-
-# Abortion different
-
-```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_abortion_different + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod1)
-```
+* 0.05: 
+* 0.10: health (-), standing (+)
+* 0.20: bad law (+), morality & religion (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_abortion_regret + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                forgauf_abortion_regret,
               family = binomial, data = data,  
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_bad_law + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_bad_law,
               family = binomial, data = data,  
@@
 
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_compulsory_motherhood + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_compulsory_motherhood_ii + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6b)
-```
-
-\newpage
-
 # Evidence
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_evidence + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_evidence,
               family = binomial, data = data,  
@@
 
+\newpage
+
+# Fetus
+
+```{r}
+mod11 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_fetus,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod11)
+```
+
+\newpage
+
 # Final Authority
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_final_authority + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                forgauf_final_authority,
               family = binomial, data = data,  
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_morality_religion + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_morality_religion,
               family = binomial, data = data,  
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_overturn_roe + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                forgauf_overturn_roe,
               family = binomial, data = data,  
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_privacy + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_privacy,
               family = binomial, data = data,  
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_standing + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                forgauf_standing,
               family = binomial, data = data,  
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_uncertainty + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_uncertainty,
               family = binomial, data = data,  
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_undue_burden + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_undue_burden,
               family = binomial, data = data,  
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_untruthful + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_untruthful,
               family = binomial, data = data,  
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_womens_future_life + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                forgauf_womens_future_life,
               family = binomial, data = data,  
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_womens_health + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_womens_health,
               family = binomial, data = data,  
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                forgauf_womens_rights + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                forgauf_womens_rights,
               family = binomial, data = data,  

### 2022-05-15 modeling/amicus_type/legauf.Rmd
rm nonftyp

@@
 ---
-title: "Legauf Amicus Brief Models"
+title: "legauf Amicus Brief Models"
 author: "Amanda Konet"
@@
 library(boxr)
+library(kableExtra)
+library(broom.mixed)
 box_auth()
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(legauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
-```
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(legauf_abortion_different:legauf_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
 data <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+  select(case:cirsplit, pfemam, legauf_abortion_different:legauf_womens_rights) %>%  
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
+total_cols <- data %>% select(contains('legauf')) %>% colnames()
 data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('legauf')) %>% colnames()
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.10:
+* 0.20:
 
@@
 
-# Abortion different
+# Abortion Regret
 
-```{r, eval=F}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_abortion_different,
+```{r}
+mod3 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                legauf_abortion_regret,
               family = binomial, data = data,  
@@
 
-summary(mod1)
-```
-
-\newpage
-
-# Abortion Immoral
-
-```{r}
-mod2 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_abortion_immoral,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_bad_law,
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
-```
-
-\newpage
-
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_compulsory_motherhood,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_compulsory_motherhood_ii,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_evidence,
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
-```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
 ```
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_fetus,
@@
                 check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 legauf_final_authority,
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 legauf_overturn_roe,
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_privacy,
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 legauf_standing,
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauf_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 legauf_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_womens_rights,

### 2022-05-15 modeling/amicus_type/legauo.Rmd
rm nonftyp

@@
 ---
-title: "Legauo Amicus Brief Models"
+title: "legauo Amicus Brief Models"
 author: "Amanda Konet"
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(legauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
-```
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(legauo_abortion_different:legauo_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
 data <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+  select(case:cirsplit, poppam, legauo_abortion_different:legauo_womens_rights) %>%  
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
+total_cols <- data %>% select(contains('legauo')) %>% colnames()
 data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('legauo')) %>% colnames()
+#setdiff(total_cols, remaining_cols)
 ```
@@
 
-# Abortion different
+# Abortion Regret
 
 ```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_abortion_different,
+mod3 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                legauo_abortion_regret,
               family = binomial, data = data,  
@@
 
-summary(mod1)
-```
-
-\newpage
-
-# Abortion Immoral
-
-```{r}
-mod2 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_abortion_immoral,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_bad_law,
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
-```
-
-\newpage
-
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_compulsory_motherhood,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_compulsory_motherhood_ii,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_evidence,
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
-```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
 ```
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                 legauo_final_authority,
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                 legauo_overturn_roe,
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_privacy,
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                 legauo_standing,
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                legauo_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                 legauo_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_womens_rights,

### 2022-05-15 modeling/amicus_type/lifauo.Rmd
rm nonftyp

@@
 ---
-title: "Lifauo Amicus Brief Models"
+title: "lifauo Amicus Brief Models"
 author: "Amanda Konet"
@@
          lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(lifauo_abortion_different:lifauo_womens_rights), ~replace_na(.x, 0)))
-```
+  mutate(across(c(lifauo_abortion_different:lifauo_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
   select(case:cirsplit, poppam, lifauo_abortion_different:lifauo_womens_rights) %>%  
-  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                 ~(scale(., center=T, scale=T))))
@@
 remaining_cols <- data %>% select(contains('lifauo')) %>% colnames()
-setdiff(total_cols, remaining_cols)
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.05: 
-* 0.10: final authority, privacy
-
-\newpage
-
-# Abortion different
-
-```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_abortion_different + poppam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod1)
-```
+* 0.10: final authority (+)
+* 0.20: privacy (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_abortion_regret + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                lifauo_abortion_regret,
               family = binomial, data = data,  
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_bad_law + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_bad_law,
               family = binomial, data = data,  
@@
 
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_compulsory_motherhood + poppam,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_compulsory_motherhood_ii + poppam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6b)
-```
-
-\newpage
-
 # Evidence
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_evidence + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_evidence,
               family = binomial, data = data,  
@@
 
+\newpage
+
+# Fetus
+
+```{r}
+mod11 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_fetus,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod11)
+```
+
+\newpage
+
 # Final Authority
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_final_authority + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                lifauo_final_authority,
               family = binomial, data = data,  
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_morality_religion + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_morality_religion,
               family = binomial, data = data,  
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_overturn_roe + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                lifauo_overturn_roe,
               family = binomial, data = data,  
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_privacy + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_privacy,
               family = binomial, data = data,  
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_standing + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                lifauo_standing,
               family = binomial, data = data,  
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_uncertainty + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_uncertainty,
               family = binomial, data = data,  
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_undue_burden + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_undue_burden,
               family = binomial, data = data,  
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_untruthful + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_untruthful,
               family = binomial, data = data,  
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_womens_future_life + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                lifauo_womens_future_life,
               family = binomial, data = data,  
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_womens_health + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_womens_health,
               family = binomial, data = data,  
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                lifauo_womens_rights + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                lifauo_womens_rights,
               family = binomial, data = data,  

### 2022-05-15 modeling/amicus_type/medauf.Rmd
rm nonftyp

@@
          lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(medauf_abortion_different:medauf_womens_rights), ~replace_na(.x, 0)))
-```
+  mutate(across(c(medauf_abortion_different:medauf_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
   select(case:cirsplit, pfemam, medauf_abortion_different:medauf_womens_rights) %>%  
-  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                 ~(scale(., center=T, scale=T))))
@@
 * 0.01:
-* 0.05: women's future life
-* 0.10: abortion different, bad law
-* 0.20: standing
-
-\newpage
-
-# Abortion different
-
-```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_abortion_different + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod1)
-```
+* 0.05: women's future life (-)
+* 0.10: standing (+)
+* 0.20: bad law (+), fetus (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_abortion_regret + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                medauf_abortion_regret,
               family = binomial, data = data,  
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_bad_law + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_bad_law,
               family = binomial, data = data,  
@@
 
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_compulsory_motherhood + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_compulsory_motherhood_ii + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6b)
-```
-
-\newpage
-
 # Evidence
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_evidence + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_evidence,
               family = binomial, data = data,  
@@
 
+\newpage
+
+# Fetus
+
+```{r}
+mod11 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_fetus,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod11)
+```
+
+\newpage
+
 # Final Authority
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_final_authority + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                medauf_final_authority,
               family = binomial, data = data,  
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_morality_religion + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_morality_religion,
               family = binomial, data = data,  
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_overturn_roe + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                medauf_overturn_roe,
               family = binomial, data = data,  
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_privacy + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_privacy,
               family = binomial, data = data,  
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_standing + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                medauf_standing,
               family = binomial, data = data,  
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_uncertainty + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_uncertainty,
               family = binomial, data = data,  
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_undue_burden + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_undue_burden,
               family = binomial, data = data,  
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_untruthful + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_untruthful,
               family = binomial, data = data,  
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_womens_future_life + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                medauf_womens_future_life,
               family = binomial, data = data,  
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_womens_health + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_womens_health,
               family = binomial, data = data,  
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauf_womens_rights + pfemam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                medauf_womens_rights,
               family = binomial, data = data,  

### 2022-05-15 modeling/amicus_type/medauo.Rmd
rm nonftyp

@@
 ---
-title: "Medauo Amicus Brief Models"
+title: "medauo Amicus Brief Models"
 author: "Amanda Konet"
@@
          lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(medauo_abortion_different:medauo_womens_rights), ~replace_na(.x, 0)))
-```
+  mutate(across(c(medauo_abortion_different:medauo_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
   select(case:cirsplit, poppam, medauo_abortion_different:medauo_womens_rights) %>%  
-  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                 ~(scale(., center=T, scale=T))))
@@
 remaining_cols <- data %>% select(contains('medauo')) %>% colnames()
-setdiff(total_cols, remaining_cols)
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0:
-* 0.01
-* 0.05: morality/relig, protest
-* 0.10: abortion regret
-* 0.20: compulsory motherhood, undue burden, women's health
-
-\newpage
-
-# Abortion different
-
-```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_abortion_different + poppam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod1)
-```
+* 0.01:
+* 0.05: morality & religion (-)
+* 0.10: abortion regret (+)
+* 0.20: undue burden (-), women's health (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_abortion_regret + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                medauo_abortion_regret,
               family = binomial, data = data,  
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_bad_law + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_bad_law,
               family = binomial, data = data,  
@@
 
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_compulsory_motherhood + poppam,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_compulsory_motherhood_ii + poppam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6b)
-```
-
-\newpage
-
 # Evidence
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_evidence + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_evidence,
               family = binomial, data = data,  
@@
 
+\newpage
+
+# Fetus
+
+```{r}
+mod11 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_fetus,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod11)
+```
+
+\newpage
+
 # Final Authority
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_final_authority + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                medauo_final_authority,
               family = binomial, data = data,  
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_morality_religion + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_morality_religion,
               family = binomial, data = data,  
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_overturn_roe + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                medauo_overturn_roe,
               family = binomial, data = data,  
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_privacy + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_privacy,
               family = binomial, data = data,  
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_standing + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                medauo_standing,
               family = binomial, data = data,  
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_uncertainty + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_uncertainty,
               family = binomial, data = data,  
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_undue_burden + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_undue_burden,
               family = binomial, data = data,  
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_untruthful + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_untruthful,
               family = binomial, data = data,  
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_womens_future_life + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                medauo_womens_future_life,
               family = binomial, data = data,  
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_womens_health + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_womens_health,
               family = binomial, data = data,  
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                medauo_womens_rights + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                medauo_womens_rights,
               family = binomial, data = data,  

### 2022-05-15 modeling/amicus_type/relauf.Rmd
rm nonftyp

@@
 ---
-title: "Relauf Amicus Brief Models"
+title: "relauf Amicus Brief Models"
 author: "Amanda Konet"
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
-```
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(relauf_abortion_different:relauf_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, pfemam, relauf_abortion_different:relauf_womens_rights) %>%  
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('relauf')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('relauf')) %>% colnames()
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.05: 
-* 0.10: privacy
+* 0.10: 
+* 0.20: privacy (+)
 
@@
 
-# Abortion different
+# Abortion Regret
 
 ```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_abortion_different,
+mod3 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                relauf_abortion_regret,
               family = binomial, data = data,  
@@
 
-summary(mod1)
-```
-
-\newpage
-
-# Abortion Immoral
-
-```{r}
-mod2 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_abortion_immoral,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod2)
-```
-
-\newpage
-
-# Anti-Women
-
-```{r}
-mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_anti_women,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
 
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_bad_law,
@@
 
+tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod4)
-```
-
-\newpage
-
-# Bodily Integrity
-
-```{r}
-mod5 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_bodily_integrity,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod5)
-```
-
-\newpage
-
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_compulsory_motherhood,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_compulsory_motherhood_ii,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod6b)
-```
-
-\newpage
-
-# Couple
-
-```{r}
-mod7 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_couple,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod7)
-```
-
-\newpage
-
-# Eql Protection
-
-```{r}
-mod8 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_equal_protection,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod8)
 ```
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_evidence,
@@
 
+tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod9)
-```
-
-\newpage
-
-# Favor Childbirth
-
-```{r}
-mod10 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_favor_childbirth,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod10)
 ```
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 relauf_final_authority,
@@
 
+tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod12)
-```
-
-\newpage
-
-# Informed Consent
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_informed_consent,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
-```
-
-\newpage
-
-# Intersectionality
-
-```{r}
-mod13 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_intersectionality,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod13)
 ```
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 relauf_overturn_roe,
@@
 
+tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod15)
-```
-
-\newpage
-
-# Physician
-
-```{r}
-mod16 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_physician,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod16)
-```
-
-\newpage
-
-# Physician Negative
-
-```{r}
-mod17 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_physician_negative,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod17)
 ```
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_privacy,
@@
 
+tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod18)
-```
-
-\newpage
-
-# Protesters
-
-```{r}
-mod19 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_protesters,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod19)
 ```
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 relauf_standing,
@@
 
+tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
 summary(mod20)
-```
-
-\newpage
-
-# State Interest
-
-```{r}
-mod21 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauf_state_interest,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-summary(mod21)
 ```
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                 relauf_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_womens_rights,

### 2022-05-15 modeling/amicus_type/relauo.Rmd
rm nonftyp

@@
 ---
-title: "Relauo Amicus Brief Models"
+title: "relauo Amicus Brief Models"
 author: "Amanda Konet"
@@
          lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0)))
-```
+  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
   select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>%  
-  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                 ~(scale(., center=T, scale=T))))
@@
 remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
-setdiff(total_cols, remaining_cols)
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0.01:
-* 0.05: abortion regret
-* 0.10: evidence
-* 0.20: bad law, compulsory motherhood, women's health
-
-\newpage
-
-# Abortion different
-
-```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_abortion_different + poppam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod1)
-```
+* 0.05: abortion regret (+)
+* 0.10: evidence (+)
+* 0.20: bad law (+), women's health (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_abortion_regret + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                relauo_abortion_regret,
               family = binomial, data = data,  
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_bad_law + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_bad_law,
               family = binomial, data = data,  
@@
 
-# Comp Motherhood
-
-```{r}
-mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_compulsory_motherhood + poppam,
-              family = binomial, data = data,  
-              nAGQ = 1, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6a)
-```
-
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
-mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_compulsory_motherhood_ii + poppam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod6b)
-```
-
-\newpage
-
 # Evidence
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_evidence + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_evidence,
               family = binomial, data = data,  
@@
 
+\newpage
+
+# Fetus
+
+```{r}
+mod11 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_fetus,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod11)
+```
+
+\newpage
+
 # Final Authority
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_final_authority + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                relauo_final_authority,
               family = binomial, data = data,  
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_morality_religion + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_morality_religion,
               family = binomial, data = data,  
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_overturn_roe + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                relauo_overturn_roe,
               family = binomial, data = data,  
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_privacy + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_privacy,
               family = binomial, data = data,  
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_standing + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                relauo_standing,
               family = binomial, data = data,  
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_uncertainty + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_uncertainty,
               family = binomial, data = data,  
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_undue_burden + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_undue_burden,
               family = binomial, data = data,  
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_untruthful + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_untruthful,
               family = binomial, data = data,  
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_future_life + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                relauo_womens_future_life,
               family = binomial, data = data,  
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_health + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_womens_health,
               family = binomial, data = data,  
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                relauo_womens_rights + poppam,
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                relauo_womens_rights,
               family = binomial, data = data,  

### 2022-05-15 modeling/justicemq-interactions/chcauf.Rmd
ideology interactions

---
title: "chcauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(chcauf_abortion_different:chcauf_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, chcauf_abortion_different:chcauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('chcauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('chcauf')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_abortion_regret + chcauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = chcauf_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_abortion_regret = as.factor(chcauf_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_bad_law + chcauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = chcauf_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_bad_law", mod = mod4)
ef <- effect(term="justicemq:chcauf_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(chcauf_bad_law = as.factor(chcauf_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = chcauf_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_evidence + chcauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = chcauf_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_evidence = as.factor(chcauf_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_fetus + chcauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = chcauf_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_fetus = as.factor(chcauf_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_final_authority + chcauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = chcauf_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_final_authority = as.factor(chcauf_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_morality_religion + chcauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = chcauf_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_morality_religion = as.factor(chcauf_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_overturn_roe + chcauf_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = chcauf_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_overturn_roe = as.factor(chcauf_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_privacy + chcauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = chcauf_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_privacy = as.factor(chcauf_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_standing + chcauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = chcauf_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_standing = as.factor(chcauf_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_uncertainty + chcauf_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = chcauf_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_uncertainty = as.factor(chcauf_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_undue_burden + chcauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = chcauf_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_undue_burden = as.factor(chcauf_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_untruthful + chcauf_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = chcauf_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_untruthful = as.factor(chcauf_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_womens_future_life + chcauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = chcauf_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_womens_future_life = as.factor(chcauf_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_womens_health + chcauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = chcauf_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_womens_health = as.factor(chcauf_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                chcauf_womens_rights + chcauf_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = chcauf_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:chcauf_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(chcauf_womens_rights = as.factor(chcauf_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = chcauf_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = chcauf_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=chcauf_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/forgauf.Rmd
ideology interactions

---
title: "forgauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(forgauf_abortion_different:forgauf_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, forgauf_abortion_different:forgauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('forgauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('forgauf')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_abortion_regret + forgauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = forgauf_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_abortion_regret = as.factor(forgauf_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_bad_law + forgauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = forgauf_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_bad_law", mod = mod4)
ef <- effect(term="justicemq:forgauf_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(forgauf_bad_law = as.factor(forgauf_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = forgauf_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_evidence + forgauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = forgauf_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_evidence = as.factor(forgauf_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_fetus + forgauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = forgauf_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_fetus = as.factor(forgauf_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_final_authority + forgauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = forgauf_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_final_authority = as.factor(forgauf_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_morality_religion + forgauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = forgauf_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_morality_religion = as.factor(forgauf_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_overturn_roe + forgauf_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = forgauf_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_overturn_roe = as.factor(forgauf_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_privacy + forgauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = forgauf_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_privacy = as.factor(forgauf_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_standing + forgauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = forgauf_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_standing = as.factor(forgauf_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_uncertainty + forgauf_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = forgauf_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_uncertainty = as.factor(forgauf_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_undue_burden + forgauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = forgauf_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_undue_burden = as.factor(forgauf_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_untruthful + forgauf_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = forgauf_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_untruthful = as.factor(forgauf_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_future_life + forgauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = forgauf_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_womens_future_life = as.factor(forgauf_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_health + forgauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = forgauf_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_womens_health = as.factor(forgauf_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_rights + forgauf_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = forgauf_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:forgauf_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(forgauf_womens_rights = as.factor(forgauf_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = forgauf_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/legauf.Rmd
ideology interactions

---
title: "legauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(legauf_abortion_different:legauf_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, legauf_abortion_different:legauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('legauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('legauf')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_abortion_regret + legauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = legauf_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_abortion_regret = as.factor(legauf_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_bad_law + legauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = legauf_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_bad_law", mod = mod4)
ef <- effect(term="justicemq:legauf_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(legauf_bad_law = as.factor(legauf_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = legauf_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_evidence + legauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = legauf_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_evidence = as.factor(legauf_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_fetus + legauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = legauf_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_fetus = as.factor(legauf_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_final_authority + legauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = legauf_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_final_authority = as.factor(legauf_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_morality_religion + legauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = legauf_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_morality_religion = as.factor(legauf_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_overturn_roe + legauf_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = legauf_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_overturn_roe = as.factor(legauf_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_privacy + legauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = legauf_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_privacy = as.factor(legauf_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_standing + legauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = legauf_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_standing = as.factor(legauf_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_uncertainty + legauf_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = legauf_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_uncertainty = as.factor(legauf_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_undue_burden + legauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = legauf_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_undue_burden = as.factor(legauf_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_untruthful + legauf_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = legauf_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_untruthful = as.factor(legauf_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_future_life + legauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = legauf_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_womens_future_life = as.factor(legauf_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_health + legauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = legauf_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_womens_health = as.factor(legauf_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_rights + legauf_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = legauf_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauf_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauf_womens_rights = as.factor(legauf_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauf_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/legauo.Rmd
ideology interactions

---
title: "legauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(legauo_abortion_different:legauo_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, poppam, legauo_abortion_different:legauo_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('legauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('legauo')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_abortion_regret + legauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = legauo_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_abortion_regret = as.factor(legauo_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_bad_law + legauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = legauo_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_bad_law", mod = mod4)
ef <- effect(term="justicemq:legauo_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(legauo_bad_law = as.factor(legauo_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = legauo_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_evidence + legauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = legauo_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_evidence = as.factor(legauo_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_fetus + legauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = legauo_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_fetus = as.factor(legauo_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_final_authority + legauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = legauo_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_final_authority = as.factor(legauo_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_morality_religion + legauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = legauo_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_morality_religion = as.factor(legauo_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_overturn_roe + legauo_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = legauo_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_overturn_roe = as.factor(legauo_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_privacy + legauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = legauo_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_privacy = as.factor(legauo_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_standing + legauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = legauo_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_standing = as.factor(legauo_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_uncertainty + legauo_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = legauo_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_uncertainty = as.factor(legauo_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_undue_burden + legauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = legauo_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_undue_burden = as.factor(legauo_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_untruthful + legauo_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = legauo_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_untruthful = as.factor(legauo_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_future_life + legauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = legauo_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_womens_future_life = as.factor(legauo_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_health + legauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = legauo_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_womens_health = as.factor(legauo_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_rights + legauo_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = legauo_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:legauo_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(legauo_womens_rights = as.factor(legauo_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = legauo_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/lifauo.Rmd
ideology interactions

---
title: "lifauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(lifauo_abortion_different:lifauo_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, poppam, lifauo_abortion_different:lifauo_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('lifauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('lifauo')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_abortion_regret + lifauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = lifauo_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_abortion_regret = as.factor(lifauo_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_bad_law + lifauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = lifauo_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_bad_law", mod = mod4)
ef <- effect(term="justicemq:lifauo_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(lifauo_bad_law = as.factor(lifauo_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = lifauo_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_evidence + lifauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = lifauo_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_evidence = as.factor(lifauo_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_fetus + lifauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = lifauo_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_fetus = as.factor(lifauo_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_final_authority + lifauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = lifauo_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_final_authority = as.factor(lifauo_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_morality_religion + lifauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = lifauo_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_morality_religion = as.factor(lifauo_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_overturn_roe + lifauo_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = lifauo_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_overturn_roe = as.factor(lifauo_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_privacy + lifauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = lifauo_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_privacy = as.factor(lifauo_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_standing + lifauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = lifauo_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_standing = as.factor(lifauo_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_uncertainty + lifauo_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = lifauo_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_uncertainty = as.factor(lifauo_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_undue_burden + lifauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = lifauo_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_undue_burden = as.factor(lifauo_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_untruthful + lifauo_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = lifauo_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_untruthful = as.factor(lifauo_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_womens_future_life + lifauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = lifauo_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_womens_future_life = as.factor(lifauo_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_womens_health + lifauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = lifauo_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_womens_health = as.factor(lifauo_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                lifauo_womens_rights + lifauo_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = lifauo_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:lifauo_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(lifauo_womens_rights = as.factor(lifauo_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = lifauo_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/medauf.Rmd
ideology interactions

---
title: "medauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(medauf_abortion_different:medauf_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, medauf_abortion_different:medauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('medauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('medauf')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_abortion_regret + medauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = medauf_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_abortion_regret = as.factor(medauf_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_bad_law + medauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = medauf_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_bad_law", mod = mod4)
ef <- effect(term="justicemq:medauf_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(medauf_bad_law = as.factor(medauf_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = medauf_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_evidence + medauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = medauf_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_evidence = as.factor(medauf_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_fetus + medauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = medauf_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_fetus = as.factor(medauf_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_final_authority + medauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = medauf_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_final_authority = as.factor(medauf_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_morality_religion + medauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = medauf_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_morality_religion = as.factor(medauf_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_overturn_roe + medauf_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = medauf_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_overturn_roe = as.factor(medauf_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_privacy + medauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = medauf_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_privacy = as.factor(medauf_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_standing + medauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = medauf_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_standing = as.factor(medauf_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_uncertainty + medauf_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = medauf_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_uncertainty = as.factor(medauf_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_undue_burden + medauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = medauf_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_undue_burden = as.factor(medauf_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_untruthful + medauf_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = medauf_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_untruthful = as.factor(medauf_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_womens_future_life + medauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = medauf_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_womens_future_life = as.factor(medauf_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_womens_health + medauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = medauf_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_womens_health = as.factor(medauf_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                medauf_womens_rights + medauf_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = medauf_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauf_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauf_womens_rights = as.factor(medauf_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauf_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/medauo.Rmd
ideology interactions

---
title: "medauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(medauo_abortion_different:medauo_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, poppam, medauo_abortion_different:medauo_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('medauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('medauo')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_abortion_regret + medauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = medauo_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_abortion_regret = as.factor(medauo_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_bad_law + medauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = medauo_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_bad_law", mod = mod4)
ef <- effect(term="justicemq:medauo_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(medauo_bad_law = as.factor(medauo_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = medauo_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_evidence + medauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = medauo_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_evidence = as.factor(medauo_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_fetus + medauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = medauo_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_fetus = as.factor(medauo_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_final_authority + medauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = medauo_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_final_authority = as.factor(medauo_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_morality_religion + medauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = medauo_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_morality_religion = as.factor(medauo_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_overturn_roe + medauo_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = medauo_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_overturn_roe = as.factor(medauo_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_privacy + medauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = medauo_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_privacy = as.factor(medauo_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_standing + medauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = medauo_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_standing = as.factor(medauo_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_uncertainty + medauo_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = medauo_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_uncertainty = as.factor(medauo_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_undue_burden + medauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = medauo_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_undue_burden = as.factor(medauo_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_untruthful + medauo_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = medauo_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_untruthful = as.factor(medauo_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_womens_future_life + medauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = medauo_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_womens_future_life = as.factor(medauo_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_womens_health + medauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = medauo_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_womens_health = as.factor(medauo_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                medauo_womens_rights + medauo_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = medauo_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:medauo_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(medauo_womens_rights = as.factor(medauo_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = medauo_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/relauf.Rmd
ideology interactions

---
title: "relauf Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(relauf_abortion_different:relauf_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, relauf_abortion_different:relauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('relauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('relauf')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_abortion_regret + relauf_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = relauf_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_abortion_regret = as.factor(relauf_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_bad_law + relauf_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = relauf_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_bad_law", mod = mod4)
ef <- effect(term="justicemq:relauf_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(relauf_bad_law = as.factor(relauf_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = relauf_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_evidence + relauf_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = relauf_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_evidence = as.factor(relauf_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_fetus + relauf_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = relauf_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_fetus = as.factor(relauf_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_final_authority + relauf_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = relauf_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_final_authority = as.factor(relauf_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_morality_religion + relauf_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = relauf_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_morality_religion = as.factor(relauf_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_overturn_roe + relauf_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = relauf_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_overturn_roe = as.factor(relauf_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_privacy + relauf_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = relauf_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_privacy = as.factor(relauf_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_standing + relauf_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = relauf_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_standing = as.factor(relauf_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_uncertainty + relauf_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = relauf_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_uncertainty = as.factor(relauf_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_undue_burden + relauf_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = relauf_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_undue_burden = as.factor(relauf_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_untruthful + relauf_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = relauf_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_untruthful = as.factor(relauf_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_womens_future_life + relauf_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = relauf_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_womens_future_life = as.factor(relauf_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_womens_health + relauf_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = relauf_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_womens_health = as.factor(relauf_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                relauf_womens_rights + relauf_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = relauf_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauf_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauf_womens_rights = as.factor(relauf_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauf_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/justicemq-interactions/relauo.Rmd
ideology interactions

---
title: "relauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

library(tidyverse)
library(lme4)
library(kableExtra)
library(broom.mixed)
library(ggplot2)
library(effects)
library(interactions)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
final_cases <- "949901868853"
```

# Data

Filter out instances where we don't have the dependent variable, justicevot. Change data types where necessary. Fill in NAs for frame freq with 0s

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #justicemq = cut(justicemq, breaks = c(-8, -2, 2, 5), labels = c("lib", "mod", "consv"),
         #               include.lowest = T, right = F),
         #justicemq = ifelse(justicemq >= 0, 0, 1),
         #justicemq = as.factor(justicemq),
         cirsplit = as.factor(cirsplit)) %>%
  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

justicemq_conv <- data %>% select(orig = justicemq) %>% 
  mutate(scaled = scale(orig)) %>%
  arrange(scaled)
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

# Scale Data

Remove cols where all values are NA. Not sure if we will do this or not in models.

```{r}
data <- data %>%
  select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('relauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

```{r, eval=F}
# Full List of Frames

_abortion_different +
_abortion_immoral +
_anti_women +
_bad_law + 
_bodily_integrity + 
_compulsory_motherhood +   
_compulsory_motherhoood_ii +
_couple +
_equal_protection +
_evidence  +
_favor_childbirth +
_fetus +
_final_authority +
_informed_consent +
_intersectionality +
_morality_religion +
_overturn_roe  +
_physician +
_physician_negative +
_privacy  +
_protesters +               
_standing +
_state_interest +
_uncertainty +
_undue_burden +
_untruthful +
_womens_future_life + 
_womens_health + 
womens_rights
```

# Significance

The following frames are significant: (see excel)

* 0:
* 0.01
* 0.05: 
* 0.10: 
* 0.20:

\newpage

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_abortion_regret + relauo_abortion_regret:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod3, pred = relauo_abortion_regret, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              #interval = T,
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_abortion_regret", mod = mod3)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_abortion_regret = as.factor(relauo_abortion_regret))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_abortion_regret))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_abortion_regret))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_abortion_regret),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod3)
```

\newpage

# Bad Law

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_bad_law + relauo_bad_law:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod4, pred = relauo_bad_law, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_bad_law", mod = mod4)
ef <- effect(term="justicemq:relauo_bad_law", xlevels = list(justicemq=c(-4,-1,1,4)) ,mod = mod4)  #used this in paper

# as dataframe
#ef_df <-as.data.frame(ef) %>% mutate(relauo_bad_law = as.factor(relauo_bad_law))
ef_df <-as.data.frame(ef) %>% mutate(justicemq = as.factor(justicemq))

#By Color 
ggplot(ef_df, aes(x = relauo_bad_law, y= fit, group = justicemq))+
  geom_point()+
  geom_line(size = 1, aes(linetype = justicemq))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=justicemq),alpha=0.5) + 
  labs(title = "Frequency of Bad Law Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod4)
```

\newpage

# Evidence

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_evidence + relauo_evidence:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod9, pred = relauo_evidence, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_evidence", mod = mod9)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_evidence = as.factor(relauo_evidence))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_evidence))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_evidence))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_evidence),alpha=0.5) + 
  labs(title = "Frequency of Evidence Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod9)
```

\newpage

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_fetus + relauo_fetus:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod11, pred = relauo_fetus, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_fetus", mod = mod11)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_fetus = as.factor(relauo_fetus))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_fetus))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_fetus))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_fetus),alpha=0.5) + 
  labs(title = "Frequency of Fetus Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod11)
```

\newpage

# Final Authority

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_final_authority + relauo_final_authority:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod12, pred = relauo_final_authority, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_final_authority", mod = mod12)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_final_authority = as.factor(relauo_final_authority))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_final_authority))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_final_authority))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_final_authority),alpha=0.5) + 
  labs(title = "Frequency of Final Authority Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod12)
```
\newpage

# Morality Religion

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_morality_religion + relauo_morality_religion:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod14, pred = relauo_morality_religion, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_morality_religion", mod = mod14)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_morality_religion = as.factor(relauo_morality_religion))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_morality_religion))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_morality_religion))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_morality_religion),alpha=0.5) + 
  labs(title = "Frequency of Morality & Religion Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod14)
```

\newpage

# Overturn Roe

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_overturn_roe + relauo_overturn_roe:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod15, pred = relauo_overturn_roe, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_overturn_roe", mod = mod15)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_overturn_roe = as.factor(relauo_overturn_roe))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_overturn_roe))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_overturn_roe))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_overturn_roe),alpha=0.5) + 
  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod15)
```

\newpage

# Privacy

```{r}
mod18 <- glmer(justicevot ~
               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_privacy + relauo_privacy:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod18, pred = relauo_privacy, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_privacy", mod = mod18)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_privacy = as.factor(relauo_privacy))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_privacy))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_privacy))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_privacy),alpha=0.5) + 
  labs(title = "Frequency of Privacy Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod18)
```

\newpage

# Standing

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_standing + relauo_standing:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod20, pred = relauo_standing, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_standing", mod = mod20)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_standing = as.factor(relauo_standing))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_standing))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_standing))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_standing),alpha=0.5) + 
  labs(title = "Frequency of Standing Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod20)
```

\newpage

# Uncertainty

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_uncertainty + relauo_uncertainty:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod22, pred = relauo_uncertainty, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_uncertainty", mod = mod22)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_uncertainty = as.factor(relauo_uncertainty))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_uncertainty))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_uncertainty))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_uncertainty),alpha=0.5) + 
  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod22)
```

\newpage

# Undue Burden

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_undue_burden + relauo_undue_burden:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod23, pred = relauo_undue_burden, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_undue_burden", mod = mod23)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_undue_burden = as.factor(relauo_undue_burden))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_undue_burden))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_undue_burden))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_undue_burden),alpha=0.5) + 
  labs(title = "Frequency of Undue Burden Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod23)
```

\newpage

# Untruthful

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_untruthful + relauo_untruthful:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod24, pred = relauo_untruthful, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_untruthful", mod = mod24)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_untruthful = as.factor(relauo_untruthful))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_untruthful))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_untruthful))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_untruthful),alpha=0.5) + 
  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod24)
```
\newpage

# Women's Future Life

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_future_life + relauo_womens_future_life:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod25, pred = relauo_womens_future_life, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_womens_future_life", mod = mod25)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_womens_future_life = as.factor(relauo_womens_future_life))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_womens_future_life))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_womens_future_life))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_womens_future_life),alpha=0.5) + 
  labs(title = "Frequency of Abortion Regret Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod25)
```
\newpage

# Women's Health

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_health + relauo_womens_health:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

```

<br>

```{r}
interact_plot(mod26, pred = relauo_womens_health, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_womens_health", mod = mod26)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_womens_health = as.factor(relauo_womens_health))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_womens_health))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_womens_health))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_womens_health),alpha=0.5) + 
  labs(title = "Frequency of Women's Health Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod26)
```

\newpage

# Women's Rights

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_rights + relauo_womens_rights:justicemq,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
```

<br>

```{r}
interact_plot(mod27, pred = relauo_womens_rights, modx = justicemq,
              #modx.values = c(-3.5, -1, 0, 1, 3.5),
              # random
              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
              # quantiles
              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
              #outcome.scale = "link",
              x.label = "Frame Frequency",
              y.label = "Probability of Voting in Favor of Repro. Rights")
```

```{r, eval=F}
# interaction levels
ef <- effect(term="justicemq:relauo_womens_rights", mod = mod27)
#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper

# as dataframe
ef_df <-as.data.frame(ef) %>% mutate(relauo_womens_rights = as.factor(relauo_womens_rights))

#By Color 
ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_womens_rights))+
  geom_point()+
  geom_line(size = 1, aes(linetype = relauo_womens_rights))+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_womens_rights),alpha=0.5) + 
  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
       x= "Liberal                        Justice Ideology                         Conservative",
       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
  guides(fill=guide_legend(reverse=T))+
  guides(linetype=guide_legend(reverse=T))+
  theme_bw() +
  #scale_fill_grey()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill="Frame Frequency",
       linetype="Frame Frequency")
```

\newpage

```{r}
summary(mod27)
```

### 2022-05-15 modeling/base-models.Rmd
add base w/o nonftyp2

@@
          nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 ```
@@
 
-# Base Model (lcdisdirfem)
+# Base Model 0 (w/ lcdisdirfem)
 
@@
 base_mod <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem,
+                (1|id) + justicemq + justicefem + lcdisdirfem,
               family = binomial, data = data,  
@@
 calc_ICC(base_mod)
+```
+
+# Base Model 1 (w/ nonftyp2 & lcdisdirfem)
+
+(1 | group) + predictors = random intercept for each level in the group
+(0 | group) + predictors = fixed intercept 
+(1 | group) + (1 | predictor) + predictors = random intercept and random slope for predictor. the remaining predictors are fixed.
+
+Here, we use justicevot ~ (1 | id) + predictors.
+This means we want a random intercept that changes for each justice.
+The formula would be: $$justicevot_{ij} = \beta_{0j} + \beta_1(justicemq_{ij}) +...+\epsilon_{ij}$$
+
+with $$\beta_{0j} = \gamma_{00} + \mu_{0j}$$
+and this equation, but one $$\beta_1 = \gamma_{10}$$
+
+```{r}
+base_mod_1 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem,
+              family = binomial, data = data,  
+              nAGQ = 1, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+summary(base_mod_1)
+```
+
+ICC for base model
+
+```{r}
+calc_ICC(base_mod_1)
 ```

### 2022-05-16 modeling/justicemq-interactions/forgauf.Rmd
random effects interactions

@@
 ---
-title: "forgauf Amicus Brief Models"
+title: "Forgauf Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_abortion_regret + forgauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_bad_law + forgauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_evidence + forgauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_fetus + forgauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_final_authority + forgauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_morality_religion + forgauf_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                forgauf_overturn_roe + forgauf_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = forgauf_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:forgauf_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(forgauf_overturn_roe = as.factor(forgauf_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = forgauf_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_privacy + forgauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_standing + forgauf_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                forgauf_uncertainty + forgauf_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = forgauf_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:forgauf_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(forgauf_uncertainty = as.factor(forgauf_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = forgauf_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_undue_burden + forgauf_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                forgauf_untruthful + forgauf_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = forgauf_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:forgauf_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(forgauf_untruthful = as.factor(forgauf_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = forgauf_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_womens_future_life + forgauf_womens_future_life:justicemq,
@@
 ```
+
 \newpage
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 forgauf_womens_health + forgauf_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                forgauf_womens_rights + forgauf_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = forgauf_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:forgauf_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(forgauf_womens_rights = as.factor(forgauf_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = forgauf_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = forgauf_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=forgauf_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/legauf.Rmd
random effects interactions

@@
 ---
-title: "legauf Amicus Brief Models"
+title: "Legauf Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_abortion_regret + legauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_bad_law + legauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_evidence + legauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_fetus + legauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_final_authority + legauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_morality_religion + legauf_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                legauf_overturn_roe + legauf_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = legauf_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauf_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauf_overturn_roe = as.factor(legauf_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauf_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_privacy + legauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_standing + legauf_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                legauf_uncertainty + legauf_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = legauf_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauf_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauf_uncertainty = as.factor(legauf_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauf_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_undue_burden + legauf_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                legauf_untruthful + legauf_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = legauf_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauf_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauf_untruthful = as.factor(legauf_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauf_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_womens_future_life + legauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 legauf_womens_health + legauf_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                legauf_womens_rights + legauf_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = legauf_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauf_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauf_womens_rights = as.factor(legauf_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauf_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauf_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauf_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/legauo.Rmd
random effects interactions

@@
 ---
-title: "legauo Amicus Brief Models"
+title: "Legauo Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_abortion_regret + legauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_bad_law + legauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_evidence + legauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_fetus + legauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_final_authority + legauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_morality_religion + legauo_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                legauo_overturn_roe + legauo_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = legauo_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauo_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauo_overturn_roe = as.factor(legauo_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauo_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_privacy + legauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_standing + legauo_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                legauo_uncertainty + legauo_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = legauo_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauo_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauo_uncertainty = as.factor(legauo_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauo_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_undue_burden + legauo_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                legauo_untruthful + legauo_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = legauo_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauo_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauo_untruthful = as.factor(legauo_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauo_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_womens_future_life + legauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 legauo_womens_health + legauo_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                legauo_womens_rights + legauo_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = legauo_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:legauo_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(legauo_womens_rights = as.factor(legauo_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = legauo_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = legauo_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=legauo_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/lifauo.Rmd
random effects interactions

@@
 ---
-title: "lifauo Amicus Brief Models"
+title: "Lifauo Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_abortion_regret + lifauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_bad_law + lifauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_evidence + lifauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_fetus + lifauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_final_authority + lifauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_morality_religion + lifauo_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                lifauo_overturn_roe + lifauo_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = lifauo_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:lifauo_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(lifauo_overturn_roe = as.factor(lifauo_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = lifauo_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_privacy + lifauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_standing + lifauo_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                lifauo_uncertainty + lifauo_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = lifauo_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:lifauo_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(lifauo_uncertainty = as.factor(lifauo_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = lifauo_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_undue_burden + lifauo_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                lifauo_untruthful + lifauo_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = lifauo_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:lifauo_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(lifauo_untruthful = as.factor(lifauo_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = lifauo_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_womens_future_life + lifauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 lifauo_womens_health + lifauo_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                lifauo_womens_rights + lifauo_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = lifauo_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:lifauo_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(lifauo_womens_rights = as.factor(lifauo_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = lifauo_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = lifauo_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=lifauo_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/medauf.Rmd
random effects interactions

@@
 ---
-title: "medauf Amicus Brief Models"
+title: "Medauf Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_abortion_regret + medauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_bad_law + medauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_evidence + medauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_fetus + medauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_final_authority + medauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_morality_religion + medauf_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                medauf_overturn_roe + medauf_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = medauf_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauf_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauf_overturn_roe = as.factor(medauf_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauf_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_privacy + medauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_standing + medauf_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                medauf_uncertainty + medauf_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = medauf_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauf_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauf_uncertainty = as.factor(medauf_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauf_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_undue_burden + medauf_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                medauf_untruthful + medauf_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = medauf_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauf_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauf_untruthful = as.factor(medauf_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauf_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_womens_future_life + medauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 medauf_womens_health + medauf_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                medauf_womens_rights + medauf_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = medauf_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauf_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauf_womens_rights = as.factor(medauf_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauf_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauf_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauf_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/medauo.Rmd
random effects interactions

@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_abortion_regret + medauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_bad_law + medauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_evidence + medauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_fetus + medauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_final_authority + medauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_morality_religion + medauo_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                medauo_overturn_roe + medauo_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = medauo_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauo_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauo_overturn_roe = as.factor(medauo_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauo_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_privacy + medauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_standing + medauo_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                medauo_uncertainty + medauo_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = medauo_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauo_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauo_uncertainty = as.factor(medauo_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauo_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_undue_burden + medauo_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                medauo_untruthful + medauo_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = medauo_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauo_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauo_untruthful = as.factor(medauo_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauo_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_womens_future_life + medauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 medauo_womens_health + medauo_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                medauo_womens_rights + medauo_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = medauo_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:medauo_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(medauo_womens_rights = as.factor(medauo_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = medauo_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = medauo_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=medauo_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/relauf.Rmd
random effects interactions

@@
 ---
-title: "relauf Amicus Brief Models"
+title: "Relauf Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_abortion_regret + relauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_bad_law + relauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_evidence + relauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_fetus + relauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_final_authority + relauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_morality_religion + relauf_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                relauf_overturn_roe + relauf_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = relauf_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauf_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauf_overturn_roe = as.factor(relauf_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauf_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_privacy + relauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_standing + relauf_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                relauf_uncertainty + relauf_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = relauf_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauf_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauf_uncertainty = as.factor(relauf_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauf_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_undue_burden + relauf_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                relauf_untruthful + relauf_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = relauf_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauf_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauf_untruthful = as.factor(relauf_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauf_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_womens_future_life + relauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                 relauf_womens_health + relauf_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
-                relauf_womens_rights + relauf_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = relauf_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauf_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauf_womens_rights = as.factor(relauf_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauf_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauf_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauf_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/justicemq-interactions/relauo.Rmd
random effects interactions

@@
 ---
-title: "relauo Amicus Brief Models"
+title: "Relauo Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_abortion_regret + relauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_bad_law + relauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_evidence + relauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_fetus + relauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_final_authority + relauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_morality_religion + relauo_morality_religion:justicemq,
@@
 
-# Overturn Roe
-
-```{r}
-mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                relauo_overturn_roe + relauo_overturn_roe:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod15, pred = relauo_overturn_roe, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauo_overturn_roe", mod = mod15)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauo_overturn_roe = as.factor(relauo_overturn_roe))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_overturn_roe))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauo_overturn_roe))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_overturn_roe),alpha=0.5) + 
-  labs(title = "Frequency of Overturn Roe Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod15)
-```
-
-\newpage
-
 # Privacy
@@
 mod18 <- glmer(justicevot ~
-               (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_privacy + relauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_standing + relauo_standing:justicemq,
@@
 
-# Uncertainty
-
-```{r}
-mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                relauo_uncertainty + relauo_uncertainty:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod22, pred = relauo_uncertainty, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauo_uncertainty", mod = mod22)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauo_uncertainty = as.factor(relauo_uncertainty))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_uncertainty))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauo_uncertainty))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_uncertainty),alpha=0.5) + 
-  labs(title = "Frequency of Uncertainty Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod22)
-```
-
-\newpage
-
 # Undue Burden
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_undue_burden + relauo_undue_burden:justicemq,
@@
 
-# Untruthful
-
-```{r}
-mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                relauo_untruthful + relauo_untruthful:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-```
-
-<br>
-
-```{r}
-interact_plot(mod24, pred = relauo_untruthful, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauo_untruthful", mod = mod24)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauo_untruthful = as.factor(relauo_untruthful))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_untruthful))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauo_untruthful))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_untruthful),alpha=0.5) + 
-  labs(title = "Frequency of Untruthful Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod24)
-```
-\newpage
-
 # Women's Future Life
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_womens_future_life + relauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                 relauo_womens_health + relauo_womens_health:justicemq,
@@
 ```
-
-\newpage
-
-# Women's Rights
-
-```{r}
-mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
-                relauo_womens_rights + relauo_womens_rights:justicemq,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-```
-
-<br>
-
-```{r}
-interact_plot(mod27, pred = relauo_womens_rights, modx = justicemq,
-              #modx.values = c(-3.5, -1, 0, 1, 3.5),
-              # random
-              #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
-              # quantiles
-              modx.values = c(-3.4, -.75, -.3, .59, 1.9),
-              modx.labels = c("More Liberal", "Moderately Liberal","Moderate", "Moderately Conservative", "More Conservative"),
-              colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
-              #outcome.scale = "link",
-              x.label = "Frame Frequency",
-              y.label = "Probability of Voting in Favor of Repro. Rights")
-```
-
-```{r, eval=F}
-# interaction levels
-ef <- effect(term="justicemq:relauo_womens_rights", mod = mod27)
-#ef1<-effect(term="pfemau*justicemq",xlevels=list(pfemau=c(0,.5,1)),mod=res0)  #used this in paper
-
-# as dataframe
-ef_df <-as.data.frame(ef) %>% mutate(relauo_womens_rights = as.factor(relauo_womens_rights))
-
-#By Color 
-ggplot(ef_df, aes(x = justicemq, y= fit, group = relauo_womens_rights))+
-  geom_point()+
-  geom_line(size = 1, aes(linetype = relauo_womens_rights))+
-  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=relauo_womens_rights),alpha=0.5) + 
-  labs(title = "Frequency of Women's Rights Frame and Justice Ideology", 
-       x= "Liberal                        Justice Ideology                         Conservative",
-       y="Vote for Opp.             Marginal Effects             Vote for Fem.") + 
-  guides(fill=guide_legend(reverse=T))+
-  guides(linetype=guide_legend(reverse=T))+
-  theme_bw() +
-  #scale_fill_grey()+
-  theme(plot.title = element_text(hjust = 0.5))+
-  labs(fill="Frame Frequency",
-       linetype="Frame Frequency")
-```
-
-\newpage
-
-```{r}
-summary(mod27)
-```

### 2022-05-16 modeling/amicus_type/forgauf.Rmd
add sgfem3 to base

@@
 * 0.01:
-* 0.05: 
-* 0.10: health (-), standing (+)
+* 0.05: standing (+)
+* 0.10: health (-) 
 * 0.20: bad law (+), morality & religion (+)
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 forgauf_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 forgauf_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 forgauf_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 forgauf_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 forgauf_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 forgauf_womens_rights,

### 2022-05-16 modeling/amicus_type/legauf.Rmd
add sgfem3 to base

@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 legauf_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 legauf_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 legauf_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 legauf_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 legauf_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 legauf_womens_rights,

### 2022-05-16 modeling/amicus_type/legauo.Rmd
add sgfem3 to base

@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 legauo_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 legauo_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 legauo_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 legauo_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 legauo_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 legauo_womens_rights,

### 2022-05-16 modeling/amicus_type/lifauo.Rmd
add sgfem3 to base

@@
 * 0.05: 
-* 0.10: final authority (+)
-* 0.20: privacy (+)
+* 0.10: final authority (+), privacy (+)
+* 0.20: fetus (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 lifauo_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 lifauo_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 lifauo_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 lifauo_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 lifauo_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 lifauo_womens_rights,

### 2022-05-16 modeling/amicus_type/medauf.Rmd
add sgfem3 to base

@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 medauf_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 medauf_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 medauf_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 medauf_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 medauf_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 medauf_womens_rights,

### 2022-05-16 modeling/amicus_type/medauo.Rmd
add sgfem3 to base

@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 medauo_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 medauo_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 medauo_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 medauo_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 medauo_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 medauo_womens_rights,

### 2022-05-16 modeling/amicus_type/relauf.Rmd
add sgfem3 to base

@@
 * 0.05: 
-* 0.10: 
-* 0.20: privacy (+)
+* 0.10: privacy (+)
+* 0.20: fetus (+), overturn roe (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 relauf_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 relauf_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 relauf_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 relauf_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                 relauf_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                 relauf_womens_rights,

### 2022-05-16 modeling/amicus_type/relauo.Rmd
add sgfem3 to base

@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_abortion_regret,
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_bad_law,
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_evidence,
@@
 mod11 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_fetus,
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 relauo_final_authority,
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_morality_religion,
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 relauo_overturn_roe,
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_privacy,
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 relauo_standing,
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_uncertainty,
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_undue_burden,
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_untruthful,
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                 relauo_womens_future_life,
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_womens_health,
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                 relauo_womens_rights,

### 2022-05-16 modeling/justicemq-interactions/forgauf.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_abortion_regret + forgauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_bad_law + forgauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_evidence + forgauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_fetus + forgauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_final_authority + forgauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_morality_religion + forgauf_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_privacy + forgauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_standing + forgauf_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_undue_burden + forgauf_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_womens_future_life + forgauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 forgauf_womens_health + forgauf_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/legauf.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_abortion_regret + legauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_bad_law + legauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_evidence + legauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_fetus + legauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_final_authority + legauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_morality_religion + legauf_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_privacy + legauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_standing + legauf_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_undue_burden + legauf_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_womens_future_life + legauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 legauf_womens_health + legauf_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/legauo.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_abortion_regret + legauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_bad_law + legauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_evidence + legauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_fetus + legauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_final_authority + legauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_morality_religion + legauo_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_privacy + legauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_standing + legauo_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_undue_burden + legauo_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_womens_future_life + legauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 legauo_womens_health + legauo_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/lifauo.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_abortion_regret + lifauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_bad_law + lifauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_evidence + lifauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_fetus + lifauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_final_authority + lifauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_morality_religion + lifauo_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_privacy + lifauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_standing + lifauo_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_undue_burden + lifauo_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_womens_future_life + lifauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 lifauo_womens_health + lifauo_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/medauf.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_abortion_regret + medauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_bad_law + medauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_evidence + medauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_fetus + medauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_final_authority + medauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_morality_religion + medauf_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_privacy + medauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_standing + medauf_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_undue_burden + medauf_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_womens_future_life + medauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 medauf_womens_health + medauf_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/medauo.Rmd
add sgfem3 to interaction models

@@
 ---
-title: "medauo Amicus Brief Models"
+title: "Medauo Amicus Brief Models"
 author: "Amanda Konet"
@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_abortion_regret + medauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_bad_law + medauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_evidence + medauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_fetus + medauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_final_authority + medauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_morality_religion + medauo_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_privacy + medauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_standing + medauo_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_undue_burden + medauo_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_womens_future_life + medauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 medauo_womens_health + medauo_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/relauf.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_abortion_regret + relauf_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_bad_law + relauf_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_evidence + relauf_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_fetus + relauf_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_final_authority + relauf_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_morality_religion + relauf_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_privacy + relauf_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_standing + relauf_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_undue_burden + relauf_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_womens_future_life + relauf_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + pfemam + 
                 relauf_womens_health + relauf_womens_health:justicemq,

### 2022-05-16 modeling/justicemq-interactions/relauo.Rmd
add sgfem3 to interaction models

@@
 mod3 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_abortion_regret + relauo_abortion_regret:justicemq,
@@
 mod4 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_bad_law + relauo_bad_law:justicemq,
@@
 mod9 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_evidence + relauo_evidence:justicemq,
@@
 mod11 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_fetus + relauo_fetus:justicemq,
@@
 mod12 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_final_authority + relauo_final_authority:justicemq,
@@
 mod14 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_morality_religion + relauo_morality_religion:justicemq,
@@
 mod18 <- glmer(justicevot ~
-               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+               (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_privacy + relauo_privacy:justicemq,
@@
 mod20 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_standing + relauo_standing:justicemq,
@@
 mod23 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_undue_burden + relauo_undue_burden:justicemq,
@@
 mod25 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_womens_future_life + relauo_womens_future_life:justicemq,
@@
 mod26 <- glmer(justicevot ~
-                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + poppam + 
+                (1+justicemq|id) + justicemq + justicefem + lcdisdirfem + sgfem3 + poppam + 
                 relauo_womens_health + relauo_womens_health:justicemq,

### 2022-05-17 eda/abortion-cases-frames-plots.Rmd
frame freq by case for eda

@@
 ---
-title: "abortion cases"
+title: "Frame X Amici Frequencies by Case"
 author: "Amanda Konet"
-date: "`r date()`"
 output: pdf_document
@@
 box_auth()
+final_cases <- "949901868853"
 ```
@@
 ```{r}
-df <- box_read("949904531983", read_fun = readr::read_csv)
+# data is 1 row per justice vote; convert to 1 row per case
+df <- box_read(final_cases) %>% 
+  filter(justicevot != "NA") %>% 
+  filter(case != "Gonzales v PP") %>% 
+  mutate(across(c(forgauf_abortion_different:forgauf_womens_rights,
+                  legauf_abortion_different:legauo_womens_rights,
+                  lifauo_abortion_different:medauo_womens_rights,
+                  relauf_abortion_different:relauo_womens_rights),
+                ~replace_na(.x, 0))) %>% 
+  distinct(case, ddate2,
+           forgauf_privacy, forgauf_undue_burden, forgauf_womens_health, forgauf_evidence,
+           medauf_womens_future_life, medauf_womens_health,
+           lifauo_undue_burden,
+           relauo_undue_burden, relauo_abortion_regret, relauo_fetus,
+           medauo_final_authority, medauo_evidence, medauo_morality_religion) %>% 
+  mutate(case = case_when(
+    case == "Anders v Floyd" ~ "Anders",
+    case == "Ayotte v PP" ~ "Ayotte",
+    case == "Beal v Doe" ~ "Beal",
+    case == "Bellotti v Baird 1976" ~ "Bellotti 76",
+    case == "Bellotti v Baird 1979" ~ "Bellotti 79",
+    case == "Bigelow v Virginia" ~ "Bigelow",
+    case == "Bray v Alexandria Womens Health Clinic" ~ "Bray",
+    case == "City of Akron v Akron Center" ~ "City of Akron",
+    case == "Colautti v Franklin" ~ "Colautti",
+    case == "Diamond v Charles" ~ "Diamond",
+    case == "Doe v Bolton" ~ "Bolton",
+    case == "Frisby v Schultz" ~ "Frisby",
+    case == "Gonzales v Carhart" ~ "Gonzales",
+    case == "H.L. v Matheson" ~ "H.L.",
+    case == "Harris v McRae" ~ "Harris",
+    case == "Hill v Colorado" ~ "Hill",
+    case == "Hodgson v Minnesota" ~ "Hodgson",
+    case == "Scheidler v NOW 2003" ~ "Scheidler 03",
+    case == "Scheidler v Now 2006" ~ "Scheidler 06",
+    case == "Madsen v Womens Health Center" ~ "Madsen",
+    case == "June v Russo" ~ "June",
+    case == "Maher v Roe" ~ "Maher",
+    case == "McCullen v Coakley" ~ "McCullen",
+    case == "NOW v Scheidler 1994" ~ "Scheidler 94",
+    case == "Ohio v Akron Center" ~ "Ohio",
+    case == "PP v Ashcroft" ~ "Ashcroft",
+    case == "PP v Danforth" ~ "Danforth",
+    case == "PP v Casey" ~ "Casey",
+    case == "Poelker v Doe" ~ "Poelker",
+    case == "Roe v Wade" ~ "Roe",
+    case == "Rust v Sullivan" ~ "Rust",
+    case == "Schenck v Pro-Choice Network" ~ "Schenck",
+    case == "Simopoulos v Virginia" ~ "Simopoulos",
+    case == "Singleton v Wulff" ~ "Singleton",
+    case == "Stenberg v Carhart" ~ "Stenberg",
+    case == "Thornburgh v American College of OBGYNs" ~ "Thornburgh",
+    case == "United States v Vuitch" ~ "Vuitch",
+    case == "Webster v Reproductive Health Services" ~ "Webster",
+    case == "WWH v Hellerstedt" ~ "WWH",
+    case == "Williams v Zbaraz" ~ "Williams",
+    T ~ case
+  ))
 ```
 
-# Abortion Negative II
+# Cases
+
+```{r, eval=F, echo=T}
+case == "Anders v Floyd" ~ "Anders",
+case == "Ayotte v PP" ~ "Ayotte",
+case == "Beal v Doe" ~ "Beal",
+case == "Bellotti v Baird 1976" ~ "Bellotti 76",
+case == "Bellotti v Baird 1979" ~ "Bellotti 79",
+case == "Bigelow v Virginia" ~ "Bigelow",
+case == "Bray v Alexandria Womens Health Clinic" ~ "Bray",
+case == "City of Akron v Akron Center" ~ "City of Akron",
+case == "Colautti v Franklin" ~ "Colautti",
+case == "Diamond v Charles" ~ "Diamond",
+case == "Doe v Bolton" ~ "Bolton",
+case == "Frisby v Schultz" ~ "Frisby",
+case == "Gonzales v Carhart" ~ "Gonzales",
+case == "H.L. v Matheson" ~ "H.L.",
+case == "Harris v McRae" ~ "Harris",
+case == "Hill v Colorado" ~ "Hill",
+case == "Hodgson v Minnesota" ~ "Hodgson",
+case == "Scheidler v NOW 2003" ~ "Scheidler 03",
+case == "Scheidler v Now 2006" ~ "Scheidler 06",
+case == "Madsen v Womens Health Center" ~ "Madsen",
+case == "June v Russo" ~ "June",
+case == "Maher v Roe" ~ "Maher",
+case == "McCullen v Coakley" ~ "McCullen",
+case == "NOW v Scheidler 1994" ~ "Scheidler 94",
+case == "Ohio v Akron Center" ~ "Ohio",
+case == "PP v Ashcroft" ~ "Ashcroft",
+case == "PP v Danforth" ~ "Danforth",
+case == "PP v Casey" ~ "Casey",
+case == "Poelker v Doe" ~ "Poelker",
+case == "Roe v Wade" ~ "Roe",
+case == "Rust v Sullivan" ~ "Rust",
+case == "Schenck v Pro-Choice Network" ~ "Schenck",
+case == "Simopoulos v Virginia" ~ "Simopoulos",
+case == "Singleton v Wulff" ~ "Singleton",
+case == "Stenberg v Carhart" ~ "Stenberg",
+case == "Thornburgh v American College of OBGYNs" ~ "Thornburgh",
+case == "United States v Vuitch" ~ "Vuitch",
+case == "Webster v Reproductive Health Services" ~ "Webster",
+case == "WWH v Hellerstedt" ~ "WWH",
+case == "Williams v Zbaraz" ~ "Williams"
+```
+
+\newpage
+
+# Reproductive Rights
+
+## Forgauf & Privacy
 
@@
 df %>% 
-  select(case, ddate2, ) %>% 
-  mutate(title = "Word/Phrase Count for Abortion Negative II Frame",
-         year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, decision_date), y = anii_freq)) +
+  select(case, ddate2, forgauf_privacy) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_privacy)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Abortion Negative II Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for FORG Privacy Frame"
   ) + 
@@
     strip.placement = "outside",
-    strip.text = element_text(color = "#afafaf", size = 7.4),
+    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
     # axis title
@@
     # axis text
-    axis.text.x = element_text(color = "#afafaf", size = 7.4, vjust = 0.9),
-    axis.text.y = element_text(color = "darkgray", size = 7),
+    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
+    axis.text.y = element_text(color = "gray45", size = 7),
     # axis ticks
@@
 
-# actor_couple
+## Forgauf & Undue Burden
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, ac_freq) %>% 
-  mutate(title = "Word/Phrase Count for Actor Couple Frame",
-         year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = ac_freq)) +
+df %>% 
+  select(case, ddate2, forgauf_undue_burden) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_undue_burden)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Actor Couple Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for FORG Undue Burden Frame"
   ) + 
@@
 
-# actor_fetus
+## Medauf & Women's Futures
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, af_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = af_freq)) +
+df %>% 
+  select(case, ddate2, medauf_womens_future_life) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = medauf_womens_future_life)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Actor Fetus Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for RR Med Women's Futures Frame"
   ) + 
@@
 
-# actor_physician
+## Forgauf & Women's Health
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, ap_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = ap_freq)) +
+df %>% 
+  select(case, ddate2, forgauf_womens_health) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_womens_health)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Actor Physician Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for FORG Women's Health Frame"
   ) + 
@@
 
-# compulsoryII
+## Medauf & Women's Health
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, c2_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = c2_freq)) +
+df %>% 
+  select(case, ddate2, medauf_womens_health) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = medauf_womens_health)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Compulsory II Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for RR Med Women's Health Frame"
   ) + 
@@
 
-# compulsoryMotherhood
+## Forgauf & Expert Evidence
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, cm_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = cm_freq)) +
+df %>% 
+  select(case, ddate2, forgauf_evidence) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_evidence)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Compulsory Motherhood Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for FORG Expert Evidence Frame"
   ) + 
@@
 
-# favorChildbirth
+# Antiabortion
+
+## Lifauo & Undue Burden
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, fc_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = fc_freq)) +
+df %>% 
+  select(case, ddate2, lifauo_undue_burden) %>% 
+  mutate(year = lubridate::year(ddate2),
+         ) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = lifauo_undue_burden)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Favor Childbirth Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for Antiabortion Undue Burden Frame"
   ) + 
@@
 
-# health
+## Relauo & Undue Burden
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, he_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = he_freq)) +
+df %>% 
+  select(case, ddate2, relauo_undue_burden) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = relauo_undue_burden)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Health Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for AA Rel Undue Burden Frame"
   ) + 
@@
 
-# intersectionality
+## Medauo & Final Authority
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, in_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = in_freq)) +
+df %>% 
+  select(case, ddate2, medauo_final_authority) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = medauo_final_authority)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Intersectionality Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for AA Med Final Authority Frame"
   ) + 
@@
 
-# morality
+## Relauo & Abortion Regret
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, mo_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = mo_freq)) +
+df %>% 
+  select(case, ddate2, relauo_abortion_regret) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = relauo_abortion_regret)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Morality Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for AA Rel Abortion Regret Frame"
   ) + 
@@
 
-# psy_harm
+## Medauo & Evidence
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, ph_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = ph_freq)) +
+df %>% 
+  select(case, ddate2, medauo_evidence) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = medauo_evidence)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Psycological Harm Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for AA Med Expert Evidence Frame"
   ) + 
@@
 
-# womanCitizenship
+## Relauo & Fetus
 
 ```{r}
-dec_frames %>% 
-  select(case, decision_date, wc_freq) %>% 
-  mutate(year = lubridate::year(decision_date)) %>% 
-  ggplot(., aes(x = reorder(case, year), y = wc_freq)) +
+df %>% 
+  select(case, ddate2, relauo_fetus) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = relauo_fetus)) +
   geom_bar(stat = "identity") +
@@
     x = "Case",
-    y = "Frequency of frame words/phrases in decision (divided by total word count)",
-    title = "Word/Phrase Count for Woman Citizenship Frame"
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for AA Rel Fetus Frame"
   ) + 
@@
 ```
+
+\newpage
+
+## Medauo & Morality
+
+```{r}
+df %>% 
+  select(case, ddate2, medauo_morality_religion) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = medauo_morality_religion)) +
+  geom_bar(stat = "identity") +
+  labs(
+    x = "Case",
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for AA Med Morality & Religion Frame"
+  ) + 
+  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
+  theme_bw() +
+  theme(
+    # grid lines + background
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.background = element_rect(fill = "white", size = 0.1),
+    panel.border = element_blank(),
+    plot.background = element_rect(color = "#eaeaea", size = 0.4),
+    axis.line = element_line(color = "#eaeaea", size = 0.4),
+    # facet format
+    panel.spacing = unit(0, "pt"), 
+    strip.background = element_blank(),
+    strip.placement = "outside",
+    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
+    # axis title
+    axis.title = element_text(color = "#666666", size = 8),
+    # axis text
+    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
+    axis.text.y = element_text(color = "gray45", size = 7),
+    # axis ticks
+    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
+    axis.ticks.y = element_blank(),
+    # title
+    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
+  )
+```

### 2022-05-18 modeling/amicus_type/other-authors/aclauf.Rmd
move author types we removed

--- 2022-04-22 modeling/amicus_type/aclauf.Rmd
@@
          justicefem = as.factor(justicefem),
-         nonftyp2 = as.factor(nonftyp2)) %>% 
-  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(aclauf_abortion_different:aclauf_womens_rights), ~replace_na(.x, 0)))
 ```
@@
 ```{r}
-data_scale <- data %>%
-  mutate(across(c(where(is.numeric), -justicevot, -id),
-                ~(scale(., center=T, scale=T) %>% as.vector)))
+data <- data %>%
+  select(case:cirsplit, aclauf_abortion_different:aclauf_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+                ~(scale(., center=T, scale=T))))
+                #~(scale(., center=T, scale=T) %>% as.vector)))
 
-data_scale <- janitor::remove_empty(data_scale, which = "cols")
+total_cols <- data %>% select(contains('aclauf')) %>% colnames()
+data <- janitor::remove_empty(data, which = "cols")
+remaining_cols <- data %>% select(contains('aclauf')) %>% colnames()
+setdiff(total_cols, remaining_cols)
 ```

### 2022-05-18 modeling/amicus_type/other-authors/chcauf.Rmd
move author types we removed

--- 2022-04-27 modeling/amicus_type/chcauf.Rmd
@@
          lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
          cirsplit = as.factor(cirsplit)) %>% 
-  mutate(across(c(chcauf_abortion_different:chcauf_womens_rights), ~replace_na(.x, 0)))
-```
+  mutate(across(c(chcauf_abortion_different:chcauf_womens_rights, 
+                  fem_abortion_different:fem_womens_rights), ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
 
-Add Case ID-- this will be the second level var
-
-```{r}
+# add case ID (second level var)
 case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
 data <- case_ids %>% left_join(., data, by = "case")
-#data %>% head(1) %>% select(case:justicefem)
 ```
@@
 data <- data %>%
-  select(case:cirsplit, pfemam, chcauf_abortion_different:chcauf_womens_rights) %>% 
-  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
+  select(case:cirsplit, pfemam, chcauf_abortion_different:chcauf_womens_rights, fem_abortion_different:fem_womens_rights) %>% 
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                 ~(scale(., center=T, scale=T))))
@@
 remaining_cols <- data %>% select(contains('chcauf')) %>% colnames()
-setdiff(total_cols, remaining_cols)
+#setdiff(total_cols, remaining_cols)
 ```
@@
 * 0:
-* 0.01:
-* 0.05: standing
+* 0.01: standing (+)
+* 0.05: 
 * 0.10: 
-* 0.20:
-
-\newpage
-
-# Abortion different
-
-```{r}
-mod1 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_abortion_different + pfemam,
-              family = binomial, data = data,  
-              nAGQ = 0, control=glmerControl(
-                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
-
-tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
-  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
-  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
-  mutate(confidence = case_when(
-    p.value >= 0 & p.value <= 0.001 ~ "***", 
-    p.value > 0.001 & p.value <= 0.01 ~ "**",
-    p.value > 0.01 & p.value <= 0.05 ~ "*",
-    p.value > 0.05 & p.value <= 0.1 ~ ".",
-    T ~ ""
-  )) %>% 
-  rename(odds_ratio = estimate) %>% 
-  select(term, odds_ratio, p_value = p.value, confidence) %>% 
-  kable()
-
-summary(mod1)
-```
+* 0.20: overturn roe (+)
 
@@
 mod3 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_abortion_regret + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_abortion_regret +
+                chcauf_abortion_regret,
               family = binomial, data = data,  
@@
 mod4 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_bad_law + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_bad_law + 
+                chcauf_bad_law,
               family = binomial, data = data,  
@@
 
-\newpage
-
-# Comp Motherhood
-
-```{r}
+```{r, eval = F}
 mod6a <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_compulsory_motherhood + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + chcauf_compulsory_motherhood + 
+                chcauf_compulsory_motherhood,
               family = binomial, data = data,  
@@
 
-\newpage
-
-# Compulsory Motherhood II
-
-```{r}
+```{r, eval = F}
 mod6b <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_compulsory_motherhood_ii + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_compulsory_motherhood_ii + 
+                chcauf_compulsory_motherhood_ii,
               family = binomial, data = data,  
@@
 mod9 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_evidence + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_evidence + 
+                chcauf_evidence,
               family = binomial, data = data,  
@@
 
+\newpage
+
+# Fetus
+
+```{r}
+mod11 <- glmer(justicevot ~
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_fetus + 
+                chcauf_fetus,
+              family = binomial, data = data,  
+              nAGQ = 0, control=glmerControl(
+                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
+
+tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
+  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
+  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
+  mutate(confidence = case_when(
+    p.value >= 0 & p.value <= 0.001 ~ "***", 
+    p.value > 0.001 & p.value <= 0.01 ~ "**",
+    p.value > 0.01 & p.value <= 0.05 ~ "*",
+    p.value > 0.05 & p.value <= 0.1 ~ ".",
+    T ~ ""
+  )) %>% 
+  rename(odds_ratio = estimate) %>% 
+  select(term, odds_ratio, p_value = p.value, confidence) %>% 
+  kable()
+
+summary(mod11)
+```
+
+\newpage
+
 # Final Authority
@@
 mod12 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_final_authority + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_final_authority +
+                chcauf_final_authority,
               family = binomial, data = data,  
@@
 mod14 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_morality_religion + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_morality_religion + 
+                chcauf_morality_religion,
               family = binomial, data = data,  
@@
 mod15 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_overturn_roe + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_overturn_roe +
+                chcauf_overturn_roe,
               family = binomial, data = data,  
@@
 mod18 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_privacy + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_privacy + 
+                chcauf_privacy,
               family = binomial, data = data,  
@@
 mod20 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_standing + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_standing +
+                chcauf_standing,
               family = binomial, data = data,  
@@
 mod22 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_uncertainty + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_uncertainty +
+                chcauf_uncertainty,
               family = binomial, data = data,  
@@
 mod23 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_undue_burden + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_undue_burden + 
+                chcauf_undue_burden,
               family = binomial, data = data,  
@@
 mod24 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_untruthful + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_untruthful + 
+                chcauf_untruthful,
               family = binomial, data = data,  
@@
 mod25 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_womens_future_life + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_womens_future_life +
+                chcauf_womens_future_life,
               family = binomial, data = data,  
@@
 mod26 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_womens_health + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_womens_health + 
+                chcauf_womens_health,
               family = binomial, data = data,  
@@
 mod27 <- glmer(justicevot ~
-                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
-                chcauf_womens_rights + pfemam,
+                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_womens_rights + 
+                chcauf_womens_rights,
               family = binomial, data = data,  

### 2022-05-18 modeling/amicus_type/other-authors/govauf.Rmd
move author types we removed

--- 2022-04-22 modeling/amicus_type/govauf.Rmd
@@
 * 0.05:
-* 0.10:
+* 0.10: informed consent
 

### 2022-05-18 modeling/amicus_type/other-authors/mpeauf.Rmd
move author types we removed

--- 2022-04-22 modeling/amicus_type/mpeauf.Rmd
@@
 * 0.05:
-* 0.10: bad law, physician, physician negative
+* 0.10: abortion different, bad law, physician negative
 

### 2022-05-18 modeling/amicus_type/other-authors/racauo.Rmd
move author types we removed

--- 2022-04-22 modeling/amicus_type/racauo.Rmd
@@
 
-```{r}
+```{r, eval=F}
 mod4 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod19 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod24 <- glmer(justicevot ~
@@
 
-```{r}
+```{r, eval=F}
 mod25 <- glmer(justicevot ~

### 2022-05-18 modeling/amicus_type/other-authors/sgauf.Rmd
move author types we removed

--- 2022-04-22 modeling/amicus_type/sgauf.Rmd
@@
 * 0.01:
-* 0.05:
-* 0.10:
+* 0.05: women's future (-)
+* 0.10: final authority, physician negative
 

### 2022-05-18 modeling/amicus_type/other-authors/sgauo.Rmd
move author types we removed

--- 2022-04-22 modeling/amicus_type/sgauo.Rmd
@@
 * 0.05:
-* 0.10: women's health
+* 0.10: bad law
 

### 2022-05-18 eda/paper-graphics.Rmd
Added table 1

@@
 library(boxr)
+library(stargazer)
 box_auth()
@@
 df <- box_read("949901868853", read_fun = readr::read_csv)
+amicus <- box_read("947307207905", read_fun = readr::read_csv)
 ```
@@
 ```
+
+# Table 1
+
+```{r, results='asis'}
+author_types <- amicus %>% select(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo) %>%
+  mutate(across(where(is.character), as.numeric)) %>%
+  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
+  pivot_longer(.,cols = c(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo), names_to = "var", values_to = "ct") %>%
+  arrange(var)
+
+author_types <- author_types %>% mutate(author_type = substr(var, 1, 3), position = substr(var, 4, 6)) %>% select(-var)
+
+author_types$position <- ifelse(author_types$position == "auf", 'Reproductive Rights', 'Antiabortion')
+author_types <- author_types %>% mutate(`Amicus Author Type` = case_when(
+  author_type == 'chc' ~ 'Feminist Organizations',
+  author_type == 'lif' ~ 'Anti-Feminist Organizations',
+  author_type == 'med' ~ 'Medical Practioners/Orgs/Researchers/Educators',
+  author_type == 'leg' ~ 'Legal Organizations',
+  author_type == 'rel' ~ 'Religious Groups',
+)) %>% select(-author_type)
+
+author_table <- author_types %>% pivot_wider(names_from = position, values_from = ct)
+author_table[1,3] <- 0
+author_table[3,2] <- 0
+
+stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.
+Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a.
+Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).
+Also, the same organizations file briefs in multiple cases.", header=FALSE, notes.align = 'c')
+```

### 2022-05-20 eda/paper-graphics.Rmd
updated table1 to html

@@
 date: "`r date()`"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 ---
@@
 
+total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
+author_table <- rbind(author_table, total)
+
 stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.
@@
 Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).
-Also, the same organizations file briefs in multiple cases.", header=FALSE, notes.align = 'c')
+Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l')
 ```

### 2022-05-20 eda/paper-graphics.Rmd
started table2

@@
 ```{r, results='asis'}
+#transform dataframe
 author_types <- amicus %>% select(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo) %>%
@@
 
+#clean up names
 author_types <- author_types %>% mutate(author_type = substr(var, 1, 3), position = substr(var, 4, 6)) %>% select(-var)
@@
 
+#clean values
 author_table <- author_types %>% pivot_wider(names_from = position, values_from = ct)
@@
 
+#add totals
 total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
@@
 
+#create table
 stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.
@@
 ```
+
+# Table 2
+
+```{r, results='asis'}
+#read in models
+forg_privacy_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_privacy_interactions.rds")
+forg_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_undue_interactions.rds")
+lif_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/lif_undue_interactions.rds")
+
+stargazer(forg_privacy_interactions, forg_undue_interactions, lif_undue_interactions, title="Results", type='html',align=TRUE)
+```

### 2022-05-23 eda/paper-graphics.Rmd
updated tables for paper

@@
 #read in models
+forg_privacy <- readRDS("../modeling/amicus_type/models/forg_privacy.rds")
 forg_privacy_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_privacy_interactions.rds")
+forg_undue <- readRDS("../modeling/amicus_type/models/forg_undue.rds")
 forg_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_undue_interactions.rds")
+lif_undue <- readRDS("../modeling/amicus_type/models/lif_undue.rds")
 lif_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/lif_undue_interactions.rds")
+relauo_undue <- readRDS("../modeling/amicus_type/models/relauo_undue.rds")
+relauo_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/relauo_undue_interactions.rds")
 
-stargazer(forg_privacy_interactions, forg_undue_interactions, lif_undue_interactions, title="Results", type='html',align=TRUE)
+stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
+          title="Results", type='html',align=TRUE,
+          column.labels = c("Forg Privacy", "Forg Undue", 
+                            "Life Undue", "Relauo Undue"))
+# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
 ```
+
+# Table 3
+
+```{r, results='asis'}
+#read in models
+forg_womenhealth <- readRDS("../modeling/amicus_type/models/forg_womenhealth.rds")
+forg_womenhealth_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_womenshealth_interactions.rds")
+medauf_womenhealth <- readRDS("../modeling/amicus_type/models/medauf_womenhealth.rds")
+medauf_womenhealth_interactions <- readRDS("../modeling/justicemq-interactions/models/medauf_womenshealth_interactions.rds")
+forg_womenfuture <- readRDS("../modeling/amicus_type/models/forg_womenfuture.rds")
+relauo_abortionregret <- readRDS("../modeling/amicus_type/models/relauo_abortionregret.rds")
+forg_evidence <- readRDS("../modeling/amicus_type/models/forg_evidence.rds")
+forg_evidence_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_evidence_interactions.rds")
+medauo_evidence <- readRDS("../modeling/amicus_type/models/medauo_evidence.rds")
+medauo_evidence_interactions <- readRDS("../modeling/justicemq-interactions/models/medauo_evidence_interactions.rds")
+
+stargazer(forg_womenhealth, forg_womenhealth_interactions, medauf_womenhealth, medauf_womenhealth_interactions, forg_womenfuture, relauo_abortionregret, forg_evidence, forg_evidence_interactions, medauo_evidence, medauo_evidence_interactions
+          ,title="Results", type='html',align=TRUE,
+          column.labels = c("Forg Privacy", "Forg Undue", 
+                            "Life Undue", "Relauo Undue"))
+```
+
+# Table 4
+
+```{r, results='asis'}
+#read in models
+forg_fetus <- readRDS("../modeling/amicus_type/models/forg_fetus.rds")
+forg_morality <- readRDS("../modeling/amicus_type/models/forg_morality.rds")
+relauo_fetus <- readRDS("../modeling/amicus_type/models/relauo_fetus.rds")
+relauo_fetus_interactions <- readRDS("../modeling/justicemq-interactions/models/relauo_fetus_interactions.rds")
+medauo_morality <- readRDS("../modeling/amicus_type/models/medauo_morality.rds")
+
+stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
+          ,title="Results", type='html',align=TRUE,
+          column.labels = c("Forg Privacy", "Forg Undue", 
+                            "Life Undue", "Relauo Undue"))
+```

### 2022-05-23 modeling/amicus_type/forgauf.Rmd
updated tables for paper

@@
 ```
+
+```{r, eval=F}
+#save models for paper tables
+saveRDS(mod9, "models/forg_evidence.rds")
+saveRDS(mod11, "models/forg_fetus.rds")
+saveRDS(mod14, "models/forg_morality.rds")
+saveRDS(mod18, "models/forg_privacy.rds")
+saveRDS(mod23, "models/forg_undue.rds")
+saveRDS(mod25, "models/forg_womenfuture.rds")
+saveRDS(mod26, "models/forg_womenhealth.rds")
+
+```

### 2022-05-23 modeling/amicus_type/medauo.Rmd
updated women's future frame
updated tables for paper

@@
 * 0.05: morality & religion (-)
-* 0.10: abortion regret (+)
+* 0.10: abortion regret (+), women's future life (+)
 * 0.20: undue burden (-), women's health (+)
@@
 ```
+
+```{r, eval=F}
+#save models for paper tables
+saveRDS(mod14, "models/medauo_morality.rds")
+saveRDS(mod9, "models/medauo_evidence.rds")
+
+```

### 2022-05-23 modeling/amicus_type/relauo.Rmd
updated women's future frame
updated tables for paper

@@
 * 0.05: abortion regret (+)
-* 0.10: evidence (+)
+* 0.10: evidence (+), women's futures (+)
 * 0.20: bad law (+), women's health (+)
@@
 ```
+
+```{r, eval=F}
+#save models for paper tables
+saveRDS(mod11, "models/relauo_fetus.rds")
+saveRDS(mod23, "models/relauo_undue.rds")
+saveRDS(mod26, "models/relauo_abortionregret.rds")
+
+```

### 2022-05-23 eda/paper-graphics.Rmd
fixed model labels

@@
           title="Results", type='html',align=TRUE,
-          column.labels = c("Forg Privacy", "Forg Undue", 
-                            "Life Undue", "Relauo Undue"))
+          column.labels = c("Model 1", "Model 2", 
+                            "Model 3", "Model 4", "Model 5", "Model 6", 
+                            "Model 7", "Model 8"))
 # , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
@@
           ,title="Results", type='html',align=TRUE,
-          column.labels = c("Forg Privacy", "Forg Undue", 
-                            "Life Undue", "Relauo Undue"))
+          column.labels = c("Model 1", "Model 2", 
+                            "Model 3", "Model 4", "Model 5", "Model 6", 
+                            "Model 7", "Model 8", "Model 9", "Model 10"))
 ```
@@
           ,title="Results", type='html',align=TRUE,
-          column.labels = c("Forg Privacy", "Forg Undue", 
-                            "Life Undue", "Relauo Undue"))
+          column.labels = c("Model 1", "Model 2", 
+                            "Model 3", "Model 4", "Model 5"))
 ```

### 2022-05-23 eda/paper-graphics.Rmd
graph format pending holly

@@
 output:
-  html_document:
-    df_print: paged
+  html_document
 ---
@@
 
-stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
-          title="Results", type='html',align=TRUE,
+stargazer(forg_privacy, forg_privacy_interactions,
+          forg_undue, forg_undue_interactions,
+          lif_undue, lif_undue_interactions,
+          relauo_undue, relauo_undue_interactions,
+          type='html',align=TRUE,
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
           column.labels = c("Model 1", "Model 2", 
                             "Model 3", "Model 4", "Model 5", "Model 6", 
-                            "Model 7", "Model 8"))
-# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
+                            "Model 7", "Model 8"),
+          order=c("forgauf_privacy", "justicemq:forgauf_privacy",
+                  "forgauf_undue_burden", "justicemq:forgauf_undue_burden",
+                  "lifauo_undue_burden", "justicemq:lifauo_undue_burden",
+                  "relauo_undue_burden", "justicemq:relauo_undue_burden",
+                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
+          covariate.labels = c("feminist privacy","justice ideology X feminist privacy",
+                               "feminist undue burden", "feminist undue burden x justice ideology",
+                               "AA org undue burden", "AA org undue burden x justice ideology",
+                               "religious (AA) undue burden", "religious (AA) undue burden X justice ideology",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table2.htm")
 ```
@@
 
-stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
-          ,title="Results", type='html',align=TRUE,
+stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality,
+          title="Results", type='html',align=TRUE,
           column.labels = c("Model 1", "Model 2", 

### 2022-05-24 eda/miscellaneous_eda.Rmd
eda for paper

---
title: "Miscellaneous"
author: "Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
library(stargazer)
box_auth()

amicus <- box_read("947307207905", read_fun = readr::read_csv)
```

The average number of authors on the RR and AA amici (separately) for our 40 abortion cases

 (still in progress)

The average number of amici per case on the RR and AA sides (RR and AA separately).

```{r}
amici_per_case <- amicus %>% group_by(case, brief_party) %>% summarize(count = n())
amici_per_case %>% group_by(brief_party) %>% summarize(avg = mean(count))
```

### 2022-05-24 eda/paper-graphics.Rmd
change labels

--- 2022-05-23 eda/paper-graphics.Rmd
@@
 
-stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
-          title="Results", type='html',align=TRUE,
-          column.labels = c("Forg Privacy", "Forg Undue", 
-                            "Life Undue", "Relauo Undue"))
-# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
+stargazer(forg_privacy, forg_privacy_interactions,
+          forg_undue, forg_undue_interactions,
+          lif_undue, lif_undue_interactions,
+          relauo_undue, relauo_undue_interactions,
+          type='html',align=TRUE,
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
+          column.labels = c("Model 1", "Model 2", 
+                            "Model 3", "Model 4", "Model 5", "Model 6", 
+                            "Model 7", "Model 8"),
+          order=c("forgauf_privacy", "justicemq:forgauf_privacy",
+                  "forgauf_undue_burden", "justicemq:forgauf_undue_burden",
+                  "lifauo_undue_burden", "justicemq:lifauo_undue_burden",
+                  "relauo_undue_burden", "justicemq:relauo_undue_burden",
+                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
+          covariate.labels = c("feminist org privacy","feminist org privacy X justice ideology",
+                               "feminist org undue burden", "feminist org undue burden x justice ideology",
+                               "prolife org undue burden", "prolife org undue burden x justice ideology",
+                               "religious (AA) undue burden", "religious (AA) undue burden X justice ideology",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table2.htm")
 ```
@@
 
-stargazer(forg_womenhealth, forg_womenhealth_interactions, medauf_womenhealth, medauf_womenhealth_interactions, forg_womenfuture, relauo_abortionregret, forg_evidence, forg_evidence_interactions, medauo_evidence, medauo_evidence_interactions
+stargazer(forg_womenhealth, forg_womenhealth_interactions, 
+          medauf_womenhealth, medauf_womenhealth_interactions,
+          #forg_womenfuture,
+          relauo_abortionregret,
+          forg_evidence, forg_evidence_interactions,
+          medauo_evidence, medauo_evidence_interactions
           ,title="Results", type='html',align=TRUE,
-          column.labels = c("Forg Privacy", "Forg Undue", 
-                            "Life Undue", "Relauo Undue"))
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
+          column.labels = c("Model 1", "Model 2", 
+                            "Model 3", "Model 4", "Model 5", "Model 6", 
+                            "Model 7", "Model 8", "Model 9", "Model 10"),
+          order=c("forgauf_womens_health", "justicemq:forgauf_womens_health",
+                  "medauf_womens_health", "justicemq:medauf_womens_health",
+                  #"forgauf_womens_future_life",
+                  "relauo_abortion_regret",
+                  "forgauf_evidence", "justicemq:forgauf_evidence",
+                  "medauo_evidence", "justicemq:medauo_evidence",
+                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
+          covariate.labels = c("feminist org women's health", "feminist org women's health X justice ideology",
+                               "medical (RR) women's health", "medical (RR) women's health x justice ideology",
+                               #"feminist org women's futures",
+                               "religious (AA) abortion regret", 
+                               "feminist org expert evidence", "feminist org expert evidence X justice ideology",
+                               "medical (RR) expert evidence", "medical (RR) expert evidence X justice ideology",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table3.htm")
 ```
@@
 
-stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
-          ,title="Results", type='html',align=TRUE,
-          column.labels = c("Forg Privacy", "Forg Undue", 
-                            "Life Undue", "Relauo Undue"))
+stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality,
+          title="Results", type='html',align=TRUE,
+          column.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
+          order=c("forgauf_fetus",
+                  "forgauf_morality_religion",
+                  "relauo_fetus", "justicemq:relauo_fetus",
+                  "medauo_morality_religion",
+                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
+          covariate.labels = c("feminist org fetus",
+                               "feminist org morality and religious",
+                               "religious (AA) fetus", "religious (AA) fetus X justice ideology",
+                               "medical (RR) morality",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table4.htm")
 ```

### 2022-05-24 eda/paper-graphics.Rmd
out file for table1
table3

--- 2022-05-23 eda/paper-graphics.Rmd
@@
 Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).
-Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l')
+Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l', out = "graphics/table1.htm")
 ```
@@
 
-stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
-          title="Results", type='html',align=TRUE,
+stargazer(forg_privacy, forg_privacy_interactions,
+          forg_undue, forg_undue_interactions,
+          lif_undue, lif_undue_interactions,
+          relauo_undue, relauo_undue_interactions,
+          type='html',align=TRUE,
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
           column.labels = c("Model 1", "Model 2", 
                             "Model 3", "Model 4", "Model 5", "Model 6", 
-                            "Model 7", "Model 8"))
-# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
+                            "Model 7", "Model 8"),
+          order=c("forgauf_privacy", "justicemq:forgauf_privacy",
+                  "forgauf_undue_burden", "justicemq:forgauf_undue_burden",
+                  "lifauo_undue_burden", "justicemq:lifauo_undue_burden",
+                  "relauo_undue_burden", "justicemq:relauo_undue_burden",
+                  "justicemq","justicefem","pfemam","poppam","sgfem3","lcdisdirfem"),
+          covariate.labels = c("feminist org privacy","feminist org privacy X justice ideology",
+                               "feminist org undue burden", "feminist org undue burden x justice ideology",
+                               "prolife org undue burden", "prolife org undue burden x justice ideology",
+                               "religious (AA) undue burden", "religious (AA) undue burden X justice ideology",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table2.htm")
 ```
@@
 
-stargazer(forg_womenhealth, forg_womenhealth_interactions, medauf_womenhealth, medauf_womenhealth_interactions, forg_womenfuture, relauo_abortionregret, forg_evidence, forg_evidence_interactions, medauo_evidence, medauo_evidence_interactions
-          ,title="Results", type='html',align=TRUE,
+stargazer(forg_womenhealth, forg_womenhealth_interactions, 
+          medauf_womenhealth, medauf_womenhealth_interactions,
+          forg_womenfuture,
+          relauo_abortionregret,
+          forg_evidence, forg_evidence_interactions,
+          medauo_evidence, medauo_evidence_interactions,
+          title="Results", type='html',align=TRUE,
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
           column.labels = c("Model 1", "Model 2", 
                             "Model 3", "Model 4", "Model 5", "Model 6", 
-                            "Model 7", "Model 8", "Model 9", "Model 10"))
+                            "Model 7", "Model 8", "Model 9", "Model 10"),
+          order=c("forgauf_womens_health", "justicemq:forgauf_womens_health",
+                  "medauf_womens_health", "justicemq:medauf_womens_health",
+                  "forgauf_womens_future_life",
+                  "relauo_abortion_regret",
+                  "forgauf_evidence", "justicemq:forgauf_evidence",
+                  "medauo_evidence", "justicemq:medauo_evidence",
+                  "justicemq","justicefem","pfemam","poppam","sgfem3","lcdisdirfem"),
+          covariate.labels = c("feminist org women's health", "feminist org women's health X justice ideology",
+                               "medical (RR) women's health", "medical (RR) women's health x justice ideology",
+                               "feminist org women's futures",
+                               "religious (AA) abortion regret", 
+                               "feminist org expert evidence", "feminist org expert evidence X justice ideology",
+                               "medical (RR) expert evidence", "medical (RR) expert evidence X justice ideology",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table3.htm")
 ```
@@
 
-stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
-          ,title="Results", type='html',align=TRUE,
-          column.labels = c("Model 1", "Model 2", 
-                            "Model 3", "Model 4", "Model 5"))
+stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality,
+          title="Results", type='html',align=TRUE,
+          column.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
+          model.numbers = F, ci=T,
+          dep.var.labels="Justice Vote (1 = Fem)",
+          order=c("forgauf_fetus",
+                  "forgauf_morality_religion",
+                  "relauo_fetus", "justicemq:relauo_fetus",
+                  "medauo_morality_religion",
+                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
+          covariate.labels = c("feminist org fetus",
+                               "feminist org morality and religious",
+                               "religious (AA) fetus", "religious (AA) fetus X justice ideology",
+                               "medical (RR) morality",
+                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
+                               "SG amicus brief", "lower court decision"),
+          out="graphics/table4.htm")
 ```

### 2022-05-24 data-cleaning/07-generate-frame-measures.Rmd
indiv word cts

@@
 ```{r}
-box_write(case_frames,
-           file_name = "case-level-frame-measures.csv",
-           dir_id = 161199725595)
+#box_write(case_frames,
+#           file_name = "case-level-frame-measures.csv",
+#           dir_id = 161199725595)
 ```
+
+# Additional Info
+
+```{r, eval=F}
+frame = "women's_health"
+
+phrases <- frame_terms %>% 
+  filter(frame_code == frame) %>%
+  select(word_clean) %>% 
+  .[[1]]
+
+# search tokens for the desired phrases, then create DFM
+frame_freqs <- toks %>% 
+  tokens_compound(pattern = phrase(phrases), concatenator = " ", 
+                case_insensitive = FALSE, valuetype = "fixed") %>%
+  tokens_select(phrases, case_insensitive = FALSE, valuetype = "fixed") %>%
+  dfm()
+
+# convert to df w/one row per brief+counts of phrases, joined w/brief info
+frame_word_freqs <- frame_freqs %>% 
+  convert(to = "data.frame") %>%
+  left_join(amicus_info, by = "doc_id") %>% 
+  select(case, id, brief, brief_party, word_ct, everything())
+
+# add amicus author
+amicus_type <- amicus %>% select(id, forgauf, legauf, legauo, lifauo,
+                                 medauf, medauo, relauf, relauo)
+frame_word_freqs <- frame_word_freqs %>% 
+  left_join(., amicus_type, on = "id") %>% 
+  select(-c(doc_id, legauf, legauo, lifauo, medauo, relauf, relauo)) %>% 
+  select(case, brief, id, brief_party, forgauf, medauf, word_ct, sort(colnames(.)))
+
+final <- frame_word_freqs %>% filter(forgauf == 1 | medauf == 1) %>% 
+  mutate(case = str_replace(case, 'v\\.', 'v'),
+         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""))
+
+#xlsx::write.xlsx(final, file = "womens_health_cts.xlsx")
+decisions <- readxl::read_xlsx("../eda/ab_cases.xlsx", sheet = "dat")
+decisions <- decisions %>% 
+  mutate(case = str_replace(case, 'v\\.', 'v'),
+         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
+         case = case_when(
+           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
+           case == "Ayotte AG of NH v Planned Parenhood of Northern New England" ~ "Ayotte v PP",
+           case == "Beal Sec Dept of Public Wel of PA v Doe" ~ "Beal v Doe",
+           case == "Bellotti Attorn Gen of MA v Baird 1979" ~ "Bellotti v Baird 1979",
+           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
+           case == "Colautti Sec of Wel of PA v Franklin" ~ "Colautti v Franklin",
+           case == "Doe et al v Bolton Attorn Gen of GA et al" ~ "Doe v Bolton",
+           case == "Gonzales AG v Leroy Carhart" ~ "Gonzales v Carhart",
+           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
+           case == "Harris Sec of HHS v McRae" ~ "Harris v McRae",
+           case == "Hartigan Attor Gen of IL v David Zbaraz and Allan G Charles" ~ "Hartigan v Zbaraz",
+           case == "Hill et al v Colorado" ~ "Hill v Colorado",
+           case == "H L v Matheson Gov of UT" ~ "H.L. v Matheson",
+           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
+           case == "Maher Comm of Soc Serv of CT v Roe" ~ "Maher v Roe",
+           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
+           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
+           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
+             "PP v Ashcroft",
+           case == "Planned Parenhood of SE Penn v Casey" ~ "PP v Casey",
+           case == "Planned Parenthood of Central MO v Danforth Attorn Gen of MO" ~ "PP v Danforth",
+           case == "Roe et al v Wade District Attorn of Dallas County" ~ "Roe v Wade",
+           case == "Rust v Sullivan Sec of HHS" ~ "Rust v Sullivan",
+           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
+           case == "Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
+           case == "Schenck et al v Pro-Choice Network of Western NY" ~
+             "Schenck v Pro-Choice Network",
+           case == "Stenberg AG of Neb v Leroy Carhart" ~ "Stenberg v Carhart",
+           case == "Thornburgh Gov of PA v American College of Obstetricians and Gynecologists" ~
+             "Thornburgh v American College of OBGYNs",
+           case == "Webster Attor Gen of MO v Reproductive Health Services" ~ "Webster v Reproductive Health Services", 
+           case == "Whole Womans Health v Hellerstedt" ~ "WWH v Hellerstedt",
+           T ~ case
+         )) %>%
+  arrange(case)
+
+final %>% 
+  janitor::clean_names() %>% 
+  left_join(., decisions, by = "case") %>% 
+  mutate(death = mortality+morbidity) %>% 
+  group_by(fem_win, forgauf, medauf) %>% 
+  summarize(n = sum(death))
+
+final %>% 
+  janitor::clean_names() %>% 
+  left_join(., decisions, by = "case") %>%
+  mutate(death = mortality+morbidity) %>% 
+  filter(forgauf == 1, fem_win == 0) %>% 
+  group_by(case, ddate2) %>% 
+  summarize(n = sum(death)) %>% 
+  arrange(ddate2)
+
+final %>% 
+  janitor::clean_names() %>% 
+  left_join(., decisions, by = "case") %>% 
+  mutate(illegal_abortion = illegal_abortion+illegal_abortions,
+         safe_abortion = safe_abortion + safe_legal_abortion,
+         self_abortion = self_abortion+self_abortions+
+           self_induced_abortion+self_induced_abortions) %>% 
+  select(-id, -brief_party, -word_ct, -sentences, -tokens, -types) %>% 
+  group_by(fem_win, forgauf, medauf) %>%
+  #summarize(across(where(is.numeric), ~sum(.x)))
+  summarize(illegal_abortion = sum(illegal_abortion),
+            safe_abortion = sum(safe_abortion),
+            self_abortion = sum(self_abortion))
+```

### 2022-05-24 modeling/amicus_type/relauo.Rmd
change relauo model

@@
 saveRDS(mod23, "models/relauo_undue.rds")
-saveRDS(mod26, "models/relauo_abortionregret.rds")
+saveRDS(mod3, "models/relauo_abortionregret.rds")
 

### 2022-05-25 eda/paper-graphics.Rmd
updated tables

@@
 library(stargazer)
+library(stringi)
 box_auth()
@@
 
+other_types <- amicus %>% select(forgau, antauo, govauf, govauo, sg, racauf, racauo, mpeauf, mpeauo, lg_bauf, forgauf, aclauf, aclauo, sgauf, sgauo) %>%
+  mutate(across(where(is.character), as.numeric)) %>%
+  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
+  pivot_longer(.,cols = c(forgau, antauo, govauf, govauo, sg, racauf, racauo, mpeauf, mpeauo, lg_bauf, forgauf, aclauf, aclauo, sgauf, sgauo), names_to = "var", values_to = "ct") %>%
+  arrange(var)
+
 #clean up names
@@
 author_types$position <- ifelse(author_types$position == "auf", 'Reproductive Rights', 'Antiabortion')
-author_types <- author_types %>% mutate(`Amicus Author Type` = case_when(
+author_types <- author_types %>% mutate(`Amicus-Author Type` = case_when(
   author_type == 'chc' ~ 'Feminist Organizations',
-  author_type == 'lif' ~ 'Anti-Feminist Organizations',
-  author_type == 'med' ~ 'Medical Practioners/Orgs/Researchers/Educators',
+  author_type == 'lif' ~ 'Prolife Organizations',
+  author_type == 'med' ~ 'Medical Organizations',
   author_type == 'leg' ~ 'Legal Organizations',
@@
 
+#create other category
+other_types <- other_types %>% mutate(position = stri_sub(var,-1))
+other_types$position <- ifelse(other_types$position == 'f', 'Reproductive Rights', 'Antiabortion')
+other_types <- other_types %>% group_by(position) %>% summarize(ct = sum(ct))
+other <- other_types %>% pivot_wider(names_from = position, values_from = ct)
+author_table <- rbind(author_table, c("Other", other$`Reproductive Rights`, other$`Antiabortion`))
+
 #add totals
-total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
+total <- c("Total", 330, 441)
 author_table <- rbind(author_table, total)
+
+#manually order
+author_table$order <- c(1, 4, 2, 3, 5, 6, 7)
+author_table <- author_table %>% arrange(order) %>% select(-order)
 
@@
 stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.
-Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a.
-Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).
-Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l', out = "graphics/table1.htm")
+Total Number of Amicus Briefs by Amicus-Author Type in the Supreme Court Abortion Cases", notes = c("a.
+The “Other” category contains various additional types of amici, including for organizations focused on racial justice and LGBTQ rights and from the U.S.
+Solicitor General.", "b.
+The separate amicus categories do not sum to the column totals because amicus briefs can be counted in more than one category."), header=FALSE, type = 'html', notes.align = 'l', out = "graphics/table1.htm")
 ```

### 2022-05-25 data-cleaning/07-generate-frame-measures.Rmd
update from when box wasnt working

@@
 frame_terms <- box_read("947335700912", read_fun = readr::read_csv)
+#frame_terms <- read_csv("~/Box/Amicus IV/data/amicus contents - frames/clean-amicus-iv-frame-dictionary.csv")
 ```
@@
   mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))
+
+#amicus <- read_csv("~/Box/Amicus IV/data/processed amicus files/clean-shortened-amicus-text-vars.csv") %>% 
+#  mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))
 ```
@@
 ```{r}
-box_write(amicus_frames,
-           file_name = "amicus-level-frame-measures.csv",
-           dir_id = 161199725595)
+#box_write(amicus_frames,
+#           file_name = "amicus-level-frame-measures.csv",
+#           dir_id = 161199725595)
 ```
@@
 
-#xlsx::write.xlsx(final, file = "womens_health_cts.xlsx")
 decisions <- readxl::read_xlsx("../eda/ab_cases.xlsx", sheet = "dat")
@@
   left_join(., decisions, by = "case") %>%
-  mutate(death = mortality+morbidity) %>% 
+  mutate(death = mortality+morbidity,
+         health_risk = health_risk+health_risks) %>% 
   filter(forgauf == 1, fem_win == 0) %>% 
   group_by(case, ddate2) %>% 
-  summarize(n = sum(death)) %>% 
+  summarize(maternal_health = sum(maternal_health), death = sum(death),
+            health_risk = sum(health_risk)) %>% 
   arrange(ddate2)
+
+final %>% 
+  janitor::clean_names() %>% 
+  left_join(., decisions, by = "case") %>%
+  mutate(death = mortality+morbidity) %>% 
+  filter(medauf == 1, fem_win == 1) %>% 
+  arrange(-death) %>% 
+  select(case, brief, forgauf, medauf, death, maternal_health)
 
@@
          self_abortion = self_abortion+self_abortions+
-           self_induced_abortion+self_induced_abortions) %>% 
+           self_induced_abortion+self_induced_abortions,
+         health_risk = health_risk+health_risks) %>% 
   select(-id, -brief_party, -word_ct, -sentences, -tokens, -types) %>% 
@@
             safe_abortion = sum(safe_abortion),
-            self_abortion = sum(self_abortion))
+            self_abortion = sum(self_abortion),
+            health_risk = sum(health_risk))
 ```

### 2022-05-25 eda/abortion-cases-frames-plots.Rmd
add forgauf wfl

@@
            forgauf_privacy, forgauf_undue_burden, forgauf_womens_health, forgauf_evidence,
-           medauf_womens_future_life, medauf_womens_health,
+           medauf_womens_future_life, medauf_womens_health, forgauf_womens_future_life,
            lifauo_undue_burden,
@@
     title = "Word/Phrase Count for RR Med Women's Futures Frame"
+  ) + 
+  facet_grid(~ year, switch = "x", scales = "free_x", space = "free_x") +
+  theme_bw() +
+  theme(
+    # grid lines + background
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.background = element_rect(fill = "white", size = 0.1),
+    panel.border = element_blank(),
+    plot.background = element_rect(color = "#eaeaea", size = 0.4),
+    axis.line = element_line(color = "#eaeaea", size = 0.4),
+    # facet format
+    panel.spacing = unit(0, "pt"), 
+    strip.background = element_blank(),
+    strip.placement = "outside",
+    strip.text = element_text(color = "gray10", size = 7.4, angle = 45),
+    # axis title
+    axis.title = element_text(color = "#666666", size = 8),
+    # axis text
+    axis.text.x = element_text(color = "gray45", size = 7.4, angle = 90, vjust = 0.5, hjust=1),
+    axis.text.y = element_text(color = "gray45", size = 7),
+    # axis ticks
+    axis.ticks.x = element_line(colour = "#bdbdbd", size = 0.4),
+    axis.ticks.y = element_blank(),
+    # title
+    plot.title = element_text(color = "#666666", size = 9.1, hjust = 0.5)
+  )
+```
+
+\newpage
+
+## Forgauf & Women's Futures
+
+```{r}
+df %>% 
+  select(case, ddate2, forgauf_womens_future_life) %>% 
+  mutate(year = lubridate::year(ddate2)) %>% 
+  ggplot(., aes(x = reorder(case, ddate2), y = forgauf_womens_future_life)) +
+  geom_bar(stat = "identity") +
+  labs(
+    x = "Case",
+    y = "Frequency of frame words/phrases in amici (divided by total word ct)",
+    title = "Word/Phrase Count for FORG Women's Futures Frame"
   ) + 

### 2022-05-25 eda/miscellaneous_eda.Rmd
analysis answers paper questions

@@
 amicus <- box_read("947307207905", read_fun = readr::read_csv)
+
+author_info <- box_read("936715223606")
+
+walkover <- box_read("941154488137", read_fun = readr::read_csv)
+
+regression_data <- box_read("949901868853", read_fun = readr::read_csv)
 ```
@@
 
- (still in progress)
+```{r}
+auth <- author_info  %>% filter(`Row Type` == "Amicus Brief") %>% select(Case, `Amicus \r\nBrief ID`, camau)
+
+walkover$case_code <- as.character(walkover$case_code)
+walkover$brief_code <- as.character(walkover$brief_code)
+auth$brief_code <- as.character(auth$`Amicus \r\nBrief ID`)
+
+auth <- left_join(auth, walkover, by = c("Case" = "case_code","brief_code"))
+
+author_parties <- left_join(auth, amicus, by = c("new_id" = "id")) %>% select(Case, brief_code, camau, brief_party)
+```
+
+```{r}
+author_per_case <- author_parties %>% group_by(Case, brief_party) %>% summarize(total_authors = sum(camau))
+author_per_case %>% group_by(brief_party) %>% summarize(avg = mean(total_authors))
+```
+
+```{r}
+author_per_amicus <- author_parties %>% group_by(Case, brief_code, brief_party) %>% summarize(total_authors = sum(camau))
+author_per_amicus %>% group_by(brief_party) %>% summarize(avg = mean(total_authors))
+```
 
@@
 ```
+
+For writing, I’d like to know who are the most liberal and most conservative justices in our data, using the MQ score?
+
+```{r}
+justices_data <- box_read("949901868853", read_fun = readr::read_csv)
+justices <- box_read_excel("934508714164", sheet = "Justices")
+
+j <- justices_data %>% filter(case != "Gonzales v PP" & !is.na(justicevot))
+
+average_mq <- j %>% select(justiceid, justicemq) %>% group_by(justiceid) %>% summarise(avg_mq = mean(justicemq)) %>% arrange(avg_mq)
+
+mq <- rbind(average_mq %>% tail(3), average_mq %>% slice(1:3))
+
+left_join(mq, justices, by = c("justiceid" = "ID"))
+```
+For writing, I’d like to know if the term “medical ethics” shows up in the medauo amici prior to the Rust v Sullivan (1991) Assoc of Amer Physicians and Surgeons brief.
+If so, where?
+List of amici and cases?
+Note for Sarah: use the clean amici text file (“947307207905”); this file has author type variables as well
+
+```{r}
+# read in file with decision dates
+decisions <- readxl::read_xlsx("../eda/ab_cases.xlsx", sheet = "dat")
+# clean up mismatched case names
+decisions <- decisions %>% 
+  mutate(case = str_replace(case, 'v\\.', 'v'),
+         case = str_replace_all(case, "(,|'|'|\\)|\\()", ""),
+         case = case_when(
+           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
+           case == "Ayotte AG of NH v Planned Parenhood of Northern New England" ~ "Ayotte v. PP",
+           case == "Beal Sec Dept of Public Wel of PA v Doe" ~ "Beal v Doe",
+           case == "Bellotti Attorn Gen of MA v Baird 1979" ~ "Bellotti v Baird (1979)",
+           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
+           case == "Colautti Sec of Wel of PA v Franklin" ~ "Colautti v Franklin",
+           case == "Doe et al v Bolton Attorn Gen of GA et al" ~ "Doe v. Bolton",
+           case == "Gonzales AG v Leroy Carhart" ~ "Gonzales v Carhart",
+           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
+           case == "Harris Sec of HHS v McRae" ~ "Harris v. McRae",
+           case == "Hartigan Attor Gen of IL v David Zbaraz and Allan G Charles" ~ "Hartigan v. Zbaraz",
+           case == "Hill et al v Colorado" ~ "Hill v. Colorado",
+           case == "H L v Matheson Gov of UT" ~ "H.L. v. Matheson",
+           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Women's Health Center",
+           case == "Maher Comm of Soc Serv of CT v Roe" ~ "Maher v. Roe",
+           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
+           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
+           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
+             "PP v Ashcroft",
+           case == "Planned Parenhood of SE Penn v Casey" ~ "PP v Casey",
+           case == "Planned Parenthood of Central MO v Danforth Attorn Gen of MO" ~ "PP v Danforth",
+           case == "Roe et al v Wade District Attorn of Dallas County" ~ "Roe v Wade",
+           case == "Rust v Sullivan Sec of HHS" ~ "Rust v Sullivan",
+           case == "Scheidler v NOW 2003" ~ "Scheidler v. NOW (2003)",
+           case == "Scheidler v NOW 2006" ~ "Scheidler v. Now (2006)",
+           case == "Schenck et al v Pro-Choice Network of Western NY" ~
+             "Schenck v. Pro-Choice Network",
+           case == "Stenberg AG of Neb v Leroy Carhart" ~ "Stenberg v. Carhart",
+           case == "Thornburgh Gov of PA v American College of Obstetricians and Gynecologists" ~
+             "Thornburgh v. American College of OBGYNs",
+           case == "Webster Attor Gen of MO v Reproductive Health Services" ~ "Webster v Reproductive Health Services", 
+           case == "Whole Womans Health v Hellerstedt" ~ "WWH v Hellerstedt",
+           case == "Bray v Alexandria Womens Health Clinic" ~ "Bray v Alexandria Women’s Health Clinic",
+           case == "Diamond v Charles" ~ "Diamond v. Charles",
+           case == "Frisby v Schultz" ~ "Frisby v. Schultz",
+           case == "Hodgson v Minnesota" ~ "Hodgson v. Minnesota",
+           case == "McCullen v Coakley" ~ "McCullen v. Coakley",
+           case == "Poelker Mayor of St Louis v Doe" ~ "Poelker v Doe",
+           case == "United States v Vuitch" ~ "United States v. Vuitch",
+           case == "Williams v Zbaraz" ~ "Williams v. Zbaraz",
+           T ~ case
+         )) %>%
+  arrange(case)
+```
+
+```{r}
+amicus_dates <- left_join(amicus, decisions, by = c("case"))
+
+amicus_dates <- amicus_dates %>% filter(ddate2 < 1991, medauo > 0) %>% select(case, ddate2, id, brief, medauo, text_clean)
+
+amicus_dates$medical_ethics <- str_count(amicus_dates$text_clean, "medical ethics")
+
+a <- amicus_dates %>% filter(medical_ethics > 0)
+a
+```
+
+```{r}
+x <- amicus %>% filter(case == "Rust v Sullivan") 
+x$medical_ethics <- str_count(x$text_clean, "medical ethics")
+y <- x %>% filter(medical_ethics > 0)
+y
+```
+
+For writing, I need to know whether I can state that the abortion regret frame is used more so by the antiabortion religious amici than the other types of antiabortion amici.
+
+```{r}
+data <- regression_data %>% filter(case != "Gonzales v PP" & !is.na(justicevot)) %>% select(legauo_abortion_regret, medauo_abortion_regret, lifauo_abortion_regret, relauo_abortion_regret)
+
+apply(data, 2, sum, na.rm=TRUE)
+```

### 2022-05-26 eda/paper-graphics.Rmd
update figure 1

@@
 
-df <- box_read("949901868853", read_fun = readr::read_csv)
+#df <- box_read("949901868853", read_fun = readr::read_csv)
+df <- read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") 
 amicus <- box_read("947307207905", read_fun = readr::read_csv)
@@
 
-# Cases per Year
-
-```{r}
-num_cases <- df %>%  distinct(case, decision_date=ddate2) %>% 
-  group_by(decision_date) %>% 
-  summarize(n = n())
-
-num_cases %>% 
-  ggplot(., aes(x = decision_date, y = n)) +
-  geom_line() + 
-  labs(
-    x = "Decision Year",
-    y = "Count of Amici",
-    title = "Number of Amici per Case"
-  ) +
-  theme_minimal()
-```
-
-# Number of Amici by Case
+# Figure 1 Number of Amici by Case
 
@@
   ggplot(., aes(x = year)) +
-  geom_line(aes(y = cfemam, linetype = "Feminist")) + 
-  geom_line(aes(y = coppam, linetype = "Opponent")) + 
-  scale_linetype_manual("Party", values=c("Feminist" = 1,"Opponent" = 2)) + 
+  geom_line(aes(y = cfemam, linetype = "Reproductive-Rights")) + 
+  geom_line(aes(y = coppam, linetype = "Antiabortion")) + 
+  scale_linetype_manual("Amici Type", values=c("Reproductive-Rights" = 1,"Antiabortion" = 2)) + 
   coord_cartesian(ylim = c(0, 50)) +
@@
   theme(
-    title = element_text(size = 10)
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"),
+    legend.position = "bottom"
   )
@@
 ```
+
 Check spike

### 2022-05-26 eda/vif.Rmd
vif for models

---
title: "VIF"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, warning=F, error=F)

library(tidyverse)
library(lme4)
library(boxr)
library(kableExtra)
library(broom.mixed)
library(performance)
```

# Data

Regression data used in models

```{r}
data <- #box_read(final_cases) %>% 
  read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #sgfem3 = as.factor(sgfem3), 
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(forgauf_abortion_regret:forgauf_womens_health,
                  legauf_abortion_regret:legauo_womens_health,
                  lifauo_abortion_regret:medauo_womens_health,
                  relauf_abortion_regret:relauo_womens_health,
                  fem_abortion_regret:opp_womens_health),
                ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

# add case ID (second level var)
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")

# scale
data <- data %>%
  select(case:cirsplit, pfemam, poppam,
         forgauf_abortion_regret:forgauf_womens_health,
         legauf_abortion_regret:legauo_womens_health,
         lifauo_abortion_regret:medauo_womens_health,
         relauf_abortion_regret:relauo_womens_health,
         fem_abortion_regret:opp_womens_health) %>%  
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                ~(scale(., center=T, scale=T))))
```

# Models

VIF for each frame X amici type

## Feminist-org

Abortion regret

```{r}
mod_forg_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_1)

#qqnorm(resid(mod_forg_1))
```

Expert evidence

```{r}
mod_forg_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_2)
```

Fetus

```{r}
mod_forg_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_3)
```

Morality & religion

```{r}
mod_forg_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_4)
```

Privacy

```{r}
mod_forg_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_5)
```

Undue burden

```{r}
mod_forg_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_6)
```

Women's futures

```{r}
mod_forg_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_7)
```

Women's health

```{r}
mod_forg_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_forg_8)
```

## Medical (RR)

Abortion regret

```{r}
mod_medRR_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                medauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_1)
```

Expert evidence

```{r}
mod_medRR_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_2)
```

Fetus

```{r}
mod_medRR_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_3)
```

Morality & religion

```{r}
mod_medRR_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_4)
```

Privacy

```{r}
mod_medRR_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_5)
```

Undue burden

```{r}
mod_medRR_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_6)
```

Women's futures

```{r}
mod_medRR_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                medauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_7)
```

Women's health

```{r}
mod_medRR_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                medauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medRR_8)
```

## Legal (RR)

Abortion regret

```{r}
mod_legRR_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_1)
```

Expert evidence

```{r}
mod_legRR_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_2)
```

Fetus

```{r}
mod_legRR_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_3)
```

Morality & religion

```{r}
mod_legRR_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_4)
```

Privacy

```{r}
mod_legRR_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_5)
```

Undue burden

```{r}
mod_legRR_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_6)
```

Women's futures

```{r}
mod_legRR_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_7)
```

Women's health

```{r}
mod_legRR_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legRR_8)
```

## Religious (RR)

Abortion regret

```{r}
mod_relRR_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                relauf_abortion_regret + fem_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_1)
```

Expert evidence

```{r}
mod_relRR_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_evidence + fem_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_2)
```

Fetus

```{r}
mod_relRR_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_fetus + fem_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_3)
```

Morality & religion

```{r}
mod_relRR_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_morality_religion + fem_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_4)
```

Privacy

```{r}
mod_relRR_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_privacy + fem_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_5)
```

Undue burden

```{r}
mod_relRR_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_undue_burden + fem_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_6)
```

Women's futures

```{r}
mod_relRR_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                relauf_womens_future_life + fem_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_7)
```

Women's health

```{r}
mod_relRR_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                relauf_womens_health + fem_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relRR_8)
```

## Prolife-orgs

Abortion regret

```{r}
mod_lif_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                lifauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_1)
```

Expert evidence

```{r}
mod_lif_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_2)
```

Fetus

```{r}
mod_lif_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_3)
```

Morality & religion

```{r}
mod_lif_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_4)
```

Privacy

```{r}
mod_lif_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_5)
```

Undue burden

```{r}
mod_lif_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_6)
```

Women's futures

```{r}
mod_lif_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                lifauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_7)
```

Women's health

```{r}
mod_lif_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                lifauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_lif_8)
```

## Medical (AA)

Abortion regret

```{r}
mod_medAA_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                medauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_1)
```

Expert evidence

```{r}
mod_medAA_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_2)
```

Fetus

```{r}
mod_medAA_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_3)
```

Morality & religion

```{r}
mod_medAA_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_4)
```

Privacy

```{r}
mod_medAA_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_5)
```

Undue burden

```{r}
mod_medAA_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_6)
```

Women's futures

```{r}
mod_medAA_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                medauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_7)
```

Women's health

```{r}
mod_medAA_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                medauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_medAA_8)
```

## Legal (AA)

Abortion regret

```{r}
mod_legAA_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_1)
```

Expert evidence

```{r}
mod_legAA_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_2)
```

Fetus

```{r}
mod_legAA_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_3)
```

Morality & religion

```{r}
mod_legAA_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_4)
```

Privacy

```{r}
mod_legAA_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_5)
```

Undue burden

```{r}
mod_legAA_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_6)
```

Women's futures

```{r}
mod_legAA_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_7)
```

Women's health

```{r}
mod_legAA_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_legAA_8)
```

## Religious (AA)

Abortion regret

```{r}
mod_relAA_1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                relauo_abortion_regret + opp_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_1)
```

Expert evidence

```{r}
mod_relAA_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_evidence + opp_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_2)
```

Fetus

```{r}
mod_relAA_3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_fetus + opp_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_3)
```

Morality & religion

```{r}
mod_relAA_4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_morality_religion + opp_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_4)
```

Privacy

```{r}
mod_relAA_5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_privacy + opp_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_5)
```

Undue burden

```{r}
mod_relAA_6 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_undue_burden + opp_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_6)
```

Women's futures

```{r}
mod_relAA_7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                relauo_womens_future_life + opp_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_7)
```

Women's health

```{r}
mod_relAA_8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                relauo_womens_health + opp_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

check_collinearity(mod_relAA_8)
```

### 2022-05-27 eda/paper-graphics.Rmd
appendix 3 tables

@@
 library(ggplot2)
+library(interactions)
 library(boxr)
@@
 library(stringi)
-box_auth()
+#box_auth()
 
@@
 df <- read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") 
-amicus <- box_read("947307207905", read_fun = readr::read_csv)
+#amicus <- box_read("947307207905", read_fun = readr::read_csv)
 ```
@@
   geom_line(aes(y = coppam, linetype = "Antiabortion")) + 
-  scale_linetype_manual("Amici Type", values=c("Reproductive-Rights" = 1,"Antiabortion" = 2)) + 
+  scale_linetype_manual("Amici Type:", values=c("Reproductive-Rights" = 1,"Antiabortion" = 2)) + 
   coord_cartesian(ylim = c(0, 50)) +
@@
 
-# Table 2
+# Table A.1
 
@@
 
-# Table 3
+# Table A.2
 
@@
 
-# Table 4
+# Table A.3
 
@@
 ```
+
+# Justice ideology graphs
+
+```{r}
+data <- #box_read(final_cases) %>% 
+  read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") %>% 
+  filter(justicevot != "NA") %>% 
+  mutate(justicevot = as.numeric(justicevot),
+         justiceid = as.factor(justiceid),
+         justicefem = as.factor(justicefem),
+         nonftyp2 = as.factor(nonftyp2),
+         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
+         lcdisdirfem = as.factor(lcdisdirfem),
+         #sgfem3 = as.factor(sgfem3), 
+         cirsplit = as.factor(cirsplit)) %>% 
+  mutate(across(c(forgauf_abortion_regret:forgauf_womens_health,
+                  legauf_abortion_regret:legauo_womens_health,
+                  lifauo_abortion_regret:medauo_womens_health,
+                  relauf_abortion_regret:relauo_womens_health,
+                  fem_abortion_regret:opp_womens_health),
+                ~replace_na(.x, 0))) %>% 
+  filter(case != "Gonzales v PP")
+
+# add case ID (second level var)
+case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
+data <- case_ids %>% left_join(., data, by = "case")
+
+# scale
+data <- data %>%
+  select(case:cirsplit, pfemam, poppam,
+         forgauf_abortion_regret:forgauf_womens_health,
+         legauf_abortion_regret:legauo_womens_health,
+         lifauo_abortion_regret:medauo_womens_health,
+         relauf_abortion_regret:relauo_womens_health,
+         fem_abortion_regret:opp_womens_health) %>%  
+  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
+                ~(scale(., center=T, scale=T))))
+```
+
+## Forg
+
+Privacy
+
+```{r}
+forg_privacy_plt <- 
+  interact_plot(forg_privacy_interactions, pred = forgauf_privacy, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/forg_privacy.png", forg_privacy_plt, height = 5, width = 8)
+
+forg_privacy_plt
+```
+
+Undue Burden
+
+```{r}
+forg_undue_plt <- 
+  interact_plot(forg_undue_interactions, pred = forgauf_undue_burden, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/forg_undue.png", forg_undue_plt, height = 5, width = 8)
+
+forg_undue_plt
+```
+
+Women's Health
+
+```{r}
+forg_health_plt <- 
+  interact_plot(forg_womenhealth_interactions, pred = forgauf_womens_health, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/forg_health.png", forg_health_plt, height = 5, width = 8)
+
+forg_health_plt
+```
+
+Evidence
+
+```{r}
+forg_evidence_plt <- 
+  interact_plot(forg_evidence_interactions, pred = forgauf_evidence, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/forg_evidence.png", forg_evidence_plt, height = 5, width = 8)
+
+forg_evidence_plt
+```
+
+## RR Medical
+
+Women's health
+
+```{r}
+medauf_health_plt <- 
+  interact_plot(medauf_womenhealth_interactions, pred = medauf_womens_health, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/medauf_health.png", medauf_health_plt, height = 5, width = 8)
+
+medauf_health_plt
+```
+
+## Prolife
+
+Undue Burden
+
+```{r}
+lifauo_undue_plt <- 
+  interact_plot(lif_undue_interactions, pred = lifauo_undue_burden, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/lifauo_undue.png", lifauo_undue_plt, height = 5, width = 8)
+
+lifauo_undue_plt
+```
+
+## AA Medical
+
+Expert-evidence
+
+```{r}
+medauo_evidence_plt <- 
+  interact_plot(medauo_evidence_interactions, pred = medauo_evidence, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/medauo_evidence.png", medauo_evidence_plt, height = 5, width = 8)
+
+medauo_evidence_plt
+```
+
+## AA Religious
+
+Undue burden
+
+```{r}
+relauo_undue_plt <- 
+  interact_plot(relauo_undue_interactions, pred = relauo_undue_burden, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/relauo_undue.png", relauo_undue_plt, height = 5, width = 8)
+
+relauo_undue_plt
+```
+
+Fetus
+
+```{r}
+relauo_fetus_plt <- 
+  interact_plot(relauo_fetus_interactions, pred = relauo_fetus, modx = justicemq,
+                #modx.values = c(-3.5, -1, 0, 1, 3.5),
+                # random
+                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
+                # quantiles
+                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
+                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
+                                "Moderately Conservative", "More Conservative"),
+                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
+                #outcome.scale = "link",
+                x.label = "Frame Frequency (Scaled)",
+                y.label = "Probability of Voting in Favor of Repro-Rights",
+                legend.main = "Justice Ideology") +
+  theme_minimal() +
+  theme(
+    plot.title = element_blank(),
+    title = element_text(size = 10, family = "Times New Roman"),
+    legend.text = element_text(size = 10, family = "Times New Roman"),
+    axis.text = element_text(size = 10, family = "Times New Roman"))
+
+ggsave("graphics/relauo_fetus.png", relauo_fetus_plt, height = 5, width = 8)
+
+relauo_fetus_plt
+```
